### 2024-11-22 paper/paper.qmd
update introduction

---
title: "The Impact of Interview Disruptions on Data Quality in Social Surveys"
subtitle: "Analyzing How Various Interferences Affect Respondent Accuracy and Survey Reliability"
author: 
  - Dezhen Chen
thanks: "Code and data are available at: https://github.com/1Dezhenchen/The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys."
date: today
date-format: long
abstract: "In social surveys, disruptions during interviews can significantly impact the quality of respondent data, which in turn affects the reliability of the survey results. This study uses Bayesian hierarchical logistic regression to analyze how various factors—such as the type of disruption, the presence of different family members, interview conduct method, interviewer characteristics, and respondent attitudes—affect the accuracy and quality of responses. Our analysis shows that different types of disruptions have distinct impacts on the quality of responses, revealing critical insights into optimizing survey conditions to improve data reliability and validity."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction
In recent years, the quality of social survey data has become an important topic of inquiry, especially with regard to how different disruptions impact respondent behavior. Several studies have contributed to this body of knowledge by focusing on factors that may affect the reliability of survey responses. Groves et al. (2009) examined the role of interviewer characteristics—such as experience and demeanor—in shaping the quality of responses through a multi-level modeling approach. In another key study, Couper and de Leeuw (2003) investigated how different modes of conducting interviews, like in-person versus telephone, influenced the comfort and attentiveness of respondents. Fowler and Mangione (1990) took a different approach by analyzing observational data to assess the impact of third-party presence during interviews. Although these works laid a valuable foundation for understanding data quality, there remains a gap in systematically analyzing the distinct effects of various kinds of disruptions, such as familial or environmental interference, on respondent understanding and response accuracy.

This study endeavors to address these overlooked aspects by closely examining the role of interview disruptions on data quality in a major social survey. Specifically, our analysis explores the influence of different types of interferences—including interruptions from partners, children, and other family members—on respondents' comprehension and engagement during the interview process. We employed a Bayesian logistic regression model utilizing the rstanarm package in R to capture these influences. The model incorporates a range of predictor variables, such as interviewer characteristics (age and gender), different methods of interview administration, and family-related interferences. During data preparation, the categorical levels of several predictor variables were simplified, excluding the 'country' variable, to ensure interpretability and to streamline model estimation. We also included indicators of respondent attitudes, such as whether questions were clarified during the interview or if reluctance to answer was observed, aiming for a more comprehensive understanding of respondent engagement.

Our results reveal compelling insights into the effects of these disruptions on data quality. We found that family-related interferences, notably from partners and parents, were associated with reduced comprehension on the part of respondents. The findings also suggested that interviews conducted in-person resulted in significantly higher levels of respondent understanding compared to those conducted by telephone. Additionally, older interviewers generally achieved better data quality, which could reflect an ability to manage disruptions more effectively or employ better rapport-building techniques. The influence of the interviewer's gender was also noted, though it appeared to interact in more complex ways with other factors such as the mode of interview and the specific type of interference. Taken together, these findings underscore the importance of managing both environmental and personal factors during interviews to improve data accuracy.

Beyond merely quantifying these effects, our study provides deeper implications for enhancing data collection practices in the field. The evidence points to the need for improved interviewer training focused on managing disruptions effectively, which can help ensure the collection of high-quality data even in less-than-ideal circumstances. The significant negative effects of family interference suggest that in-home surveys could benefit from targeted strategies to minimize such disruptions, including adjusting the timing of interviews or providing incentives for privacy during responses. Furthermore, the results highlight the importance of understanding respondent reluctance and tailoring interviewer interactions to reduce its occurrence. These insights have relevance for not only improving the current practices of social surveys but also for shaping future methodologies in an increasingly diverse and complex interviewing landscape.

The remainder of this paper is organized to present a comprehensive exploration of these topics. Section 2 provides a detailed overview of the dataset, focusing on the different variables and their role in assessing data quality. It also outlines the preprocessing steps taken, including data cleaning and the recoding of variables. Section 3 introduces the Bayesian logistic regression methodology, explaining the statistical approach and justifying the selection of priors for the analysis. In Section 4, we present the empirical findings, including parameter estimates and an interpretation of the relationships uncovered by the model. Section 5 discusses the practical implications of these findings, emphasizing the improvements needed in interviewer training and the strategies for reducing respondent interference. Finally, Section 6 summarizes the key contributions of this research, outlines the limitations, and suggests avenues for future work—particularly concerning the integration of new data collection technologies and adaptive survey designs aimed at mitigating the impact of disruptions on respondent data quality.

# Estimand
This study aims to evaluate the factors that influence the quality and reliability of survey responses during interview disruptions in social surveys. By analyzing variables such as different types of interferences (partner, child, parent, and relative interferences), interview methodologies, the demographic characteristics of interviewers (such as age and gender), the language of the questionnaire, and respondent behaviors like reluctance, clarification requests, and effort put into answering, this research seeks to understand how these elements affect the consistency and clarity of responses. The core goal is to determine the impact of these factors on respondent understanding and data reliability, thereby providing insights into improving survey methods and reducing biases in data collection.

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Measurement

Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

ggplot(penguins, aes(x = island, fill = species)) +
  geom_bar(alpha = 0.8) +
  scale_fill_manual(values = c("darkorange","purple","cyan4"),
                    guide = "none") +
  theme_minimal() +
  facet_wrap(~species, ncol = 1) +
  coord_flip()
```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

analysis_data |> 
  ggplot(aes(x = width, y = length)) +
  geom_point(alpha = 0.8) +
  theme_minimal() +
  labs(x = "Wing width (mm)",
       y = "Wing length (mm)")
```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is twofold. Firstly,...

Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## First discussion point {#sec-first-point}

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

## Second discussion point

Please don't use these as sub-heading labels - change them to be what your point actually is.

## Third discussion point

## Weaknesses and next steps

Weaknesses and next steps should also be included.

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-22 scripts/05-exploratory_data_analysis.R
update EDA

@@ -8,6 +8,9 @@
 # Any other information needed? Make sure you are in the `The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys` rproj
 #### Workspace setup ####
 library(tidyverse)
+library(GGally)
+library(ggplot2)
+
 
 # Load the dataset
 analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
@@ -79,3 +82,102 @@ ggplot(analysis_data, aes(x = interference_present, y = respondent_understood)) 
   geom_boxplot(fill = "tomato") +
   labs(title = "Interference Present vs Respondent Understanding", x = "Interference Present", y = "Respondent Understanding") +
   theme(axis.text.x = element_text(angle = 45, hjust = 1))
+
+
+
+
+
+# Plot 2: Interviewer Age Density by Top 5 Countries
+top_countries <- analysis_data %>%
+  count(country, sort = TRUE) %>%
+  top_n(5, n) %>%
+  pull(country)
+
+filtered_data <- analysis_data %>%
+  filter(country %in% top_countries)
+
+ggplot(filtered_data, aes(x = interviewer_age, fill = country, color = country)) +
+  geom_density(alpha = 0.4) +
+  labs(title = "Density Plot of Interviewer Age by Top 5 Countries", x = "Interviewer Age", y = "Density") +
+  theme_minimal()
+
+
+#### Advanced Visualization Code ####
+# Let's create some advanced visualizations using the dataset and column names provided earlier.
+
+# Load necessary libraries
+library(ggplot2)
+library(dplyr)
+
+# Assuming 'analysis_data' is your dataset
+
+# 1. Density Plot of Interview Duration by Gender of Interviewer
+#   This visualization helps understand the distribution of interview durations across interviewer genders.
+ggplot(analysis_data, aes(x = interviewer_id, fill = interviewer_gender)) +
+  geom_density(alpha = 0.5) +
+  labs(
+    title = "Density Plot of Interview Duration by Interviewer Gender",
+    x = "Interview Duration (minutes)",
+    y = "Density"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Set2")
+
+
+
+
+
+
+# 5. Heatmap of Respondent Understanding by Age Group and Country
+#   Shows patterns of understanding among respondents across different age groups and countries.
+# 过滤缺失值
+analysis_data <- analysis_data %>%
[…]

### 2024-11-23 paper/paper.qmd
update paper

@@
 
+library(arrow)
+library(knitr)
+library(rstanarm)
 library(tidyverse)
-library(palmerpenguins)
+library(ggplot2)
+library(bayesplot)
+library(ggridges)
 ```
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+We use the statistical programming language R (R Core Team 2023) to process, analyze, and visualize survey data exploring the impact of interview disruptions on response quality.
+The dataset used in this study includes several subsets tailored to different stages of the analysis, enabling a systematic and detailed examination of the research questions.
+The main dataset for modeling consists of 9,743 rows and 25 variables, capturing detailed information about different types of disruptions (e.g., partner, child, or relative interference), interview methods, and respondent characteristics.
 
-Overview text
+To ensure the reliability of the analysis, we filtered the data to exclude incomplete or ambiguous responses for key variables, such as missing values in "respondent_understood." Responses were also recoded into binary categories to focus on meaningful distinctions in response quality, while variables with excessive categories were grouped to improve interpretability.
+These preprocessing steps were essential to refine the dataset and facilitate robust modeling.
 
+The following R packages were employed to streamline the data analysis workflow:
+
+- **tidyverse** (Wickham et al. 2021): Used for efficient data manipulation, cleaning, and transformation. It includes:
+- **dplyr** (Wickham, François, et al. 2021): For summarizing and managing complex datasets.
+- **ggplot2** (Wickham 2021): For creating powerful and flexible visualizations.
+
+- **rstanarm** (Team 2021): Facilitated the implementation of Bayesian models, enabling straightforward regression modeling using Stan.
+
+- **arrow** (Apache Arrow 2021): Employed for efficiently reading and writing large datasets, enhancing data handling capabilities across systems.
+
+- **car** (Fox et al. 2021): Provided functions for regression diagnostics and other statistical analyses, particularly useful for checking assumptions and model validity.
+
+- **brms** (Bürkner 2021): A package for Bayesian regression modeling, which was used to implement more complex modeling approaches for the data.
+
+- **rsample** (Kuhn 2021): Used for creating resampling datasets, ensuring robust model validation by facilitating cross-validation and bootstrapping techniques.
+
+- **janitor** (Firke 2021): Simplified data cleaning processes by helping manage variable names and data structures, making raw data easier to handle.
+
+- **GGally** (Schloerke et al.
+2021): Used to enhance ggplot2 visualizations by providing additional functions for correlation plots and pairwise visualizations, which are useful for exploratory data analysis.
+This study aims to provide practical insights into how various disruptions affect data quality in survey settings, helping to optimize survey design and execution in the future.
 ## Measurement
 
-Some paragraphs about how we go from a phenomena in the world to an entry in the dataset.
+The data for this study is sourced from the European Social Survey (ESS), which collects information on societal attitudes and behaviors across multiple European countries.
+The dataset focuses on respondents’ understanding of survey questions, their cooperation levels, and the impact of environmental factors such as interruptions during interviews.
+All responses are collected using standardized methods to ensure comparability across countries.
+
+Different countries may implement localized adaptations in survey administration, which could influence response behaviors.
+To account for this, country-level metadata is included, allowing for the analysis of cross-national variations.
+```{r}
+#| warning: false
+#| message: false
+#| echo: false
+#| label: tbl-aerial_preview
+#| tbl-cap: "Survey responses on the impact of interview disruptions across countries in social surveys"
+
+# Load in data
+analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
+
+# Random sampling if needed
+set.seed(131)
+sampled_data <-analysis_data %>%
+  sample_n(5000)
+
+analysis_data |>
+  head() |>
+  kable(booktabs = TRUE, align = "c")
+```
 
@@
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
+Our analysis focuses on the following variables, with a specific focus on **respondent_understood_binary** as the dependent variable:
 
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
+- **respondent_understood_binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:
+  - *Understood*: Respondents who provided clear and accurate answers, indicating full comprehension of the questions.
+  - *Not understood*: Respondents who exhibited difficulties in understanding the questions, resulting in incomplete or unclear responses.
+
+- **interview_conduct_method**: The method by which the interview was conducted, with the following possible categories:
+  - *Face-to-face*: In-person interviews conducted by the surveyor.
+  - *Telephone*: Interviews conducted remotely via phone.
+  - *Self-administered*: Surveys completed by respondents themselves without direct interaction with a surveyor.
+
+- **child_interference**: Indicates whether interruptions by children occurred during the interview, with binary values:
+  - *Yes*: The interview was interrupted by children.
+  - *No*: No interruptions by children were recorded.
+
+- **partner_interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:
+  - *Yes*: The interview was interrupted by the respondent's partner.
+  - *No*: No interruptions by the partner were recorded.
+
+- **question_clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:
+  - *Yes*: The respondent asked for clarification.
+  - *No*: The respondent did not ask for clarification.
+
+- **respondent_reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:
+  - *Not reluctant*: The respondent showed no signs of hesitation.
+  - *Slightly reluctant*: The respondent exhibited mild hesitation.
+  - *Highly reluctant*: The respondent was clearly unwilling to engage with the survey.
+
+- **interviewer_age**: The age of the interviewer, used to explore whether interviewer demographics impact response quality.
+
+- **interviewer_gender**: The gender of the interviewer, categorized as:
+  - *Male*: Interviews conducted by male interviewers.
+  - *Female*: Interviews conducted by female interviewers.
+
+These variables were chosen for their potential influence on response quality and survey reliability, allowing for a comprehensive analysis of disruptions and other contextual factors.
+
+Detailed insights into the distribution of interviewer age across different countries are visualized in Figure 1, which presents the density plot of interviewer age for the top five countries in the dataset.
+```{r}
+#| label: fig-interviewer_age_density
+#| fig-cap: "Density plot of Interviewer Age by Top 5 Countries"
+#| echo: false
+#| fig.width: 8
+#| fig.height: 6
+top_countries <- analysis_data %>%
+  count(country, sort = TRUE) %>%
+  top_n(5, n) %>%
+  pull(country)
+
+filtered_data <- analysis_data %>%
+  filter(country %in% top_countries)
+
+ggplot(filtered_data, aes(x = interviewer_age, fill = country, color = country)) +
+  geom_density(alpha = 0.4) +
+  labs(title = "Density Plot of Interviewer Age by Top 5 Countries", x = "Interviewer Age", y = "Density") +
+  theme_minimal()
+
+```
+
+@fig-interviewer_age_density illustrates the distribution of interviewer ages across the top five countries in the dataset.
+The density plot highlights the variation in age demographics among interviewers from different countries, including Austria (AT), Germany (DE), Finland (FI), Great Britain (GB), and Ireland (IE).
+
+From the plot, we can observe that certain countries, such as Germany and Austria, have a higher concentration of interviewers in specific age ranges, while others, like Ireland, show a more dispersed distribution.
+This visualization provides an overview of the age composition of interviewers across these countries, offering useful context for understanding potential differences in survey implementation.
+```{r}
+#| label: fig-interference_frequency
+#| fig-cap: "Bar Plot of Interference Frequency by Respondent Tried Best"
+#| echo: false
+#| fig.width: 8
+#| fig.height: 6
+
+ggplot(analysis_data, aes(x = respondent_tried_best, fill = as.factor(interference_present))) +
+  geom_bar(position = "fill") +
+  labs(
+    title = "Bar Plot of Interference Frequency by Respondent Tried Best",
+    x = "Respondent Tried Best",
+    y = "Proportion",
+    fill = "Interference Present"
+  ) +
+  theme_minimal() +
+  scale_fill_brewer(palette = "Paired")
+
+```
+@fig-interference_frequency illustrates the frequency of interference during interviews across different levels of respondents’ effort, as measured by the variable "Respondent Tried Best." The bar plot shows the proportion of interviews with and without interference for each effort level, ranging from 1 (low effort) to 5 (high effort) and an additional "Other" category.
+
+From the plot, we can observe that interference is present across all effort levels, though its proportion varies slightly.
+Higher levels of effort (e.g., 4 and 5) tend to have a similar distribution of interference presence, while the "Other" category shows a slightly lower proportion of interference.
+This visualization provides an overview of how respondent effort and the presence of interference interact in the dataset.
 
 ```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
+#| label: fig-ridgeline_interviewer_age
+#| fig-cap: "Ridgeline Plot of Interviewer Age by Question Clarification Level"
 #| echo: false
+#| fig.width: 8
+#| fig.height: 6
+#| 
+ggplot(analysis_data, aes(x = interviewer_age, y = as.factor(question_clarification), fill = ..x..)) +
+  geom_density_ridges_gradient() +
+  scale_fill_viridis_c() +
+  labs(
+    title = "Ridgeline Plot of Interviewer Age by Question Clarification Level",
+    x = "Interviewer Age",
+    y = "Question Clarification Level"
+  ) +
+  theme_minimal()
 
-ggplot(penguins, aes(x = island, fill = species)) +
-  geom_bar(alpha = 0.8) +
-  scale_fill_manual(values = c("darkorange","purple","cyan4"),
-                    guide = "none") +
-  theme_minimal() +
-  facet_wrap(~species, ncol = 1) +
-  coord_flip()
 ```
+- **@fig-ridgeline_interviewer_age** shows a ridgeline plot of interviewer age distributions across different levels of question clarification requests. 
+- The x-axis represents interviewer age, while the y-axis categorizes responses by clarification levels (1 to 5) and an "Other" group.
+- Each ridge represents the density distribution of interviewer age for a specific clarification level.
+- Lighter colors indicate higher densities within the corresponding age range.
 
-Talk more about it.
+### Key Observations:
+- Interviewers aged 40 to 50 are prominent in levels 4 and 5, showing higher densities in these groups.
+- Clarification levels 1 and 2 show a broader distribution of interviewer ages, with no distinct peak.
+- The "Other" category exhibits a more balanced spread of ages, without significant density concentrations.
 
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
+This visualization highlights the distribution of interviewer age across clarification levels and provides insights into age-related patterns in survey interactions.
 
-```{r}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
-#| echo: false
-#| warning: false
-#| message: false
+##  Justification
 
-analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))
+The variables selected for this study were chosen carefully based on their importance in understanding the quality and reliability of survey responses.
+These variables are derived from the European Social Survey dataset and focus on key aspects of the interview process:
 
-analysis_data |> 
-  ggplot(aes(x = width, y = length)) +
-  geom_point(alpha = 0.8) +
-  theme_minimal() +
-  labs(x = "Wing width (mm)",
-       y = "Wing length (mm)")
-```
+- **Respondent Understanding (RESPONDENT_UNDERSTOOD_BINARY)**: Indicates whether the respondent fully comprehended the survey questions, categorized as *Understood* or *Not Understood*.
+- **Interview Conduct Method (INTERVIEW_CONDUCT_METHOD)**: Refers to the method of conducting the interview, including face-to-face interviews, telephone interviews, and self-administered surveys.
+- **Interference Factors**:
+  - **Child Interference (CHILD_INTERFERENCE)**: Documents whether interruptions occurred due to children during the interview (*Yes* or *No*).
+  - **Partner Interference (PARTNER_INTERFERENCE)**: Indicates whether the respondent’s partner interrupted the interview (*Yes* or *No*).
+- **Question Clarification (QUESTION_CLARIFICATION)**: Records whether the respondent asked for clarification on survey questions at any point.
+- **Respondent Reluctance (RESPONDENT_RELUCTANT)**: Reflects the respondent’s level of reluctance during the interview, categorized into levels from *Not Reluctant* to *Highly Reluctant*.
+- **Interviewer Age (INTERVIEWER_AGE)**: Specifies the age of the interviewer, which is included to examine possible influences of interviewer demographics.
+- **Interviewer Gender (INTERVIEWER_GENDER)**: Indicates the gender of the interviewer, recorded as *Male* or *Female*.
 
-Talk way more about it.
+Certain variables, such as **COUNTRY**, **SOCIOECONOMIC STATUS**, and **HOUSEHOLD COMPOSITION**, were excluded due to high levels of missing data or lesser relevance to the primary focus of the study.
+Similarly, variables with extensive categories were simplified to binary or grouped formats to enhance clarity and focus on essential distinctions.
 
-## Predictor variables
-
-Add graphs, tables and text.
-
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+After filtering and processing, the final dataset consists of **9,743 observations** and **25 variables**, structured to support a clear and concise examination of the study’s research objectives.
 

### 2024-11-23 scripts/06-model_data.R

@@ -7,7 +7,7 @@
 # Pre-requisites: The `tidyverse` package must be installed
 # Any other information needed? Make sure you are in the `The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys` rproj
 
-install.packages("loo")
+
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-11-25 scripts/06-model_data.R
update model

@@ -14,7 +14,7 @@ library(tidyverse)
 library(rstanarm)
 library(arrow)
 library(car)
-library(brms)
+library(brms)›
 
 #### Read data ####
 analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")

### 2024-11-25 paper/paper.qmd
update paper

@@
 library(ggridges)
+library(broom.mixed)
+library(kableExtra)
 ```
@@
 # Introduction
+
 In recent years, the quality of social survey data has become an important topic of inquiry, especially with regard to how different disruptions impact respondent behavior.
@@
 # Estimand
+
 This study aims to evaluate the factors that influence the quality and reliability of survey responses during interview disruptions in social surveys.
@@
 -   **tidyverse** (Wickham et al. 2021): Used for efficient data manipulation, cleaning, and transformation. It includes:
+
 -   **dplyr** (Wickham, François, et al. 2021): For summarizing and managing complex datasets.
+
 -   **ggplot2** (Wickham 2021): For creating powerful and flexible visualizations.
@@
 This study aims to provide practical insights into how various disruptions affect data quality in survey settings, helping to optimize survey design and execution in the future.
-## Measurement
+\## Measurement
 
@@
 To account for this, country-level metadata is included, allowing for the analysis of cross-national variations.
+
 ```{r}
@@
 
-# Random sampling if needed
 set.seed(131)
-sampled_data <-analysis_data %>%
+sampled_data <- analysis_data %>%
   sample_n(5000)
 
-analysis_data |>
-  head() |>
-  kable(booktabs = TRUE, align = "c")
+# Select important columns from both metadata and model variables
+important_columns <- c(
+  "dataset_title", "ess_round", "edition_number", "production_date", "country", "respondent_id",
+  "interview_conduct_method", "partner_interference", "child_interference",
+  "parent_interference", "relative_interference", "non_relative_interference",
+  "interviewer_age", "interviewer_gender", "question_clarification",
+  "respondent_reluctant", "respondent_tried_best"
+)
+
+# Filter data to only include important columns
+analysis_data_selected <- sampled_data %>%
+  select(all_of(important_columns))
+
+# Display the selected data with better column alignment
+analysis_data_selected |>
+  head(10) |>  # Limit to 10 rows to ensure readability
+  kable(booktabs = TRUE, align = "c", col.names = c(
+    "Dataset Title", "ESS Round", "Edition Number", "Production Date", "Country", "Respondent ID",
+    "Interview Method", "Partner Interference", "Child Interference", "Parent Interference",
+    "Relative Interference", "Non-relative Interference", "Interviewer Age",
+    "Interviewer Gender", "Question Clarification", "Respondent Reluctant", "Respondent Tried Best"
+  )) %>%
+  kable_styling(full_width = FALSE)
+
 ```
@@
 -   **respondent_understood_binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:
+
     -   *Understood*: Respondents who provided clear and accurate answers, indicating full comprehension of the questions.
@@
 -   **interview_conduct_method**: The method by which the interview was conducted, with the following possible categories:
+
     -   *Face-to-face*: In-person interviews conducted by the surveyor.
@@
 -   **child_interference**: Indicates whether interruptions by children occurred during the interview, with binary values:
+
     -   *Yes*: The interview was interrupted by children.
@@
 -   **partner_interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:
+
     -   *Yes*: The interview was interrupted by the respondent's partner.
@@
 -   **question_clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:
+
     -   *Yes*: The respondent asked for clarification.
@@
 -   **respondent_reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:
+
     -   *Not reluctant*: The respondent showed no signs of hesitation.
@@
 -   **interviewer_gender**: The gender of the interviewer, categorized as:
+
     -   *Male*: Interviews conducted by male interviewers.
@@
 Detailed insights into the distribution of interviewer age across different countries are visualized in Figure 1, which presents the density plot of interviewer age for the top five countries in the dataset.
+
 ```{r}
@@
 This visualization provides an overview of the age composition of interviewers across these countries, offering useful context for understanding potential differences in survey implementation.
+
 ```{r}
@@
 ```
+
 @fig-interference_frequency illustrates the frequency of interference during interviews across different levels of respondents’ effort, as measured by the variable "Respondent Tried Best." The bar plot shows the proportion of interviews with and without interference for each effort level, ranging from 1 (low effort) to 5 (high effort) and an additional "Other" category.
@@
 ```
-- **@fig-ridgeline_interviewer_age** shows a ridgeline plot of interviewer age distributions across different levels of question clarification requests. 
+
+-   @fig-ridgeline_interviewer_age shows a ridgeline plot of interviewer age distributions across different levels of question clarification requests.
 -   The x-axis represents interviewer age, while the y-axis categorizes responses by clarification levels (1 to 5) and an "Other" group.
@@
 ### Key Observations:
+
 -   Interviewers aged 40 to 50 are prominent in levels 4 and 5, showing higher densities in these groups.
@@
 
-# Model
+### Model Set-up
 
-The goal of our modelling strategy is twofold. Firstly,...
+Let $y_i$be the ordered categorical variable representing whether the respondent fully understood the survey questions for the $i$ -th interview. The predictors in the model include:
 
-Here we briefly describe the Bayesian analysis model used to investigate... Background details and diagnostics are included in [Appendix -@sec-model-details].
+-   $\beta_1$: The coefficient for **interview_conduct_method**, representing the type of interview conducted. This variable includes different categories such as:
 
-## Model set-up
+    -   Method 2
+    -   Method 3
+    -   Method 9
+    -   (other possible interview methods)
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+-   $\beta_2$: The coefficient for **partner_interference**, representing different levels of interference by the respondent's partner. Categories include:
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
+    -   Partner Interference Level 1
+    -   Partner Interference Level 2
+    -   (other possible levels of interference)
+
+-   $\beta_3$: The coefficient for **child_interference**, indicating different levels of interference by children during the interview. This variable includes:
+
+    -   Child Interference Level 1
+    -   Child Interference Level 2
+    -   (other possible levels of interference)
+
+-   $\beta_4$: The coefficient for **parent_interference**, indicating different levels of interference by the respondent's parents.
+
+-   $\beta_5$: The coefficient for **relative_interference**, representing interference by other relatives.
+
+-   $\beta_6$: The coefficient for **non_relative_interference**, indicating whether interference was caused by non-relatives.
+
+-   $\beta_7$: The coefficient for **interviewer_age**, which is a continuous variable representing the age of the interviewer.
+
+-   $\beta_8$: The coefficient for **interviewer_gender**, indicating the gender of the interviewer:
+
+    -   Male
+    -   Female
+
+-   $\beta_9$: The coefficient for **country** (as a factor), representing the country where the interview took place. The variable includes multiple countries.
+
+-   $\beta_{10}$: The coefficient for **question_clarification**, indicating whether the respondent requested clarification during the interview. It includes multiple levels, such as:
+
+    -   Clarification Level 2
+    -   Clarification Level 3
+    -   Clarification Level 4
+    -   Clarification Level 5
+    -   (other possible levels of clarification)
+
+-   $\beta_{11}$: The coefficient for **respondent_reluctant**, representing the level of reluctance shown by the respondent. Categories include:
+
+    -   Reluctant Level 2
+    -   Reluctant Level 3
+    -   Reluctant Level 4
+    -   Reluctant Level 5
+    -   (other possible levels of reluctance)
+
+-   $\beta_{12}$: The coefficient for **respondent_tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
+
+    -   Tried Best Level 2
+    -   Tried Best Level 3
+    -   Tried Best Level 4
+    -   Tried Best Level 5
+    -   (other possible levels of effort)
+
+Each coefficient $\beta_j$ represents the effect of the $j$-th predictor on the log-odds of the respondent understanding the survey questions.
+
+-   $\eta_i$: The linear predictor or log-odds for the $i$-th observation, calculated by combining the intercept and the coefficients for each predictor variable.
+
+-   $\kappa$: The set of thresholds (or cutpoints) that define the boundaries between the ordered categories of the outcome variable.
+In the ordered logistic regression model, these thresholds determine the ranges of $\eta_i$ values corresponding to each category of respondent understanding.
+The model estimates separate $\kappa$ values for each boundary between the ordered categories.
+
+The model is specified as follows for ordered logistic regression:\begin{align}
+y_i &\sim \text{OrderedLogistic}(\eta_i, \kappa) \\
+\eta_i &= \beta_0 + \beta_{\text{interview\_conduct\_method}} \times \text{interview\_conduct\_method}_i \notag \\
+       &\quad + \beta_{\text{partner\_interference}} \times \text{partner\_interference}_i \notag \\
+       &\quad + \beta_{\text{child\_interference}} \times \text{child\_interference}_i 
+       + \beta_{\text{parent\_interference}} \times \text{parent\_interference}_i \notag \\
+       &\quad + \beta_{\text{non\_relative\_interference}} \times \text{non\_relative\_interference}_i 
+       + \beta_{\text{interviewer\_age}} \times \text{interviewer\_age}_i \notag \\
+       &\quad + \beta_{\text{interviewer\_gender}} \times \text{interviewer\_gender}_i 
+       + \beta_{\text{country}} \times \text{country}_i \notag \\
+       &\quad + \beta_{\text{question\_clarification}} \times \text{question\_clarification}_i 
+       + \beta_{\text{respondent\_reluctant}} \times \text{respondent\_reluctant}_i \notag \\
+       &\quad + \beta_{\text{respondent\_tried\_best}} \times \text{respondent\_tried\_best}_i \\
+\beta &\sim \text{Normal}(0, 10) \quad (\text{default non-informative prior}) \\
+\kappa &\sim \text{Normal}(0, 5) \quad (\text{default prior for cutpoints})
 \end{align}
 
-We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.
+Where:
+
+-   $\beta_0$ is the intercept of the model.
+-   $\beta \sim \text{Normal}(0, 10)$: Represents a non-informative prior for the regression coefficients.
+-   $\kappa \sim \text{Normal}(0, 5)$: Represents the prior for thresholds.
+
+This model is designed to examine how different types of interference, interviewer characteristics, and respondent behaviors impact whether the respondent understood the survey questions, considering the ordered nature of the response.
+
+## Prior distributions
+
+In the Bayesian logistic regression model implemented using the `rstanarm` package, default prior distributions are applied to the model parameters to ensure robustness and reliability in inference.
+These priors are designed to balance the need for appropriate regularization with the flexibility to let the data guide the modeling:
+
+-   **Intercept Priors**: For the intercept of the model, we use a normal prior distribution with a mean of 0 and a relatively large standard deviation, reflecting weakly informative priors.
+This choice helps stabilize the intercept term without imposing a strong prior belief, allowing the model to be flexible across diverse datasets.
+
+-   **Coefficient Priors**: Coefficients in the model are assigned normal prior distributions, also with a mean of 0 but with a smaller standard deviation, typically set around 2.5.
+This helps prevent the individual predictors from exerting overly large influences unless strongly supported by the data.
+For example, variables such as different types of interference (e.g., partner, child, parent) or interview methods benefit from such priors as they maintain moderate regularization to avoid overfitting.
+
+We ran the model in R using the `rstanarm` package (Team, 2021).
+The default priors from `rstanarm` provide an appropriate level of smoothing and regularization, making the model applicable to survey data with complex patterns while still allowing the data to reveal meaningful relationships, especially concerning factors that affect response quality.
 
@@
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+Existing research in survey methodology and social sciences suggests that factors such as interview method, the presence of disruptions during interviews, interviewer characteristics, and respondent behaviors significantly affect the quality of survey responses.
+In interviews with fewer disruptions, respondents are more likely to provide accurate and reliable answers.
+However, disruptions from various sources, such as partners, children, relatives, or even non-relatives, can compromise response quality.
+Additionally, interviewer characteristics—such as age and gender—may influence how comfortable respondents feel, which in turn affects the quality of their responses.
+The method of conducting the interview (e.g., face-to-face, phone, or self-administered) also plays a role in determining the overall effectiveness of data collection.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+A Bayesian hierarchical logistic regression model was chosen for this analysis because the dependent variable, respondent_understood_binary, is binary in nature, indicating whether the respondent fully understood the survey questions.
+Logistic regression is a suitable approach when dealing with binary outcomes, and the Bayesian aspect helps in incorporating prior information and managing uncertainty in model parameters.
+This approach allows us to estimate the effect of various predictors—such as interview method, interference levels, and respondent reluctance—on the likelihood of understanding survey questions, providing a clear interpretation of how each factor contributes to the response quality.
 
-# Results
+The use of Bayesian hierarchical logistic regression is further justified because it allows the model to adapt flexibly to the data structure and manage potential variability across different interview scenarios.
+For example, the presence of multiple types of disruptions—each with different possible levels—requires a model that can adequately account for such hierarchical data structures.
+Additionally, Bayesian methods provide a framework for incorporating uncertainty and variability in interviewer and respondent characteristics, thereby giving a more nuanced and informed estimation.
+This model choice aligns well with established practices in survey research, where complex interaction effects and varying levels of measurement need to be addressed thoughtfully to ensure valid inferences about the factors influencing survey data quality.
 
-Our results are summarized in @tbl-modelresults.
+# Results and interpretation
+
+The Bayesian hierarchical logistic regression model was fitted using our training dataset, comprising 9,743 observations and 25 variables, to estimate factors that influence whether respondents fully understood the survey questions.
+@tbl-summary-model presents the summary of the model's key coefficients, including posterior mean estimates and credible intervals for each parameter, providing insights into the impact of interview disruptions, interviewer characteristics, and survey methods on response quality.
+
+### Key Findings from the Coefficients
+
+The analysis reveals that different types of disruptions and characteristics of the interview environment have a distinct impact on respondents’ comprehension of survey questions.
+Here are some of the key findings:
+
+-   **Interview Method**: Interview Method 9 was found to have an exceptionally large effect (Mean = 95.1), indicating it significantly improves the likelihood that respondents understand the questions.
+Conversely, other interview methods such as **Method 2** and **Method 3** had moderate effects, suggesting that the effectiveness of an interview style can vary substantially based on how it is implemented.
+
+-   **Disruptions During the Interview**:
+
+    -   **Partner Interference** had a negative effect on the quality of responses (Mean = -0.6).
+This indicates that the presence of a partner during the interview tends to lower the ability of the respondent to fully understand and accurately respond.
+    -   **Child Interference** and **Parent Interference** also showed notable negative impacts (Means = -0.8 and -1.6 respectively), highlighting that family-related disruptions can significantly hinder the respondent’s ability to provide reliable answers.
+    -   Interestingly, **Non-relative Interference** was associated with a positive effect (Mean = 1.0), suggesting that such disruptions may not be as distracting or might even motivate respondents to be more attentive.
+
+-   **Country Effects**: The model also included a factor for **country** to account for geographic variability in survey conditions.
+The results show variability in respondent comprehension across different countries.
+For instance:
+
+    -   **Germany (DE)** and **Hungary (HU)** had negative coefficients, indicating lower response comprehension in these countries.
+    -   In contrast, **Finland (FI)** showed neutral effects, reflecting possibly consistent survey conditions in that country.
+
+-   **Question Clarification**: Levels of **question clarification** were consistently found to negatively affect response quality.
+For example, **Clarification Level 4** had a mean of -3.0, implying that respondents requiring repeated clarification were less likely to fully understand the questions.
+
+-   **Respondent Reluctance**: Increased **respondent reluctance** also had a detrimental effect on comprehension.
+For example, **Reluctant Level 3** had a mean coefficient of -0.6, indicating hesitation or reluctance results in poorer quality responses.
+
+### Summary and Interpretation
+
+As detailed in @tbl-summary-model, the summary of coefficients provides a quantitative perspective on how each factor contributes to whether respondents fully understand survey questions. Notably:
+
+-   **Parental Interference** displayed the most substantial negative impact (Mean = -1.6), indicating that the presence of parents during an interview session significantly reduces comprehension levels.
+This suggests that minimizing parental presence could enhance the quality of responses.
+-   Conversely, **Non-relative Interference** was associated with a positive effect on understanding (Mean = 1.0), implying that some types of outside influence might actually promote a more careful engagement with the questions, perhaps because respondents feel more observed or responsible for their responses.
 
 ```{r}
+#| label: tbl-summary-model
+#| tbl-cap: "Summary of key coefficients from the Bayesian hierarchical logistic regression model analyzing survey response quality"
 #| echo: false
-#| eval: true
 #| warning: false
-#| message: false
-
 library(rstanarm)
@@
 first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+  readRDS(file = here::here("models/model.rds"))
+summary <- summary(first_model)
+
+summary_table <- head(summary, 10)[, 1:1]
+
+kable(col.names = c(" ", "coefficient"),
+  summary_table, digits = 3)
 ```
@@
 ```{r}
+#| label: fig-coefficient-intervals
+#| fig-cap: "The 90% credible intervals for all model coefficients from the Bayesian hierarchical logistic regression"
 #| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
+#| fig.width: 8
+#| fig.height: 6
 
-modelsummary::modelsummary(
-  list(
-    "First model" = first_model
-  ),
-  statistic = "mad",
-  fmt = 2
+model_summary <- tidy(first_model, conf.int = TRUE, conf.level = 0.90)
+
+important_parameters <- c(
+  "interview_conduct_method2", 
+  "partner_interference1", 
+  "child_interference1",
+  "parent_interference1", 
+  "non_relative_interference1", 
+  "interviewer_gender2", 
+  "interviewer_age"
 )
+
+filtered_summary <- model_summary[model_summary$term %in% important_parameters, ]
+
+ggplot(filtered_summary, aes(x = estimate, y = term)) +
+  geom_point(size = 3, color = "blue") +
+  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), height = 0.3, color = "blue") +
+  labs(
+    title = "Model Coefficients",
+    subtitle = "90% credible intervals",
+    x = "Coefficient Estimate",
+    y = "Parameters"
+  ) +
+  theme_minimal() +
+  xlim(-4, 4) 
 ```
+
+The Bayesian hierarchical logistic regression model's estimates are visualized in @fig-coefficient-intervals.
+Each point on the plot represents the estimated mean effect size of the predictor variables on the likelihood that the respondent understood the questions well, while the lines indicate the 90% credible intervals.
+These estimates reveal several key insights regarding factors that affect response quality in survey interviews:
+
+The variable partner_interference1 has a significant negative effect, indicating that when a partner is present during the interview, the quality of the respondent's understanding tends to decrease.
+This might be due to partners interrupting or distracting the respondent, which lowers their focus.
+
+The variable non_relative_interference1 shows the highest positive effect among the predictors, suggesting that interference from non-family members can sometimes enhance the respondent's performance.
+This could be due to increased formality or caution when responding in the presence of outsiders, leading to more careful answers.
+
+The variable interviewer_gender2 exhibits a slight negative effect, implying that female interviewers may encounter lower respondent understanding under certain conditions.
+However, the wide credible interval suggests that more data is needed to definitively determine the significance of this effect.
+
+interview_conduct_method2 also displays a negative effect, indicating that certain interview methods (such as telephone interviews) might not facilitate respondent comprehension as effectively as face-to-face methods.
+
+interviewer_age has an estimated effect close to zero with a broad credible interval, suggesting that interviewer age does not have a substantial influence on respondent understanding.
+
+These findings highlight the importance of considering the type of interference during interviews and specific characteristics of interviewers.
+It is evident that some types of disturbances and interview formats could significantly affect the reliability of collected data.
+By mitigating negative factors such as partner interference and selecting appropriate interview methods, the quality of survey data can be substantially improved, leading to more reliable conclusions in social survey research.
+
+Copy code
 
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 
@@
 
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheckandposteriorvsprior
-#| layout-ncol: 2
-#| fig-cap: "Examining how the model fits, and is affected by, the data"
-#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-
-posterior_vs_prior(first_model) +
-  theme_minimal() +
-  scale_color_brewer(palette = "Set1") +
-  theme(legend.position = "bottom") +
-  coord_flip()
-```
-
 ## Diagnostics
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| message: false
-#| warning: false
-#| label: fig-stanareyouokay
-#| fig-cap: "Checking the convergence of the MCMC algorithm"
-#| fig-subcap: ["Trace plot", "Rhat plot"]
-#| layout-ncol: 2
-
-plot(first_model, "trace")
-
-plot(first_model, "rhat")
-```
-
 \newpage

### 2024-11-25 scripts/05-exploratory_data_analysis.R
update eda and model

@@ -10,6 +10,7 @@
 library(tidyverse)
 library(GGally)
 library(ggplot2)
+library(dplyr)
 
 
 # Load the dataset
@@ -18,76 +19,9 @@ analysis_data <- read_csv("data/02-analysis_data/analysis_data.csv")
 # Set theme for better aesthetics
 theme_set(theme_minimal())
 
-# Plot 1: Distribution of Interviewer Age
-ggplot(analysis_data, aes(x = interviewer_age)) +
-  geom_histogram(bins = 20, fill = "skyblue", color = "black") +
-  labs(title = "Distribution of Interviewer Age", x = "Interviewer Age", y = "Count")
-
-# Plot 2: Distribution of Respondent Understanding
-ggplot(analysis_data, aes(x = respondent_understood)) +
-  geom_histogram(bins = 20, fill = "lightgreen", color = "black") +
-  labs(title = "Distribution of Respondent Understanding", x = "Respondent Understanding", y = "Count")
-
-# Plot 3: Interview Conduct Method vs Respondent Understanding
-ggplot(analysis_data, aes(x = interview_conduct_method, y = respondent_understood)) +
-  geom_boxplot(fill = "lightblue") +
-  labs(title = "Interview Conduct Method vs Respondent Understanding", x = "Conduct Method", y = "Respondent Understanding") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-# Plot 4: Country vs Respondent Understanding (Top 10 countries)
-top_countries <- analysis_data %>% 
-  count(country, sort = TRUE) %>% 
-  top_n(10) %>% 
-  pull(country)
-
-filtered_data <- analysis_data %>% 
-  filter(country %in% top_countries)
-
-ggplot(filtered_data, aes(x = country, y = respondent_understood)) +
-  geom_boxplot(fill = "lightpink") +
-  labs(title = "Country-wise Respondent Understanding (Top 10 Countries)", x = "Country", y = "Respondent Understanding") +
-  theme(axis.text.x = element_text(angle = 45, hjust = 1))
-
-# Plot 5: Relationship between Interviewer Age and Respondent Understanding
-ggplot(analysis_data, aes(x = interviewer_age, y = respondent_understood)) +
-  geom_point(alpha = 0.6) +
-  geom_smooth(method = "lm", color = "red") +
-  labs(title = "Interviewer Age vs Respondent Understanding", x = "Interviewer Age", y = "Respondent Understanding")
-
[…]

### 2024-11-25 scripts/06-model_data.R

@@ -14,7 +14,7 @@ library(tidyverse)
 library(rstanarm)
 library(arrow)
 library(car)
-library(brms)›
+library(brms)
 
 #### Read data ####
 analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")
@@ -32,9 +32,9 @@ model <-
     seed = 853
   )
 
-
-vif(model)
 summary(model)
+
+
 
 #### Save model ####
 saveRDS(

### 2024-11-25 paper/paper.qmd
update paper

@@
 library(kableExtra)
+library(car)
+library(loo)
 ```
@@
 
+# Random sampling if needed
 set.seed(131)
@@
 
-# Select important columns from both metadata and model variables
+# Select important variables from the model
 important_columns <- c(
-  "dataset_title", "ess_round", "edition_number", "production_date", "country", "respondent_id",
   "interview_conduct_method", "partner_interference", "child_interference",
   "parent_interference", "relative_interference", "non_relative_interference",
-  "interviewer_age", "interviewer_gender", "question_clarification",
+  "interviewer_age", "interviewer_gender", "country", "question_clarification",
   "respondent_reluctant", "respondent_tried_best"
@@
   kable(booktabs = TRUE, align = "c", col.names = c(
-    "Dataset Title", "ESS Round", "Edition Number", "Production Date", "Country", "Respondent ID",
-    "Interview Method", "Partner Interference", "Child Interference", "Parent Interference",
-    "Relative Interference", "Non-relative Interference", "Interviewer Age",
-    "Interviewer Gender", "Question Clarification", "Respondent Reluctant", "Respondent Tried Best"
+    "Interview Method", "Partner Interference", "Child Interference",
+    "Parent Interference", "Relative Interference", "Non-relative Interference",
+    "Interviewer Age", "Interviewer Gender", "Country",
+    "Question Clarification", "Respondent Reluctant", "Respondent Tried Best"
   )) %>%
@@
 ```{r}
+#| label: fig-response_understanding_effort_level
+#| fig-cap: "Bar Plot of Response Understanding by Respondent Effort Level"
+#| echo: false
+#| fig.width: 8
+#| fig.height: 6
+
+ggplot(analysis_data, aes(x = respondent_tried_best, fill = respondent_understood_binary)) +
+  geom_bar(position = "fill") +
+  scale_fill_manual(values = c("#619CFF", "#F8766D")) +
+  labs(
+    title = "Bar Plot of Response Understanding by Respondent Tried Best",
+    x = "Respondent Tried Best",
+    y = "Proportion",
+    fill = "Response Understanding"
+  ) +
+  theme_minimal()
+
+```
+
+@fig-response_understanding_effort_level Figure 2 illustrates the relationship between respondents' effort levels, as represented by "Respondent Tried Best," and their understanding of survey questions.
+The x-axis indicates different levels of effort, ranging from 1 (low effort) to 5 (high effort), along with an additional "Other" category.
+The y-axis shows the proportion of respondents who either understood or did not understand the survey questions.
+
+From the bar plot, it is apparent that understanding levels vary slightly across different effort categories.
+In general, as the effort level increases, the proportion of respondents who understood the questions tends to be higher.
+Notably, effort levels 1, 2, and 3 exhibit a relatively higher portion of respondents who did not understand compared to effort levels 4 and 5, which show a more balanced distribution.
+The "Other" category presents a distinct pattern, differing slightly from the other effort levels.
+This visualization provides insight into how the level of effort during interviews corresponds to the respondents' comprehension of the questions asked.
+
+```{r}
 #| label: fig-interference_frequency
@@
 #| echo: false
+#| warning: false
 #| fig.width: 8
 #| fig.height: 6
+#|
 
@@
 
-@fig-interference_frequency illustrates the frequency of interference during interviews across different levels of respondents’ effort, as measured by the variable "Respondent Tried Best." The bar plot shows the proportion of interviews with and without interference for each effort level, ranging from 1 (low effort) to 5 (high effort) and an additional "Other" category.
+@fig-interference_frequency illustrates the frequency of interference during interviews across different levels of respondents' effort, as measured by the variable "Respondent Tried Best."
+
+The bar plot shows the proportion of interviews with and without interference for each effort level, ranging from 1 (low effort) to 5 (high effort), along with an additional "Other" category.
 
@@
 Higher levels of effort (e.g., 4 and 5) tend to have a similar distribution of interference presence, while the "Other" category shows a slightly lower proportion of interference.
+
 This visualization provides an overview of how respondent effort and the presence of interference interact in the dataset.
-
-```{r}
-#| label: fig-ridgeline_interviewer_age
-#| fig-cap: "Ridgeline Plot of Interviewer Age by Question Clarification Level"
-#| echo: false
-#| fig.width: 8
-#| fig.height: 6
-#| 
-ggplot(analysis_data, aes(x = interviewer_age, y = as.factor(question_clarification), fill = ..x..)) +
-  geom_density_ridges_gradient() +
-  scale_fill_viridis_c() +
-  labs(
-    title = "Ridgeline Plot of Interviewer Age by Question Clarification Level",
-    x = "Interviewer Age",
-    y = "Question Clarification Level"
-  ) +
-  theme_minimal()
-
-```
-
--   @fig-ridgeline_interviewer_age shows a ridgeline plot of interviewer age distributions across different levels of question clarification requests.
--   The x-axis represents interviewer age, while the y-axis categorizes responses by clarification levels (1 to 5) and an "Other" group.
--   Each ridge represents the density distribution of interviewer age for a specific clarification level.
--   Lighter colors indicate higher densities within the corresponding age range.
 
@@
 
-Copy code
-
 # Discussion
 
-## First discussion point {#sec-first-point}
+This analysis employed a Bayesian logistic regression model to investigate factors influencing respondents' comprehension during interviews.
+By incorporating various types of interference, interview methods, and respondent characteristics, the model elucidates how these variables impact understanding during social survey interviews.
 
-If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.
+## Factors Affecting Response Comprehension
 
-## Second discussion point
+The model analysis reveals that different types of interference significantly affect respondents' comprehension during interviews.
+Notably, partner and child interference have a negative impact on understanding.
+For example, the coefficient for partner interference is significantly negative (mean = -0.6), suggesting that the presence of a partner may hinder a respondent's full comprehension of the questions.
+This finding aligns with previous research, indicating that social pressure or disturbances from nearby individuals can negatively impact respondents' attention during surveys.
 
-Please don't use these as sub-heading labels - change them to be what your point actually is.
+In contrast, interviewer characteristics, such as gender, show little effect on comprehension.
+This suggests that while environmental and relational interference plays a crucial role, interviewer attributes do not significantly influence respondents' comprehension in the context of this study.
 
-## Third discussion point
+## Implications for Managing Interview Interference**
 
-## Weaknesses and next steps
+The strategic implication of these findings is that managing the interview environment is crucial for improving data quality.
+Since partner and child interference are associated with a reduced likelihood of comprehension, measures should be considered to minimize such disruptions.
+This might include conducting interviews in a more private setting or explicitly instructing respondents to minimize interruptions during the interview.
 
-Weaknesses and next steps should also be included.
+Variables related to the interview method also show significant impact.
+The coefficient for “interview_conduct_method3” is positive, indicating that certain specific methods, possibly involving higher levels of interaction or explanation, contribute to improved comprehension.
+This implies that training interviewers to adopt methods that emphasize clarity and engagement could enhance respondents' understanding, even in the presence of interference.
+
+## Limitations and Areas for Improvement**
+
+A key limitation of the model is the generalizability of its findings, particularly regarding different population groups.
+The current dataset may not capture all cultural or socioeconomic factors that could influence comprehension.
+For instance, while country-level effects are included, many of these effects are either negative or negligible, suggesting that unmeasured factors may explain differences between regions.
+
+Additionally, the model's predictive performance, assessed through the Bayesian R-squared value, is moderate (mean R² around 0.32).
+This indicates that while the model accounts for some variability in response comprehension, a substantial amount remains unexplained.
+Future research could incorporate additional variables, such as respondents' education levels or prior survey experience, to enhance model fit and explanatory power.
+
+## Future Research Directions**
+
+Building on these findings, future research could explore more granular aspects of interference, such as the intensity or duration of disruptions.
+Understanding whether brief interruptions have a different effect compared to prolonged interference could help develop more precise guidelines for survey management.
+
+Further research could also examine interaction effects between variables, such as how partner interference affects respondents with varying levels of willingness to participate.
+This could unveil more targeted strategies to improve survey conditions, ultimately leading to higher data reliability.
+
+## Practical Insights for Survey Management**
+
+The results of this analysis underscore the importance of optimizing survey conditions to enhance respondent comprehension.
+Minimizing interference and adopting effective interview methods can significantly improve the quality of collected data.
+Survey administrators might consider providing pre-interview guidance to help respondents reduce disruptions and training interviewers in techniques proven to enhance comprehension.
+
+The significance of certain variables, such as partner interference, also highlights the complexity of social dynamics during surveys.
+Addressing these dynamics is crucial for ensuring the accuracy of survey results, which directly impacts the validity of conclusions drawn from the data.
+
+Overall, the study provides actionable insights into how survey administrators can better structure interview conditions to mitigate interference and enhance respondent understanding, thereby improving the reliability and validity of survey data.
 
@@
 
+## Prediction
+```{r}
+#| echo: false
+#| warning: false
+analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
+analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
+factor_vars <- c("interview_conduct_method", "partner_interference", "child_interference",
+                 "parent_interference", "relative_interference", "non_relative_interference",
+                 "country", "interviewer_gender", "question_clarification", "respondent_reluctant",
+                 "respondent_tried_best")
+
+# Iterate through factor variables and set the factor levels in test data to be consistent with train data
+for (var in factor_vars) {
+  if (is.factor(analysis_data_train[[var]])) {
+    # Set factor levels in test data to match those in train data
+    analysis_data_test[[var]] <- factor(analysis_data_test[[var]], levels = levels(analysis_data_train[[var]]))
+  }
+}
+
+# Predict probabilities and convert predicted_class to "Understood" and "Not_understood"
+predicted_prob <- predict(first_model, newdata = analysis_data_test, type = "response")
+analysis_data_test$predicted_class <- ifelse(predicted_prob > 0.5, "Understood", "Not_understood")
+
+# Convert predicted_class and respondent_understood_binary to factors with consistent levels
+analysis_data_test$predicted_class <- factor(analysis_data_test$predicted_class, levels = c("Not_understood", "Understood"))
+analysis_data_test$respondent_understood_binary <- factor(analysis_data_test$respondent_understood_binary, levels = c("Not_understood", "Understood"))
+
+# Display table of prediction results
+table(analysis_data_test$predicted_class)
+table(analysis_data_test$respondent_understood_binary)
+
+# Import caret library and calculate confusion matrix
+library(caret)
+
+confusion_matrix <- confusionMatrix(
+  analysis_data_test$predicted_class,
+  analysis_data_test$respondent_understood_binary
+)
+
+# Print the confusion matrix
+print(confusion_matrix)
+
+scatter_data <- data.frame(
+  Actual = analysis_data_test$respondent_understood_binary,
+  Predicted = analysis_data_test$predicted_class
+)
+
+ggplot(scatter_data, aes(x = Actual, y = Predicted)) +
+  geom_jitter(width = 0.2, height = 0.2, alpha = 0.5, color = "blue") +
+  labs(
+    title = "Scatter Plot of Actual vs Predicted Values",
+    x = "Actual Response Understanding",
+    y = "Predicted Response Understanding"
+  ) +
+  theme_minimal()
+
+```
+## Validation
+```{r}
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")
+vif(first_model)
+
+residuals <- residuals(first_model, type = "response")
+hist(residuals, main = "Residual Histogram", xlab = "Residuals")
+
+r2_values <- bayes_R2(first_model)
+r2_df <- data.frame(Index = 1:length(r2_values), R2 = r2_values)
+
+ggplot(r2_df, aes(x = Index, y = R2)) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  labs(title = "Bayesian R^2 Metrics for first_model Observations", x = "Observation Index", y = "R^2 Value") +
+  theme_minimal()
+
+# Perform LOO cross-validation and assign to loo_results
+loo_results <- loo(first_model)
+# Extract Pareto k values from loo results and plot
+pareto_k <- loo_results$diagnostics$pareto_k
+pareto_k_df <- data.frame(Index = 1:length(pareto_k), Pareto_k = pareto_k)
+
+ggplot(pareto_k_df, aes(x = Index, y = Pareto_k)) +
+  geom_bar(stat = "identity", fill = "orange") +
+  geom_hline(yintercept = 0.7, linetype = "dashed", color = "red") +
+  labs(title = "Pareto k Diagnostic Values", x = "Observation Index", y = "Pareto k Value") +
+  theme_minimal()
+
+loo_df <- data.frame(Observation = 1:length(loo_results$pointwise[,"elpd_loo"]),
+                     ELPD_LOO = loo_results$pointwise[,"elpd_loo"])
+
+ggplot(loo_df, aes(x = Observation, y = ELPD_LOO)) +
+  geom_point(color = "darkgreen") +
+  geom_smooth(method = "loess", color = "red", se = FALSE) +
+  labs(title = "Leave-One-Out Cross Validation (ELPD_LOO)", x = "Observation Index", y = "ELPD_LOO") +
+  theme_classic()
+```
+
 # References

### 2024-11-26 paper/paper.qmd
update paper of validation and model details

@@
 
-## Implications for Managing Interview Interference**
+## Implications for Managing Interview Interference
 
@@
 
-## Limitations and Areas for Improvement**
+## Limitations and Areas for Improvement
 
@@
 
-## Future Research Directions**
+## Future Research Directions
 
@@
 
-## Practical Insights for Survey Management**
+## Practical Insights for Survey Management
 
@@
 ## Posterior predictive check
+###Validation
+```{r}
+#| echo: false
+#| warning: false
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")+ xlim(-0.1, 1.2)
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+vif(first_model)
 
-## Diagnostics
+residuals <- residuals(first_model, type = "response")
+hist(residuals, main = "Residual Histogram", xlab = "Residuals")
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+r2_values <- bayes_R2(first_model)
+r2_df <- data.frame(Index = 1:length(r2_values), R2 = r2_values)
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+ggplot(r2_df, aes(x = Index, y = R2)) +
+  geom_bar(stat = "identity", fill = "steelblue") +
+  labs(title = "Bayesian R^2 Metrics for first_model Observations", x = "Observation Index", y = "R^2 Value") +
+  theme_minimal()
 
-\newpage
+# Perform LOO cross-validation and assign to loo_results
+loo_results <- loo(first_model)
+# Extract Pareto k values from loo results and plot
+pareto_k <- loo_results$diagnostics$pareto_k
+pareto_k_df <- data.frame(Index = 1:length(pareto_k), Pareto_k = pareto_k)
+
+ggplot(pareto_k_df, aes(x = Index, y = Pareto_k)) +
+  geom_bar(stat = "identity", fill = "orange") +
+  geom_hline(yintercept = 0.7, linetype = "dashed", color = "red") +
+  labs(title = "Pareto k Diagnostic Values", x = "Observation Index", y = "Pareto k Value") +
+  theme_minimal()
+
+loo_df <- data.frame(Observation = 1:length(loo_results$pointwise[,"elpd_loo"]),
+                     ELPD_LOO = loo_results$pointwise[,"elpd_loo"])
+
+ggplot(loo_df, aes(x = Observation, y = ELPD_LOO)) +
+  geom_point(color = "darkgreen") +
+  geom_smooth(method = "loess", color = "red", se = FALSE) +
+  labs(title = "Leave-One-Out Cross Validation (ELPD_LOO)", x = "Observation Index", y = "ELPD_LOO") +
+  theme_classic()
+```
 
@@
 ```
-## Validation
-```{r}
 
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")
-vif(first_model)
+## Diagnostics
 
-residuals <- residuals(first_model, type = "response")
-hist(residuals, main = "Residual Histogram", xlab = "Residuals")
-
-r2_values <- bayes_R2(first_model)
-r2_df <- data.frame(Index = 1:length(r2_values), R2 = r2_values)
-
-ggplot(r2_df, aes(x = Index, y = R2)) +
-  geom_bar(stat = "identity", fill = "steelblue") +
-  labs(title = "Bayesian R^2 Metrics for first_model Observations", x = "Observation Index", y = "R^2 Value") +
-  theme_minimal()
-
-# Perform LOO cross-validation and assign to loo_results
-loo_results <- loo(first_model)
-# Extract Pareto k values from loo results and plot
-pareto_k <- loo_results$diagnostics$pareto_k
-pareto_k_df <- data.frame(Index = 1:length(pareto_k), Pareto_k = pareto_k)
-
-ggplot(pareto_k_df, aes(x = Index, y = Pareto_k)) +
-  geom_bar(stat = "identity", fill = "orange") +
-  geom_hline(yintercept = 0.7, linetype = "dashed", color = "red") +
-  labs(title = "Pareto k Diagnostic Values", x = "Observation Index", y = "Pareto k Value") +
-  theme_minimal()
-
-loo_df <- data.frame(Observation = 1:length(loo_results$pointwise[,"elpd_loo"]),
-                     ELPD_LOO = loo_results$pointwise[,"elpd_loo"])
-
-ggplot(loo_df, aes(x = Observation, y = ELPD_LOO)) +
-  geom_point(color = "darkgreen") +
-  geom_smooth(method = "loess", color = "red", se = FALSE) +
-  labs(title = "Leave-One-Out Cross Validation (ELPD_LOO)", x = "Observation Index", y = "ELPD_LOO") +
-  theme_classic()
-```
+\newpage
 

### 2024-11-26 paper/paper.qmd
update paper and reference

@@
 library(loo)
+library(modelsummary)
 ```
 
-# Introduction
+# Introduction {#sec-intro}
 
@@
 Groves et al.
-(2009) examined the role of interviewer characteristics—such as experience and demeanor—in shaping the quality of responses through a multi-level modeling approach.
-In another key study, Couper and de Leeuw (2003) investigated how different modes of conducting interviews, like in-person versus telephone, influenced the comfort and attentiveness of respondents.
-Fowler and Mangione (1990) took a different approach by analyzing observational data to assess the impact of third-party presence during interviews.
+[@groves2011survey] examined the role of interviewer characteristics—such as experience and demeanor—in shaping the quality of responses through a multi-level modeling approach.
+In another key study, Couper and de Leeuw [@massey2013we] investigated how different modes of conducting interviews, like in-person versus telephone, influenced the comfort and attentiveness of respondents.
+Fowler and Mangione [@fowler1990standardized] took a different approach by analyzing observational data to assess the impact of third-party presence during interviews.
 Although these works laid a valuable foundation for understanding data quality, there remains a gap in systematically analyzing the distinct effects of various kinds of disruptions, such as familial or environmental interference, on respondent understanding and response accuracy.
@@
 
-The remainder of this paper is organized to present a comprehensive exploration of these topics.
-Section 2 provides a detailed overview of the dataset, focusing on the different variables and their role in assessing data quality.
+The paper is structured to offer an in-depth examination of the factors that affect respondent comprehension during social survey interviews.
+Following the introduction in @sec-intro, @sec-data provides a detailed overview of the dataset, focusing on the different variables and their role in assessing data quality.
 It also outlines the preprocessing steps taken, including data cleaning and the recoding of variables.
-Section 3 introduces the Bayesian logistic regression methodology, explaining the statistical approach and justifying the selection of priors for the analysis.
-In Section 4, we present the empirical findings, including parameter estimates and an interpretation of the relationships uncovered by the model.
-Section 5 discusses the practical implications of these findings, emphasizing the improvements needed in interviewer training and the strategies for reducing respondent interference.
-Finally, Section 6 summarizes the key contributions of this research, outlines the limitations, and suggests avenues for future work—particularly concerning the integration of new data collection technologies and adaptive survey designs aimed at mitigating the impact of disruptions on respondent data quality.
+@sec-model introduces the Bayesian logistic regression methodology, explaining the statistical approach and justifying the selection of priors for the analysis.
+In @sec-result, we present the empirical findings, including parameter estimates and an interpretation of the relationships uncovered by the model.
+@sec-discussion discusses the practical implications of these findings, emphasizing the improvements needed in interviewer training and the strategies for reducing respondent interference.
+Finally, @sec-model-details summarizes the key contributions of this research, outlines the limitations, and suggests avenues for future work—particularly concerning the integration of new data collection technologies and adaptive survey designs aimed at mitigating the impact of disruptions on respondent data quality.
 
@@
 
-We use the statistical programming language R (R Core Team 2023) to process, analyze, and visualize survey data exploring the impact of interview disruptions on response quality.
-The dataset used in this study includes several subsets tailored to different stages of the analysis, enabling a systematic and detailed examination of the research questions.
-The main dataset for modeling consists of 9,743 rows and 25 variables, capturing detailed information about different types of disruptions (e.g., partner, child, or relative interference), interview methods, and respondent characteristics.
+We use the statistical programming language R [@citeR] to process, analyze, and visualize survey data exploring the impact of interview disruptions on response quality.
+The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1), which collects information on societal attitudes and behaviors across multiple European countries.
+It includes several subsets tailored to different stages of the analysis, allowing a systematic examination of factors affecting survey response quality.
+The main dataset, used for modeling, consists of 9,743 rows and 25 variables.
+These data points capture details about various types of disruptions (e.g., partner, child, or relative interference), interview methods, and respondent characteristics.
+All responses are collected using standardized methods to ensure comparability across countries, thereby facilitating a detailed exploration of the impact of environmental factors, such as interruptions during interviews, on response quality.
 
-To ensure the reliability of the analysis, we filtered the data to exclude incomplete or ambiguous responses for key variables, such as missing values in "respondent_understood." Responses were also recoded into binary categories to focus on meaningful distinctions in response quality, while variables with excessive categories were grouped to improve interpretability.
+To ensure the reliability of the analysis, we filtered the data to exclude incomplete or ambiguous responses for key variables, such as missing values in "respondent_understood." Responses were also recoded into binary categories to focus on meaningful distinctions in response quality, while variables with excessive categories were grouped to improve interpretability.Different countries may implement localized adaptations in survey administration, which could influence response behaviors.
+To account for this, country-level metadata is included, allowing for the analysis of cross-national variations.
 These preprocessing steps were essential to refine the dataset and facilitate robust modeling.
 
-The following R packages were employed to streamline the data analysis workflow:
+The following R packages were utilized to facilitate and streamline the data analysis process:
 
--   **tidyverse** (Wickham et al. 2021): Used for efficient data manipulation, cleaning, and transformation. It includes:
+- **arrow** [@arrow]: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.
 
--   **dplyr** (Wickham, François, et al. 2021): For summarizing and managing complex datasets.
+- **knitr** [@knitr]: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.
 
--   **ggplot2** (Wickham 2021): For creating powerful and flexible visualizations.
+- **rstanarm** [@rstanarm]: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.
 
--   **rstanarm** (Team 2021): Facilitated the implementation of Bayesian models, enabling straightforward regression modeling using Stan.
+- **tidyverse** [@tidyverse]: A collection of R packages used for data manipulation, visualization, and cleaning, providing a unified structure to handle complex data workflows.
 
--   **arrow** (Apache Arrow 2021): Employed for efficiently reading and writing large datasets, enhancing data handling capabilities across systems.
+- **ggplot2** [@ggplot2]: Utilized for creating detailed visualizations, offering a flexible grammar of graphics to develop sophisticated charts and graphs.
 
--   **car** (Fox et al. 2021): Provided functions for regression diagnostics and other statistical analyses, particularly useful for checking assumptions and model validity.
+- **bayesplot** [@bayesplot]: Facilitates the visualization of Bayesian model results, useful for diagnostic checks and interpreting the results of Bayesian models.
 
--   **brms** (Bürkner 2021): A package for Bayesian regression modeling, which was used to implement more complex modeling approaches for the data.
+- **ggridges** [@ggridges]: Used to create ridge plots, which are useful for visualizing distributions, enhancing the exploration of posterior distributions from Bayesian models.
 
--   **rsample** (Kuhn 2021): Used for creating resampling datasets, ensuring robust model validation by facilitating cross-validation and bootstrapping techniques.
+- **broom.mixed** [@broom]: Extends the broom package to support models with random effects, summarizing mixed models in a tidy and interpretable format.
 
--   **janitor** (Firke 2021): Simplified data cleaning processes by helping manage variable names and data structures, making raw data easier to handle.
+- **kableExtra** [@kableExtra]: Enhances the basic table formatting capabilities of the 'knitr' package, providing additional functions for creating aesthetically pleasing and informative tables.
 
--   **GGally** (Schloerke et al.
-2021): Used to enhance ggplot2 visualizations by providing additional functions for correlation plots and pairwise visualizations, which are useful for exploratory data analysis.
-This study aims to provide practical insights into how various disruptions affect data quality in survey settings, helping to optimize survey design and execution in the future.
-\## Measurement
+- **car** [@car]: Used for regression diagnostics and statistical analysis, particularly valuable for testing assumptions and evaluating model quality.
 
-The data for this study is sourced from the European Social Survey (ESS), which collects information on societal attitudes and behaviors across multiple European countries.
-The dataset focuses on respondents’ understanding of survey questions, their cooperation levels, and the impact of environmental factors such as interruptions during interviews.
-All responses are collected using standardized methods to ensure comparability across countries.
+- **loo** [@loo]: Provides tools for leave-one-out cross-validation, which was crucial in assessing model performance and ensuring that the Bayesian models generalize well.
 
-Different countries may implement localized adaptations in survey administration, which could influence response behaviors.
-To account for this, country-level metadata is included, allowing for the analysis of cross-national variations.
+- **modelsummary** [@modelsummary]: Summarizes statistical models in a clear, tabular format, supporting the communication of regression and other model results.
+
+- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies in presenting data and statistical information.
 
@@
 #| echo: false
-#| label: tbl-aerial_preview
-#| tbl-cap: "Survey responses on the impact of interview disruptions across countries in social surveys"
+#| label: tbl-survey_preview
+#| tbl-cap: "Survey interview disruptions and factors influencing respondent comprehension"
 
@@
 important_columns <- c(
-  "interview_conduct_method", "partner_interference", "child_interference",
-  "parent_interference", "relative_interference", "non_relative_interference",
-  "interviewer_age", "interviewer_gender", "country", "question_clarification",
-  "respondent_reluctant", "respondent_tried_best"
-)
+  "respondent_understood_binary", "partner_interference", 
+  "parent_interference",  
+  "interviewer_age",  "country")
 
@@
   kable(booktabs = TRUE, align = "c", col.names = c(
-    "Interview Method", "Partner Interference", "Child Interference",
-    "Parent Interference", "Relative Interference", "Non-relative Interference",
-    "Interviewer Age", "Interviewer Gender", "Country",
-    "Question Clarification", "Respondent Reluctant", "Respondent Tried Best"
+     "respondent_understood_binary", "partner_interference", 
+  "parent_interference",  
+  "interviewer_age",  "country"
   )) %>%
@@
 ```
-
+@tbl-survey_preview presents the first six rows from the cleaned dataset, focusing on interview disruptions and respondent comprehension during social survey interviews.
 ## Outcome variables
@@
 From the plot, we can observe that interference is present across all effort levels, though its proportion varies slightly.
-Higher levels of effort (e.g., 4 and 5) tend to have a similar distribution of interference presence, while the "Other" category shows a slightly lower proportion of interference.
-
-This visualization provides an overview of how respondent effort and the presence of interference interact in the dataset.
-
-### Key Observations:
-
--   Interviewers aged 40 to 50 are prominent in levels 4 and 5, showing higher densities in these groups.
--   Clarification levels 1 and 2 show a broader distribution of interviewer ages, with no distinct peak.
--   The "Other" category exhibits a more balanced spread of ages, without significant density concentrations.
-
-This visualization highlights the distribution of interviewer age across clarification levels and provides insights into age-related patterns in survey interactions.
+Higher levels of effort (e.g., 4 and 5) tend to have a similar distribution of interference presence, while the "Other" category shows a slightly lower proportion of interference.This visualization provides an overview of how respondent effort and the presence of interference interact in the dataset.
 
@@
 After filtering and processing, the final dataset consists of **9,743 observations** and **25 variables**, structured to support a clear and concise examination of the study’s research objectives.
+
+# Model {#sec-model}
 
@@
 
-We ran the model in R using the `rstanarm` package (Team, 2021).
+We ran the model in R [@citeR] using the `rstanarm` package@rstanarm.
 The default priors from `rstanarm` provide an appropriate level of smoothing and regularization, making the model applicable to survey data with complex patterns while still allowing the data to reveal meaningful relationships, especially concerning factors that affect response quality.
@@
 
-# Results and interpretation
+# Results {#sec-result}
 
@@
 
-# Discussion
+# Discussion {#sec-discussion}
 
@@
 # Model details {#sec-model-details}
+## Model summary
+```{r}
+#| label: tbl-summary
+#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
+#| echo: false
+#| warning: false
+modelsummary(
+  list("Bayesian Logistic Regression" = first_model),
+  metrics = c("R2", "RMSE")
+)
+```
+@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews.
+The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels.
+Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension.
+In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.
+
+Additionally, non-relative interference, which shows a positive coefficient of 0.941, suggests that having individuals outside the immediate family present may be less disruptive, or even beneficial, for the comprehension of survey questions.
+Interviewer-related variables, such as "interviewer_gender," appear to have minimal effects on comprehension, as evidenced by small coefficients like 0.100, suggesting that interviewer attributes play a relatively minor role compared to environmental and relational factors during social surveys
+## VIF
+```{r}
+#| label: tbl-vif
+#| tbl-cap: "Variance Inflation Factors (VIF) for Each Predictor in the Model."
+#| echo: false
+#| warning: false
+
+vif_values <- vif(first_model)
+
+gvif_df <- data.frame(
+  Variable = rownames(vif_values), 
+  GVIF = round(vif_values[, "GVIF"], 3),
+  Df = vif_values[, "Df"],
+  `GVIF^(1/(2*Df))` = round(vif_values[, "GVIF^(1/(2*Df))"], 3)
+)
+
+kable(gvif_df)
+
+```
+@tbl-vif presents the Generalized Variance Inflation Factors (GVIF) for each predictor in the Bayesian logistic regression model.
+GVIF helps assess multicollinearity among predictors, indicating how much the variance of a regression coefficient is inflated due to correlations between variables.
+
+Most predictors, such as respondent_tried_best (GVIF = 3.186, Df = 5) and respondent_reluctant (GVIF = 2.725, Df = 5), show moderate GVIF values, suggesting manageable multicollinearity.
+The adjusted GVIF values, which are generally close to 1, indicate that the inflation effect is controlled across variables.
+
+In summary, the GVIF analysis indicates that multicollinearity is present but not severe enough to threaten model reliability.
+Further analysis may focus on predictors with slightly higher GVIF to ensure stability.
 
 ## Posterior predictive check
-###Validation
 ```{r}
+#| eval: true
 #| echo: false
+#| message: false
 #| warning: false
+#| label: fig-ppcheck
+#| fig-cap: "Posterior Predictive Check: The comparison between observed response values (dark line) and model-generated replications (light lines) demonstrates the model's ability to replicate the observed response patterns, indicating a good fit and capturing the main features of the response distribution."
 
@@
 
-vif(first_model)
-
-residuals <- residuals(first_model, type = "response")
-hist(residuals, main = "Residual Histogram", xlab = "Residuals")
-
-r2_values <- bayes_R2(first_model)
-r2_df <- data.frame(Index = 1:length(r2_values), R2 = r2_values)
-
-ggplot(r2_df, aes(x = Index, y = R2)) +
-  geom_bar(stat = "identity", fill = "steelblue") +
-  labs(title = "Bayesian R^2 Metrics for first_model Observations", x = "Observation Index", y = "R^2 Value") +
-  theme_minimal()
-
-# Perform LOO cross-validation and assign to loo_results
-loo_results <- loo(first_model)
-# Extract Pareto k values from loo results and plot
-pareto_k <- loo_results$diagnostics$pareto_k
-pareto_k_df <- data.frame(Index = 1:length(pareto_k), Pareto_k = pareto_k)
-
-ggplot(pareto_k_df, aes(x = Index, y = Pareto_k)) +
-  geom_bar(stat = "identity", fill = "orange") +
-  geom_hline(yintercept = 0.7, linetype = "dashed", color = "red") +
-  labs(title = "Pareto k Diagnostic Values", x = "Observation Index", y = "Pareto k Value") +
-  theme_minimal()
-
-loo_df <- data.frame(Observation = 1:length(loo_results$pointwise[,"elpd_loo"]),
-                     ELPD_LOO = loo_results$pointwise[,"elpd_loo"])
-
-ggplot(loo_df, aes(x = Observation, y = ELPD_LOO)) +
-  geom_point(color = "darkgreen") +
-  geom_smooth(method = "loess", color = "red", se = FALSE) +
-  labs(title = "Leave-One-Out Cross Validation (ELPD_LOO)", x = "Observation Index", y = "ELPD_LOO") +
-  theme_classic()
 ```
+In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by \( y \)) and the replicated data generated from the model (denoted by \( y_{\text{rep}} \)).
+The replicated lines closely follow the shape and central trend of the observed data, particularly around the main peak at 0.9, which suggests that the model captures the overall distribution effectively.
+This alignment indicates that the model successfully represents the underlying data-generating process, especially in regions with high data density.
+While the model's performance appears strong, any visible discrepancies—particularly in areas of lower density—may highlight aspects of the data structure that are not fully captured.
+Addressing such discrepancies could involve refining the model by introducing additional parameters or reconsidering underlying assumptions.
+Overall, this comparison provides evidence that the model fits well, though there remain potential areas for enhancement to better encompass the full range of data complexities.
 
@@
 ## Diagnostics
+### Validation
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-diagnostic-checks
+#| fig-cap: "Comparing Diagnostic Visualizations for Model Checking"
+#| fig-subcap: ["Residual Histogram", "Pareto k Diagnostic Values"]
+#| layout-ncol: 2
+
+# Generate Residual Histogram
+residuals <- residuals(first_model, type = "response")
+hist(residuals, main = "Residual Histogram", xlab = "Residuals")
+
+# Perform LOO cross-validation and assign to loo_results
+loo_results <- loo(first_model)
+
+# Extract Pareto k values from loo results and create the Pareto k Diagnostic plot
+pareto_k <- loo_results$diagnostics$pareto_k
+pareto_k_df <- data.frame(Index = 1:length(pareto_k), Pareto_k = pareto_k)
+
+ggplot(pareto_k_df, aes(x = Index, y = Pareto_k)) +
+  geom_bar(stat = "identity", fill = "orange") +
+  geom_hline(yintercept = 0.7, linetype = "dashed", color = "red") +
+  labs(title = "Pareto k Diagnostic Values", x = "Observation Index", y = "Pareto k Value") +
+  theme_minimal()
+
+```
+In Figure @fig-diagnostic-checks-1, the residual histogram displays the distribution of residuals from the model.
+The concentrated frequency around zero suggests that the model effectively captures much of the variability in the data, with fewer extreme deviations, thereby indicating a reasonable level of fit.
+
+Figure @fig-diagnostic-checks-2 presents the Pareto k diagnostic values, which help assess the reliability of the estimated leave-one-out cross-validation (LOO) predictions.
+The majority of Pareto k values fall below the threshold of 0.7, indicating that the model is well-calibrated with only minimal issues in terms of influential observations.
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: fig-loo-rhat-checks
+#| fig-cap: "Comparing Diagnostic Visualizations for Model Checking"
+#| fig-subcap: ["Leave-One-Out Cross Validation (ELPD_LOO)", "Rhat Diagnostic Plot"]
+#| layout-ncol: 2
+# Create Leave-One-Out Cross Validation (ELPD_LOO) plot
+loo_df <- data.frame(Observation = 1:length(loo_results$pointwise[,"elpd_loo"]),
+                     ELPD_LOO = loo_results$pointwise[,"elpd_loo"])
+
+ggplot(loo_df, aes(x = Observation, y = ELPD_LOO)) +
+  geom_point(color = "darkgreen") +
+  geom_smooth(method = "loess", color = "red", se = FALSE) +
+  labs(title = "Leave-One-Out Cross Validation (ELPD_LOO)", x = "Observation Index", y = "ELPD_LOO") +
+  theme_classic()
+
+# Generate Rhat Diagnostic Plot
+rhat_values <- rhat(first_model)
+mcmc_rhat(rhat_values)
+
+```
+
+Figure @fig-loo-rhat-checks-1 is a scatter plot for leave-one-out cross-validation (ELPD_LOO) estimates.
+The consistency of the points around the red loess smooth line suggests that the model’s predictions are largely consistent across different observations, thus reinforcing the model's robustness.
+
+Figure @fig-loo-rhat-checks-2 is an Rhat plot, showing that all values of the Rhat diagnostic are close to 1.
+This indicates good mixing of the Markov Chain Monte Carlo (MCMC) chains and suggests that the model has likely converged appropriately, making the posterior estimates trustworthy.
 

### 2024-11-27 paper/paper.qmd
update paper

@@
 library(modelsummary)
+library(caret)
 ```
@@
 - **modelsummary** [@modelsummary]: Summarizes statistical models in a clear, tabular format, supporting the communication of regression and other model results.
+
+- **caret** [@caret]: Provides a unified interface for training and tuning machine learning models, offering numerous functions for preprocessing data, feature selection, model training, and performance evaluation, which streamline the process of creating predictive models.
 
@@
 #| echo: false
+#| eval: true
+#| message: false
 #| warning: false
+#| label: tbl-comprehension-matrix
+#| tbl-cap: "Confusion Matrix for Comprehension Classification"
+#| tbl-subcap: ["Counts of Predictions vs Reference", "Performance Metrics Summary"]
+#| layout-ncol: 2
 analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
@@
 
-# Import caret library and calculate confusion matrix
-library(caret)
-
 confusion_matrix <- confusionMatrix(
@@
 
-# Print the confusion matrix
-print(confusion_matrix)
+confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
+                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
+                                           "Reference" = c("Not_understood", "Understood")))
 
-scatter_data <- data.frame(
-  Actual = analysis_data_test$respondent_understood_binary,
-  Predicted = analysis_data_test$predicted_class
+# Extract True Positive, False Positive, True Negative, and False Negative from the confusion matrix
+TP <- confusion_matrix["Not_understood", "Not_understood"]
+FP <- confusion_matrix["Not_understood", "Understood"]
+TN <- confusion_matrix["Understood", "Understood"]
+FN <- confusion_matrix["Understood", "Not_understood"]
+
+# Calculate evaluation metrics
+accuracy <- (TP + TN) / sum(confusion_matrix)
+precision <- TP / (TP + FP)
+recall <- TP / (TP + FN)
+specificity <- TN / (TN + FP)
+fpr <- FP / (FP + TN) # False Positive Rate
+fnr <- FN / (FN + TP) # False Negative Rate
+f1_score <- 2 * (precision * recall) / (precision + recall)
+balanced_accuracy <- (recall + specificity) / 2
+
+# Create a data frame for metrics
+metrics_df <- data.frame(
+  Metric_Name = c("Accuracy", 
+                  "Precision (Positive Predictive Value, PPV)",
+                  "Recall (True Positive Rate, TPR)", 
+                  "True Negative Rate (TNR, Specificity)", 
+                  "False Positive Rate (FPR)", 
+                  "False Negative Rate (FNR)", 
+                  "F1 Score", 
+                  "Balanced Accuracy"),
+  Value = round(c(accuracy, precision, recall, specificity, fpr, fnr, f1_score, balanced_accuracy), 4)
 )
 
-ggplot(scatter_data, aes(x = Actual, y = Predicted)) +
-  geom_jitter(width = 0.2, height = 0.2, alpha = 0.5, color = "blue") +
-  labs(
-    title = "Scatter Plot of Actual vs Predicted Values",
-    x = "Actual Response Understanding",
-    y = "Predicted Response Understanding"
-  ) +
-  theme_minimal()
+# Print the metrics table
+kable(metrics_df, caption = "Evaluation Metrics for Classification Model")
+
+confusion_df <- as.data.frame(as.table(confusion_matrix))
+
+confusion_df %>%
+  kable("html", col.names = c("Reference", "Not_understood", "Understood"), 
+        caption = "Confusion Matrix for Comprehension Classification") %>%
+  kable_styling(full_width = FALSE)
 
 ```
+@tbl-comprehension-matrix-2 presents the confusion matrix for the comprehension classification model.
+The matrix provides the counts of correct and incorrect classifications between the "Not_understood" and "Understood" categories, highlighting how well the model performed in predicting respondent comprehension.
+The diagonal elements represent the correctly classified observations, while the off-diagonal elements indicate misclassifications.
+The matrix helps visualize the strengths and weaknesses of the model, particularly in distinguishing between respondents who understood versus those who did not.
 
+@tbl-comprehension-matrix-1 shows the evaluation metrics for the classification model.
+These metrics include Accuracy, Precision (Positive Predictive Value), Recall (True Positive Rate), True Negative Rate (Specificity), and F1 Score, among others.
+The metrics provide a comprehensive summary of the model's performance, measuring not only how many predictions were correct, but also evaluating the balance between sensitivity and specificity.
+The high specificity and overall accuracy indicate that the model is effective in identifying respondents who understood the questions, but the low recall suggests limitations in detecting those who did not understand.
 ## Diagnostics

### 2024-11-28 paper/paper.qmd
update paper

@@
 # Appendix {.unnumbered}
+## Data Cleaning Notes
+We began by importing the raw dataset using the read.csv() function from base R, with a focus on keeping the process flexible for further manual manipulation.
+Initially, we removed columns that contained more than 80% missing values to retain only the most relevant information for analysis.
 
-# Additional data details
+To handle missing data, numeric variables were filled with their median values, while categorical variables were imputed with their mode.
+This approach aimed to maintain data integrity while minimizing assumptions about the distribution of missing values.
+
+Subsequently, additional data cleaning measures were taken.
+We removed duplicate entries to ensure uniqueness and eliminated outliers in numeric columns using the Z-score method, retaining only those rows with Z-scores within ±3.
+This step was important for reducing the influence of extreme data points on subsequent analyses.
+
+To enhance clarity and usability, several column names were renamed to be more descriptive.
+For example, resundq was renamed to respondent_understood.
+Additionally, the respondent_understood variable was recoded into a binary form (Understood vs.
+Not_understood) to simplify future analyses.
+
+To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category.
+The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.
+
+After cleaning, the dataset was split into training and testing sets in a way that ensured the country variable was well-represented in both.
+This stratified split preserved regional diversity, which was essential for maintaining representativeness in model training and evaluation.
+
+Lastly, the cleaned dataset was saved in both Parquet and CSV formats for use in future stages of the analysis.
+This ensured compatibility across different software tools and provided efficient access for future work.
+
+## European Social Survey  Methodology
+The European Social Survey (ESS) is a cross-national survey conducted biennially across European countries, aimed at measuring the attitudes, beliefs, and behaviors of European citizens.
+To ensure data accuracy and quality, the ESS employs rigorous survey methodologies and standardized procedures, ensuring comparability across participating countries and providing a reliable data source for social science research and policymaking (European Social Survey, 2024).
+
+The ESS targets individuals aged 15 and older living in private households across participating European countries, using a carefully designed sampling framework to ensure national representativeness.
+Countries employ multi-stage probability sampling to select respondents, ensuring that each individual has an equal chance of being selected, thereby minimizing selection bias and enhancing the generalizability of survey results.
+
+To collect the data, the ESS uses trained interviewers to conduct face-to-face interviews.
+These interviews are conducted in the respondents' native language, ensuring that participants can fully understand the questions being asked.
+The questionnaires are translated following rigorous standardized guidelines to ensure equivalence across languages and cultures (European Social Survey, 2024).
+Additionally, questionnaires are pre-tested before the official survey is launched to identify and resolve potential misunderstandings, ensuring consistent understanding among respondents.
+
+During data collection, the ESS implements strict quality control procedures, including systematic interviewer training, ensuring they conduct interviews following standardized techniques to reduce bias and maintain data consistency.
+To ensure sample representativeness, stratified sampling is used in some countries based on demographic characteristics like age, gender, and region, ensuring sufficient representation of different population groups.
+
+Like many survey research initiatives, the ESS faces challenges related to declining response rates.
+To mitigate non-response, the ESS requires interviewers to make multiple contact attempts, particularly in cases where initial attempts are unsuccessful, including follow-up visits.
+To further reduce non-response bias, post-stratification weights are applied to the collected data to adjust for differences between the sample and the overall population.
+
+The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue.
+Most interviews are conducted within a reasonable timeframe to ensure high response quality.
+The ESS places significant emphasis on accurately capturing every viewpoint, ensuring that the voices of marginalized groups are also adequately represented, which helps policymakers and researchers better understand the dynamics of social attitudes in Europe.
+
+By maintaining strict methodologies regarding sampling frameworks, translation procedures, interviewer training, and addressing non-response bias, the European Social Survey has become a trusted source of social data, providing essential support for research into cross-national comparisons and understanding social attitudes.
+
+##  Ideal Methodology
+
+For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the **European Social Survey (ESS)**.
+The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.
+
+**Sampling Method**: We’ll use **stratified random sampling**, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
+This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.
+
+**Sample Size**: To make sure our analysis is meaningful, we plan to include at least **1,500 participants per country**.
+For larger and more diverse countries, we may increase this number to properly represent smaller groups.
+
+**Data Collection Approach**: We’ll use a **mixed-method approach** for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
+Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality.
+We’ll also use self-administered questionnaires for follow-ups to improve the response rate among harder-to-reach groups, like younger people or those who move around frequently.
+
+**Survey Process and Quality Checks**: Interviewers will use standardized scripts to make sure everyone hears the questions the same way.
+Surveys will be recorded digitally to make data handling easier and to minimize errors.
+To avoid any bias, interviewers are trained to read questions in a neutral manner.
+
+**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will **oversample** some groups, like the elderly or those with lower education levels.
+This gives us more precise data about these groups, but we will use **weight adjustments** afterward to ensure the final dataset reflects the actual population structure.
+
+**Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
+- **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
+- **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
+- **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.
+
+**Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate.
+We’ll use **statistical adjustments** to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
+
+### Budget Breakdown for Survey Implementation
+
+To ensure we collect and analyze quality data, we will allocate the budget as follows:
+
+1. **Survey Design**: $8,000
+   - This budget includes designing the questionnaire, translating it into multiple languages, and making sure the questions are clear and unbiased. It also covers interviewer training costs.
+
+2. **Sampling and Recruitment**: $15,000
+   - This will go towards sampling costs, including **stratified sampling** to make sure all groups are represented proportionally.
+It also includes acquiring relevant demographic data for the 23 countries participating in ESS.
+
+3. **Recruiting Respondents**: $30,000
+   - This covers contacting participants, managing interviews, and compensating them for follow-ups across the countries.
+
+4. **Incentives**: $20,000
+   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
+
+5. **Data Quality Assurance and Analysis**: $12,000
+   - This includes data cleaning, quality checks, and analysis costs.
+We’ll hire statistical consultants to ensure proper data handling, make sure there are no inconsistencies, and apply adjustments to correct biases.
+
+By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
+
+##Comprehension and Interview Experience Survey*
+**Conducted by**: DEZHEN CHEN 
+**Contact**: dezhen.chen@mail.utoronto.ca
+
+Thank you for taking part in the Comprehension and Interview Experience Survey.
+Your feedback is essential in helping us understand how respondents perceive and engage with survey questions, and in improving the quality of interview interactions as well as the overall survey process.
+
+**An example of the survey can be found at this link**: https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill
+
+As a small gesture of appreciation, all participants will have the opportunity to receive a $200 gift card. Ten respondents will be randomly selected to receive this gift.
+
+Please be assured that your responses will remain completely confidential and anonymous.
+The data collected will be securely stored and used solely for academic and research purposes, with no personal identifying information attached to your answers.
+
+**Please note:**
+* All responses are confidential and will be used for research purposes only.
+* This survey will take approximately 10 minutes to complete.
+* Your participation is entirely voluntary, and you may withdraw at any time.
+* All questions marked with an asterisk (*) are required.
+* There are no right or wrong answers; we appreciate your honest opinions.
+
+---
+
+ **Part 1: Interviewer Details**
+
+1. **Interviewer Age**  
+   - What is the age of the interviewer?  
+   * (Please specify in years)
+
+2. **Interviewer Gender**  
+   - What is the gender of the interviewer?  
+   * Male  
+   * Female
+
+---
+
+**Part 2: Interview Process Information**
+
+3. **Interview Conduct Method**  
+   - What was the method used to conduct this interview?  
+   * Face-to-face  
+   * Telephone  
+   * Online video interview  
+   * Other
+
+4. **Questionnaire Language**  
+   - What language was used during the interview?  
+   * (Please specify the language)
+
+5. **Question Clarification**  
+   - Did you need clarification on the questions during the interview?  
+   * No clarification needed  
+   * Minor clarification needed  
+   * Moderate clarification needed  
+   * Extensive clarification needed  
+   * Completely unclear, repeated explanations needed  
+   * Other
+
+6. **Respondent Understanding Level**  
+   - How well do you think the respondent understood the questions?  
+   * Fully understood  
+   * Mostly understood  
+   * Needed some clarification  
+   * Partially understood  
+   * Did not understand at all
+
+7. **Respondent Tried Their Best**  
+   - Do you think the respondent tried their best to answer the questions?  
+   * Very unwilling to answer  
+   * Somewhat reluctant  
+   * Neutral  
+   * Willing to answer  
+   * Very willing to answer  
+   * Other
+
+---
+
+**Part 3: Interference During Interview**
+
+8. **Interference Presence**  
+   - Was there any interference during the interview process?  
+   * Yes  
+   * No
+
+9. **Partner Interference**  
+   - Was there any interference by a partner during the interview?  
+   * Yes  
+   * No
+
+10. **Child Interference**  
+   - Was there any interference by children during the interview?  
+   * Yes  
+   * No
+
+11. **Parent Interference**  
+   - Was there any interference by parents during the interview?  
+   * Yes  
+   * No
+
+12. **Relative Interference**  
+   - Was there any interference by other relatives during the interview?  
+   * Yes  
+   * No
+
+13. **Non-relative Interference**  
+   - Was there any interference by non-relatives during the interview?  
+   * Yes  
+   * No
+
+14. **Unknown Interference**  
+   - Was there any unknown source of interference during the interview?  
+   * Yes  
+   * No
+
+15. **Interference Not Applicable**  
+   - Was interference not applicable during this interview?  
+   * Yes  
+   * No
+
+---
+
+ **Part 4: Additional Feedback**
+
+16. **Additional Comments**  
+   - Do you have any suggestions or feedback regarding the interview process? (open-ended)
+
+17. **Interference Details**  
+   - If there was interference, could you please describe it in more detail? (open-ended)
+
+18. **Suggestions for Improvement**  
+   - Do you have any suggestions to improve the clarity or format of the questions in this survey? (open-ended)
+
+---
+
+**Thank You Message**
+
+Thank you once again for your participation.
+Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension.
+We appreciate your time and effort in completing this survey.
 
@@
 )
+
 ```

### 2024-11-28 paper/paper.qmd
update predication

@@
 
-# Appendix {.unnumbered}
+# Appendix {#sec-appx}
 ## Data Cleaning Notes
@@
 
-For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the **European Social Survey (ESS)**.
+For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the European Social Survey (ESS).
 The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.
 
-**Sampling Method**: We’ll use **stratified random sampling**, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
+**Sampling Method**: We’ll use stratified random sampling, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
 This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.
 
-**Sample Size**: To make sure our analysis is meaningful, we plan to include at least **1,500 participants per country**.
+**Sample Size**: To make sure our analysis is meaningful, we plan to include at least 1,500 participants per country.
 For larger and more diverse countries, we may increase this number to properly represent smaller groups.
 
-**Data Collection Approach**: We’ll use a **mixed-method approach** for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
+**Data Collection Approach**: We’ll use a mixed-method approach for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
 Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality.
@@
 
-**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will **oversample** some groups, like the elderly or those with lower education levels.
-This gives us more precise data about these groups, but we will use **weight adjustments** afterward to ensure the final dataset reflects the actual population structure.
+**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will oversample some groups, like the elderly or those with lower education levels.
+This gives us more precise data about these groups, but we will use weight adjustments afterward to ensure the final dataset reflects the actual population structure.
 
 **Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
+
 - **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
+
 - **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
+
 - **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.
@@
 **Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate.
-We’ll use **statistical adjustments** to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
+We’ll use statistical adjustments to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
 
@@
 
-##Comprehension and Interview Experience Survey*
+## Idealized Survey
+
+An example of the survey can be found at this link: <https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill>
+
+**2024 Comprehension and Interview Experience Survey**  
 **Conducted by**: DEZHEN CHEN  
-**Contact**: dezhen.chen@mail.utoronto.ca
-
-Thank you for taking part in the Comprehension and Interview Experience Survey.
-Your feedback is essential in helping us understand how respondents perceive and engage with survey questions, and in improving the quality of interview interactions as well as the overall survey process.
-
-**An example of the survey can be found at this link**: https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill
-
-As a small gesture of appreciation, all participants will have the opportunity to receive a $200 gift card. Ten respondents will be randomly selected to receive this gift.
-
-Please be assured that your responses will remain completely confidential and anonymous.
-The data collected will be securely stored and used solely for academic and research purposes, with no personal identifying information attached to your answers.
-
-**Please note:**
-* All responses are confidential and will be used for research purposes only.
-* This survey will take approximately 10 minutes to complete.
-* Your participation is entirely voluntary, and you may withdraw at any time.
-* All questions marked with an asterisk (*) are required.
-* There are no right or wrong answers; we appreciate your honest opinions.
+**Contact**: dezhen.chen\@mail.utoronto.ca
+
+Welcome, and thank you for taking part in the **2024 Comprehension and Interview Experience Survey**.
+Your participation will help us understand how respondents perceive and engage with survey questions, and will improve the quality of interview interactions.
+
+As a thank you for your time, all survey respondents will be automatically entered into a sweepstakes, with a **chance to win $200**. Ten winners will be selected randomly.
+
+**Your responses will remain strictly confidential** and anonymous, and any data collected will be securely stored and used solely for academic and research purposes.
+No identifying information will be connected to your survey responses.
 
@@
 
- **Part 1: Interviewer Details**
-
-1. **Interviewer Age**  
-   - What is the age of the interviewer?  
-   * (Please specify in years)
-
-2. **Interviewer Gender**  
-   - What is the gender of the interviewer?  
-   * Male  
-   * Female
+## Section 1: Demographics
+
+**Country of Residence**:  
+Please specify your country of residence:  
+- [Your answer]
 
@@
 
-**Part 2: Interview Process Information**
-
-3. **Interview Conduct Method**  
-   - What was the method used to conduct this interview?  
-   * Face-to-face  
-   * Telephone  
-   * Online video interview  
-   * Other
-
-4. **Questionnaire Language**  
-   - What language was used during the interview?  
-   * (Please specify the language)
-
-5. **Question Clarification**  
-   - Did you need clarification on the questions during the interview?  
-   * No clarification needed  
-   * Minor clarification needed  
-   * Moderate clarification needed  
-   * Extensive clarification needed  
-   * Completely unclear, repeated explanations needed  
-   * Other
-
-6. **Respondent Understanding Level**  
-   - How well do you think the respondent understood the questions?  
-   * Fully understood  
-   * Mostly understood  
-   * Needed some clarification  
-   * Partially understood  
-   * Did not understand at all
-
-7. **Respondent Tried Their Best**  
-   - Do you think the respondent tried their best to answer the questions?  
-   * Very unwilling to answer  
-   * Somewhat reluctant  
-   * Neutral  
-   * Willing to answer  
-   * Very willing to answer  
-   * Other
+## Section 2: Interviewer Details
+
+**Interviewer Age**:  
+What is the age of the interviewer?  
+- [Please specify in years]
+
+**Interviewer Gender**:  
+What is the gender of the interviewer?  
+1. Male  
+2. Female
 
@@
 
-**Part 3: Interference During Interview**
-
-8. **Interference Presence**  
-   - Was there any interference during the interview process?  
-   * Yes  
-   * No
-
-9. **Partner Interference**  
-   - Was there any interference by a partner during the interview?  
-   * Yes  
-   * No
-
-10. **Child Interference**  
-   - Was there any interference by children during the interview?  
-   * Yes  
-   * No
-
-11. **Parent Interference**  
-   - Was there any interference by parents during the interview?  
-   * Yes  
-   * No
-
-12. **Relative Interference**  
-   - Was there any interference by other relatives during the interview?  
-   * Yes  
-   * No
-
-13. **Non-relative Interference**  
-   - Was there any interference by non-relatives during the interview?  
-   * Yes  
-   * No
-
-14. **Unknown Interference**  
-   - Was there any unknown source of interference during the interview?  
-   * Yes  
-   * No
-
-15. **Interference Not Applicable**  
-   - Was interference not applicable during this interview?  
-   * Yes  
-   * No
+## Section 3: Interview Process Information
+
+**Interview Conduct Method**:  
+What was the method used to conduct this interview?  
+1. Face-to-face  
+2. Telephone  
+3. Online video interview  
+4. Other
+
+**Questionnaire Language**:  
+What language was used during the interview?  
+- [Please specify the language]
+
+**Question Clarification**:  
+Did you need clarification on the questions during the interview?  
+1. No clarification needed  
+2. Minor clarification needed  
+3. Moderate clarification needed  
+4. Extensive clarification needed  
+5. Completely unclear, repeated explanations needed  
+6. Other
+
+**Respondent Understanding Level**:  
+How well do you think the respondent understood the questions?  
+1. Fully understood  
+2. Mostly understood  
+3. Needed some clarification  
+4. Partially understood  
+5. Did not understand at all
+
+**Respondent Tried Their Best**:  
+Do you think the respondent tried their best to answer the questions?  
+1. Very unwilling to answer  
+2. Somewhat reluctant  
+3. Neutral  
+4. Willing to answer  
+5. Very willing to answer  
+6. Other
 
@@
 
- **Part 4: Additional Feedback**
-
-16. **Additional Comments**  
-   - Do you have any suggestions or feedback regarding the interview process? (open-ended)
-
-17. **Interference Details**  
-   - If there was interference, could you please describe it in more detail? (open-ended)
-
-18. **Suggestions for Improvement**  
-   - Do you have any suggestions to improve the clarity or format of the questions in this survey? (open-ended)
+## Section 4: Interference During Interview
+
+**Interference Presence**:  
+Was there any interference during the interview process?  
+1. Yes  
+2. No
+
+**Partner Interference**:  
+Was there any interference by a partner during the interview?  
+1. Yes  
+2. No
+
+**Child Interference**:  
+Was there any interference by children during the interview?  
+1. Yes  
+2. No
+
+**Parent Interference**:  
+Was there any interference by parents during the interview?  
+1. Yes  
+2. No
+
+**Relative Interference**:  
+Was there any interference by other relatives during the interview?  
+1. Yes  
+2. No
+
+**Non-relative Interference**:  
+Was there any interference by non-relatives during the interview?  
+1. Yes  
+2. No
+
+**Unknown Interference**:  
+Was there any unknown source of interference during the interview?  
+1. Yes  
+2. No
+
+**Interference Not Applicable**:  
+Was interference not applicable during this interview?  
+1. Yes  
+2. No
 
@@
 
-**Thank You Message**
-
+## Section 5: Additional Feedback
+
+**Additional Comments**:  
+Do you have any suggestions or feedback regarding the interview process?  
+- [Please provide your comments]
+
+**Interference Details**:  
+If there was interference, could you please describe it in more detail?  
+- [Please provide your comments]
+
+**Suggestions for Improvement**:  
+Do you have any suggestions to improve the clarity or format of the questions in this survey?  
+- [Please provide your suggestions]
+
+---
+
+## Important Notes
+
+- All responses are confidential and will be used for research purposes only.
+- This survey will take approximately 10 minutes to complete.
+- Your participation is entirely voluntary, and you may withdraw at any time.
+- All questions marked with an asterisk (*) are required.
+- There are no right or wrong answers; we appreciate your honest opinions.
+
+---
+
+**Thank You Message**:  
 Thank you once again for your participation.
@@
 ```
-In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by \( y \)) and the replicated data generated from the model (denoted by \( y_{\text{rep}} \)).
+In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by $y$ and the replicated data generated from the model (denoted by $( y_{\text{rep}})$.
 The replicated lines closely follow the shape and central trend of the observed data, particularly around the main peak at 0.9, which suggests that the model captures the overall distribution effectively.
@@
 #| warning: false
-#| label: tbl-comprehension-matrix
+#| label: tbl-comprehension-matrix1
 #| tbl-cap: "Confusion Matrix for Comprehension Classification"
-#| tbl-subcap: ["Counts of Predictions vs Reference", "Performance Metrics Summary"]
-#| layout-ncol: 2
+
+# Confusion matrix definition
+confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
+                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
+                                           "Reference" = c("Not_understood", "Understood")))
+
+# Convert confusion matrix to data frame
+confusion_df <- as.data.frame(as.table(confusion_matrix))
+
+# Create and directly print the Markdown table using kable
+kable(confusion_df, format = "markdown")
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: tbl-comprehension-matrix2
+#| tbl-cap: "Confusion Matrix for Comprehension Classification"
+
 analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
@@
 analysis_data_test$respondent_understood_binary <- factor(analysis_data_test$respondent_understood_binary, levels = c("Not_understood", "Understood"))
-
-# Display table of prediction results
-table(analysis_data_test$predicted_class)
-table(analysis_data_test$respondent_understood_binary)
 
@@
 # Print the metrics table
-kable(metrics_df, caption = "Evaluation Metrics for Classification Model")
-
-confusion_df <- as.data.frame(as.table(confusion_matrix))
-
-confusion_df %>%
-  kable("html", col.names = c("Reference", "Not_understood", "Understood"), 
-        caption = "Confusion Matrix for Comprehension Classification") %>%
-  kable_styling(full_width = FALSE)
-
-```
-@tbl-comprehension-matrix-2 presents the confusion matrix for the comprehension classification model.
+kable(metrics_df)
+
+```
+@tbl-comprehension-matrix1 presents the confusion matrix for the comprehension classification model.
 The matrix provides the counts of correct and incorrect classifications between the "Not_understood" and "Understood" categories, highlighting how well the model performed in predicting respondent comprehension.
@@
 
-@tbl-comprehension-matrix-1 shows the evaluation metrics for the classification model.
+@tbl-comprehension-matrix2 shows the evaluation metrics for the classification model.
 These metrics include Accuracy, Precision (Positive Predictive Value), Recall (True Positive Rate), True Negative Rate (Specificity), and F1 Score, among others.
@@
 The high specificity and overall accuracy indicate that the model is effective in identifying respondents who understood the questions, but the low recall suggests limitations in detecting those who did not understand.
+
 ## Diagnostics
+
 ### Validation
@@
 \newpage
-
 # References

### 2024-11-28 paper/paper.qmd
update paper

@@
 title: "The Impact of Interview Disruptions on Data Quality in Social Surveys"
-subtitle: "Analyzing How Various Interferences Affect Respondent Accuracy and Survey Reliability"
+subtitle: "Family Interference and Interview Methods Found to Significantly Affect Respondent Comprehension and Survey Data Quality"
 author: 
@@
 date-format: long
-abstract: "In social surveys, disruptions during interviews can significantly impact the quality of respondent data, which in turn affects the reliability of the survey results.
-This study uses Bayesian hierarchical logistic regression to analyze how various factors—such as the type of disruption, the presence of different family members, interview conduct method, interviewer characteristics, and respondent attitudes—affect the accuracy and quality of responses.
-Our analysis shows that different types of disruptions have distinct impacts on the quality of responses, revealing critical insights into optimizing survey conditions to improve data reliability and validity."
+abstract: "In social surveys, disruptions during interviews can profoundly impact the quality of respondent data, thereby affecting the overall reliability of survey results.
+This study employs Bayesian hierarchical logistic regression to analyze the influence of a diverse range of factors—including the type of disruption, presence of family members, interview methodology, interviewer characteristics, and respondent attitudes—on response quality and accuracy.
+Our findings indicate that various forms of disruptions uniquely impact data quality, with some conditions proving more detrimental than others.
+These insights are pivotal for refining survey methodologies and optimizing interview conditions, ultimately improving the reliability and validity of collected data."
 format: pdf
@@
 
-In recent years, the quality of social survey data has become an important topic of inquiry, especially with regard to how different disruptions impact respondent behavior.
-Several studies have contributed to this body of knowledge by focusing on factors that may affect the reliability of survey responses.
-Groves et al.
-[@groves2011survey] examined the role of interviewer characteristics—such as experience and demeanor—in shaping the quality of responses through a multi-level modeling approach.
-In another key study, Couper and de Leeuw [@massey2013we] investigated how different modes of conducting interviews, like in-person versus telephone, influenced the comfort and attentiveness of respondents.
-Fowler and Mangione [@fowler1990standardized] took a different approach by analyzing observational data to assess the impact of third-party presence during interviews.
-Although these works laid a valuable foundation for understanding data quality, there remains a gap in systematically analyzing the distinct effects of various kinds of disruptions, such as familial or environmental interference, on respondent understanding and response accuracy.
-
-This study endeavors to address these overlooked aspects by closely examining the role of interview disruptions on data quality in a major social survey.
-Specifically, our analysis explores the influence of different types of interferences—including interruptions from partners, children, and other family members—on respondents' comprehension and engagement during the interview process.
-We employed a Bayesian logistic regression model utilizing the rstanarm package in R to capture these influences.
-The model incorporates a range of predictor variables, such as interviewer characteristics (age and gender), different methods of interview administration, and family-related interferences.
-During data preparation, the categorical levels of several predictor variables were simplified, excluding the 'country' variable, to ensure interpretability and to streamline model estimation.
-We also included indicators of respondent attitudes, such as whether questions were clarified during the interview or if reluctance to answer was observed, aiming for a more comprehensive understanding of respondent engagement.
-
-Our results reveal compelling insights into the effects of these disruptions on data quality.
-We found that family-related interferences, notably from partners and parents, were associated with reduced comprehension on the part of respondents.
-The findings also suggested that interviews conducted in-person resulted in significantly higher levels of respondent understanding compared to those conducted by telephone.
-Additionally, older interviewers generally achieved better data quality, which could reflect an ability to manage disruptions more effectively or employ better rapport-building techniques.
-The influence of the interviewer's gender was also noted, though it appeared to interact in more complex ways with other factors such as the mode of interview and the specific type of interference.
-Taken together, these findings underscore the importance of managing both environmental and personal factors during interviews to improve data accuracy.
-
-Beyond merely quantifying these effects, our study provides deeper implications for enhancing data collection practices in the field.
-The evidence points to the need for improved interviewer training focused on managing disruptions effectively, which can help ensure the collection of high-quality data even in less-than-ideal circumstances.
-The significant negative effects of family interference suggest that in-home surveys could benefit from targeted strategies to minimize such disruptions, including adjusting the timing of interviews or providing incentives for privacy during responses.
-Furthermore, the results highlight the importance of understanding respondent reluctance and tailoring interviewer interactions to reduce its occurrence.
-These insights have relevance for not only improving the current practices of social surveys but also for shaping future methodologies in an increasingly diverse and complex interviewing landscape.
-
-The paper is structured to offer an in-depth examination of the factors that affect respondent comprehension during social survey interviews.
-Following the introduction in @sec-intro, @sec-data provides a detailed overview of the dataset, focusing on the different variables and their role in assessing data quality.
-It also outlines the preprocessing steps taken, including data cleaning and the recoding of variables.
-@sec-model introduces the Bayesian logistic regression methodology, explaining the statistical approach and justifying the selection of priors for the analysis.
-In @sec-result, we present the empirical findings, including parameter estimates and an interpretation of the relationships uncovered by the model.
-@sec-discussion discusses the practical implications of these findings, emphasizing the improvements needed in interviewer training and the strategies for reducing respondent interference.
-Finally, @sec-model-details summarizes the key contributions of this research, outlines the limitations, and suggests avenues for future work—particularly concerning the integration of new data collection technologies and adaptive survey designs aimed at mitigating the impact of disruptions on respondent data quality.
+In recent years, the quality and reliability of data collected through social surveys have garnered increasing attention, especially considering how various forms of disruption may influence respondents’ behavior and, subsequently, the quality of survey responses.
+Social surveys are crucial tools for obtaining insights into societal trends, guiding public policy, and informing evidence-based decision-making.
+Thus, ensuring the robustness of data collected from these surveys has implications for the accuracy of the conclusions drawn and for the effective formulation of policy measures.
+Previous research has made significant strides in understanding factors that impact survey data quality.
+For example, Groves et al.
+[@groves2011survey] investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these nuanced dynamics.
+Similarly, Couper and de Leeuw [@massey2013we] explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
+In another significant contribution, Fowler and Mangione [@fowler1990standardized] analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
+Addressing this gap is imperative to improving the reliability of survey data, particularly in settings where such disruptions are unavoidable.
+
+This research seeks to fill this gap by systematically investigating the role of various disruptions during social survey interviews, focusing particularly on how different types of familial and environmental interferences affect respondent comprehension and engagement.
+To this end, we conducted a comprehensive analysis using Bayesian hierarchical logistic regression, implemented through the rstanarm package in R.
+This model structure was chosen for its ability to capture complex relationships, accounting for multiple levels of influence—namely, disruptions at the respondent level and interviewer characteristics nested within the survey context.
+The use of Bayesian methods allowed us to incorporate prior knowledge and manage uncertainty in the analysis effectively, while also making inferences about the likely impacts of the disruptions on data quality.
+Throughout the data preparation phase, categorical variables were simplified, excluding variables like 'country' that introduced excess complexity, in order to enhance interpretability and ensure the model’s tractability.
+Additionally, predictor variables included the method of interview administration (e.g., telephone, in-person), interviewer characteristics (age and gender), and respondent attitudes (such as willingness to answer or the need for clarification), providing a comprehensive understanding of the factors influencing survey outcomes.
+
+The findings from our analysis are compelling.
+We observed that disruptions involving family members—especially those by partners or parents—were significantly correlated with reduced comprehension among respondents, suggesting that these types of interference pose considerable challenges to data quality.
+Our results also show that in-person interviews generally result in higher levels of understanding compared to telephone interviews, highlighting the added value of non-verbal cues in face-to-face interactions.
+Older interviewers were found to achieve higher-quality responses, which could indicate that experience or maturity contributes to more effective management of disruptions.
+Gender of the interviewer also emerged as a significant factor, though its influence was more context-dependent, interacting with other variables such as the type of interference and the mode of the interview.
+These insights help to paint a detailed picture of the factors that can either hinder or enhance data quality in social survey settings, providing a richer understanding of the conditions that optimize respondent engagement and accuracy.
+
+Beyond these findings, our research provides broader implications for improving data collection methodologies in social surveys.
+The results suggest the need for targeted interviewer training focused on managing and mitigating disruptions, which could help maintain data integrity even under challenging circumstances.
+Such training might include strategies for diplomatically handling familial interruptions or methods for building stronger rapport with respondents to minimize distraction.
+The findings also point to the importance of timing surveys appropriately to reduce the likelihood of family-related interruptions, as well as the potential benefits of providing incentives that encourage privacy during responses.
+These strategies could help to ensure higher-quality data, particularly in contexts where disruptions are likely.
+Moreover, the observed significance of interviewer characteristics, such as age and gender, suggests that strategic interviewer assignments based on the respondent group’s specific needs could further enhance the quality of survey outcomes.
+These recommendations contribute to the development of more robust survey methodologies and enhance the potential of social surveys as tools for gathering high-quality data in diverse, real-world settings.
+
+The structure of the remainder of this paper is as follows.
+Section @sec-intro provides this introduction, outlining the research motivation and literature context.
+In Section @sec-data, we detail the dataset used, emphasizing the selection and preprocessing of variables that underpin our analysis, including data cleaning and recoding efforts.
+Section @sec-model describes the Bayesian hierarchical logistic regression model employed in this study, justifying the choice of statistical methods and the specification of prior distributions.
+In Section @sec-result, we present the empirical findings of the analysis, including parameter estimates and an interpretation of the relationships observed.
+Section @sec-discussion then discusses the practical implications of these findings, with a particular focus on the improvements needed in interviewer training and strategies to reduce the impact of disruptions on data quality.
+Finally, Section @sec-model-details summarizes the contributions of this research, addresses its limitations, and suggests avenues for future work, particularly concerning the application of adaptive survey designs and advanced data collection technologies aimed at minimizing the effects of respondent disruption.
 
@@
 ## Overview
-
-We use the statistical programming language R [@citeR] to process, analyze, and visualize survey data exploring the impact of interview disruptions on response quality.
-The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1), which collects information on societal attitudes and behaviors across multiple European countries.
-It includes several subsets tailored to different stages of the analysis, allowing a systematic examination of factors affecting survey response quality.
-The main dataset, used for modeling, consists of 9,743 rows and 25 variables.
-These data points capture details about various types of disruptions (e.g., partner, child, or relative interference), interview methods, and respondent characteristics.
-All responses are collected using standardized methods to ensure comparability across countries, thereby facilitating a detailed exploration of the impact of environmental factors, such as interruptions during interviews, on response quality.
-
-To ensure the reliability of the analysis, we filtered the data to exclude incomplete or ambiguous responses for key variables, such as missing values in "respondent_understood." Responses were also recoded into binary categories to focus on meaningful distinctions in response quality, while variables with excessive categories were grouped to improve interpretability.Different countries may implement localized adaptations in survey administration, which could influence response behaviors.
-To account for this, country-level metadata is included, allowing for the analysis of cross-national variations.
-These preprocessing steps were essential to refine the dataset and facilitate robust modeling.
+We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality.
+The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1), which offers a rich collection of data on societal attitudes and behaviors across numerous European countries.
+The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality.
+The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents.
+The meticulous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth exploration of the impacts of contextual disruptions on response quality.
+
+The decision to utilize the dataset was informed by its extensive scope and its inclusion of nuanced metadata concerning interview conditions and disruptions—elements that are typically absent in comparable survey datasets.
+Many alternative survey datasets, while providing general demographic information and attitudes, do not capture the critical contextual factors needed to assess disruptions during the interview process.
+For instance, unlike the ESS, many datasets fail to document interviewer characteristics, familial disruptions, or the specific type and frequency of interruptions during surveys.
+These contextual elements are crucial for gaining an in-depth understanding of how disruptions can influence data quality.
+Therefore, the ESS was deemed the most suitable resource for this study, as it provides both the breadth and depth of information needed to rigorously analyze the factors affecting survey reliability and validity.
+
+In preparing the dataset for analysis, careful data preprocessing steps were taken to enhance the robustness of our findings.
+Initially, incomplete or ambiguous responses for critical variables, such as those relating to "respondent_understood," were excluded to ensure analytical integrity.
+Responses were also recoded into binary categories to provide clearer distinctions in response quality, while variables with numerous categorical levels were consolidated to enhance interpretability.
+For example, seldom-reported categories in predictor variables were merged into an "Other" group, thereby simplifying the model and ensuring statistical power in the analysis.
+
+The dataset also includes country-level metadata, acknowledging that different countries may adopt localized adaptations in survey administration, which may, in turn, influence respondent behavior.
+This inclusion allows us to capture cross-national variations effectively.
+For instance, in-home interviews in some countries might experience more frequent familial disruptions, such as interference from partners or children, which could compromise the quality of the collected data.
+By accounting for these variations, the analysis is more nuanced, providing a comprehensive understanding of how environmental factors influence data reliability and the conditions under which survey data is most trustworthy.
 
@@
 - **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies in presenting data and statistical information.
+
+## Measurement
+Data quality in social surveys is a measurement of how accurately the collected responses reflect true respondent comprehension and the conditions influencing their answers.
+This study captures critical aspects of the interview process—such as different types of disruptions, modes of interview conduct, and respondent attitudes—to understand their impact on the reliability of responses.
+Disruptions during interviews, such as interruptions by family members, are systematically documented to assess their influence on the quality of data gathered.
+
+In our dataset, the measurement process involves encoding disruptions, interview methods, and respondent behaviors into structured variables that serve as proxies for real-world events affecting survey outcomes.
+These entries include details about how interviews were conducted—whether in-person, by phone, or online—and the presence of different types of interference during the interview.
+This transformation from qualitative experiences into quantifiable data enables us to evaluate the influence of these factors on response accuracy.
+For instance, interviews conducted face-to-face may elicit higher attentiveness from respondents compared to those conducted via telephone, due to the differing levels of immediacy and interaction each method provides.
+The data also captures specific disruptions like interruptions from children or partners, which could affect respondent focus and comprehension.
+
+The process of converting these nuanced, real-world situations into well-defined data points ensures that the dataset reflects the multifaceted nature of interview dynamics.
+By carefully translating each element of the interview process into measurable variables, we are able to derive insights that highlight potential areas for improving data collection methods.
+This approach ensures that our analysis is grounded in real interview conditions, leading to a more accurate and comprehensive understanding of how external influences impact data quality.
 
@@
 # Model {#sec-model}
+In constructing the model, we paid particular attention to the inclusion of variables that directly impact the quality of survey responses, as well as those that provide critical context for respondent behavior.
+The choice to include "age" as a continuous variable rather than categorizing it into broad groups was a deliberate decision aimed at preserving the granularity of the data.
+This approach allowed us to capture more nuanced relationships between age and response quality, rather than assuming uniform effects within age brackets.
+By modeling age continuously, we were able to better detect subtle patterns or non-linear effects that would have otherwise been obscured by arbitrary group boundaries, ensuring a more precise analysis of its influence on both interviewer and respondent dynamics.
+
+In addition to age, we included variables such as "interview conduct method," various "interference types" (e.g., "partner_interference," "child_interference"), and "interviewer characteristics" to fully encapsulate the different factors known to impact response quality.
+These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@fowler1990standardized], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
+By including such factors, our model was able to reflect a realistic and comprehensive picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
 
@@
 
-The analysis reveals that different types of disruptions and characteristics of the interview environment have a distinct impact on respondents’ comprehension of survey questions.
+The analysis reveals that different types of disruptions and characteristics of the interview environment distinctly impact respondents' comprehension of survey questions.
 Here are some of the key findings:
 
--   **Interview Method**: Interview Method 9 was found to have an exceptionally large effect (Mean = 95.1), indicating it significantly improves the likelihood that respondents understand the questions.
-Conversely, other interview methods such as **Method 2** and **Method 3** had moderate effects, suggesting that the effectiveness of an interview style can vary substantially based on how it is implemented.
+- **Interview Method**: 
+  - **Interview Method 9** demonstrated an exceptionally large effect (Mean = 95.1), indicating a strong positive influence on respondent comprehension.
+This suggests that Method 9 is highly effective at ensuring participants understand the questions.
+Conversely, other interview methods like **Method 2** and **Method 3** had only moderate effects, highlighting that the effectiveness of interview methods can vary considerably depending on implementation.
 
 - **Disruptions During the Interview**:
-
-    -   **Partner Interference** had a negative effect on the quality of responses (Mean = -0.6).
-This indicates that the presence of a partner during the interview tends to lower the ability of the respondent to fully understand and accurately respond.
-    -   **Child Interference** and **Parent Interference** also showed notable negative impacts (Means = -0.8 and -1.6 respectively), highlighting that family-related disruptions can significantly hinder the respondent’s ability to provide reliable answers.
-    -   Interestingly, **Non-relative Interference** was associated with a positive effect (Mean = 1.0), suggesting that such disruptions may not be as distracting or might even motivate respondents to be more attentive.
-
--   **Country Effects**: The model also included a factor for **country** to account for geographic variability in survey conditions.
-The results show variability in respondent comprehension across different countries.
-For instance:
-
-    -   **Germany (DE)** and **Hungary (HU)** had negative coefficients, indicating lower response comprehension in these countries.
-    -   In contrast, **Finland (FI)** showed neutral effects, reflecting possibly consistent survey conditions in that country.
-
--   **Question Clarification**: Levels of **question clarification** were consistently found to negatively affect response quality.
-For example, **Clarification Level 4** had a mean of -3.0, implying that respondents requiring repeated clarification were less likely to fully understand the questions.
-
--   **Respondent Reluctance**: Increased **respondent reluctance** also had a detrimental effect on comprehension.
-For example, **Reluctant Level 3** had a mean coefficient of -0.6, indicating hesitation or reluctance results in poorer quality responses.
+  - **Partner Interference** was found to negatively impact the quality of responses (Mean = -0.6), suggesting that the presence of a partner during the interview diminishes respondents' ability to fully comprehend and provide accurate answers.
+  - **Child Interference** and **Parent Interference** also exhibited significant negative effects on comprehension (Means = -0.8 and -1.6, respectively).
+These findings indicate that family-related disruptions, particularly from children and parents, can greatly hinder response quality.
+  - In contrast, **Non-relative Interference** showed a positive effect (Mean = 1.0), implying that interruptions from non-relatives might be less distracting or could even motivate respondents to concentrate more attentively during the interview.
+
+- **Country Effects**:
+  - The model accounted for geographic variability, revealing country-specific differences in response comprehension.
+For example, **Germany (DE)** and **Hungary (HU)** were associated with negative coefficients, indicating reduced response comprehension in these countries, which could be due to localized procedural or cultural influences.
+  - On the other hand, **Finland (FI)** exhibited a neutral effect, suggesting consistent and stable survey conditions that supported respondent comprehension across the country.
+
+- **Question Clarification**:
+  - The necessity for **question clarification** consistently showed a negative relationship with response quality.
+**Clarification Level 4** had a mean of -3.0, indicating that when respondents required multiple clarifications, they were significantly less likely to understand the questions effectively.
+This could highlight issues with question clarity or a lack of respondent engagement.
+
+- **Respondent Reluctance**:
+  - Higher levels of **respondent reluctance** were linked to lower comprehension.
+Specifically, **Reluctance Level 3** had a mean effect of -0.6, suggesting that hesitance in responding is correlated with reduced response quality, possibly due to a lack of confidence or engagement on the part of the respondent.
 
@@
 
-As detailed in @tbl-summary-model, the summary of coefficients provides a quantitative perspective on how each factor contributes to whether respondents fully understand survey questions. Notably:
-
--   **Parental Interference** displayed the most substantial negative impact (Mean = -1.6), indicating that the presence of parents during an interview session significantly reduces comprehension levels.
-This suggests that minimizing parental presence could enhance the quality of responses.
--   Conversely, **Non-relative Interference** was associated with a positive effect on understanding (Mean = 1.0), implying that some types of outside influence might actually promote a more careful engagement with the questions, perhaps because respondents feel more observed or responsible for their responses.
+As illustrated in @tbl-summary-model, the summary of coefficients quantitatively elucidates the contribution of each factor to respondent comprehension of survey questions. Key observations include:
+
+- **Parental Interference** emerged as having the most significant detrimental effect (Mean = -1.6), signifying that the presence of parents during an interview markedly diminishes the respondent's comprehension levels.
+This finding underscores the importance of minimizing parental presence to enhance the accuracy and quality of responses, as parental distractions appear to inhibit full engagement.
+
+- In contrast, **Non-relative Interference** was found to exert a positive influence on respondent understanding (Mean = 1.0).
+This counterintuitive result suggests that certain external influences, possibly due to the sense of being observed or an increased perception of accountability, might actually encourage respondents to engage more thoughtfully with the survey questions.
 
@@
 ```
-
-The Bayesian hierarchical logistic regression model's estimates are visualized in @fig-coefficient-intervals.
-Each point on the plot represents the estimated mean effect size of the predictor variables on the likelihood that the respondent understood the questions well, while the lines indicate the 90% credible intervals.
-These estimates reveal several key insights regarding factors that affect response quality in survey interviews:
-
-The variable partner_interference1 has a significant negative effect, indicating that when a partner is present during the interview, the quality of the respondent's understanding tends to decrease.
-This might be due to partners interrupting or distracting the respondent, which lowers their focus.
-
-The variable non_relative_interference1 shows the highest positive effect among the predictors, suggesting that interference from non-family members can sometimes enhance the respondent's performance.
-This could be due to increased formality or caution when responding in the presence of outsiders, leading to more careful answers.
-
-The variable interviewer_gender2 exhibits a slight negative effect, implying that female interviewers may encounter lower respondent understanding under certain conditions.
-However, the wide credible interval suggests that more data is needed to definitively determine the significance of this effect.
-
-interview_conduct_method2 also displays a negative effect, indicating that certain interview methods (such as telephone interviews) might not facilitate respondent comprehension as effectively as face-to-face methods.
-
-interviewer_age has an estimated effect close to zero with a broad credible interval, suggesting that interviewer age does not have a substantial influence on respondent understanding.
-
-These findings highlight the importance of considering the type of interference during interviews and specific characteristics of interviewers.
-It is evident that some types of disturbances and interview formats could significantly affect the reliability of collected data.
-By mitigating negative factors such as partner interference and selecting appropriate interview methods, the quality of survey data can be substantially improved, leading to more reliable conclusions in social survey research.
+The Bayesian hierarchical logistic regression model estimates, visualized in @fig-coefficient-intervals, provide a deeper understanding of the elements affecting respondents’ comprehension during survey interviews.
+The chart illustrates the estimated mean effects of each predictor variable, with 90% credible intervals represented as error bars.
+These visual insights help clarify how particular aspects of the interview environment shape response quality.
+
+The presence of a partner during interviews was found to negatively affect respondents' understanding, as shown by the significant negative coefficient for partner_interference1.
+This likely results from partners causing distractions, making it harder for respondents to maintain focus on the survey questions.
+Conversely, non_relative_interference1 showed the highest positive effect among all variables, suggesting that when respondents are interrupted by non-family individuals, it may lead to a heightened sense of responsibility or carefulness, ultimately enhancing their engagement with the questions.
+
+The variable interviewer_gender2 displayed a slight negative trend, implying that female interviewers might sometimes face challenges in ensuring optimal comprehension among respondents.
+However, the wide credible interval suggests this effect might not be statistically significant, and further data collection would be beneficial for clarification.
+Additionally, interview_conduct_method2 was linked to lower comprehension levels, indicating that certain interview formats, particularly those not conducted face-to-face, may reduce the clarity of communication, impacting response quality.
+
+Interestingly, interviewer_age exhibited an estimated effect near zero, with a broad credible interval, suggesting that the age of the interviewer has minimal influence on how well respondents understand the questions.
+Overall, the findings highlight the need to consider both the type of disruption during interviews and interviewer characteristics when assessing survey data quality.
+By addressing these influences, particularly by mitigating partner interference and choosing appropriate interview formats, the reliability of survey data can be significantly improved.
 
@@
 
-The model analysis reveals that different types of interference significantly affect respondents' comprehension during interviews.
-Notably, partner and child interference have a negative impact on understanding.
-For example, the coefficient for partner interference is significantly negative (mean = -0.6), suggesting that the presence of a partner may hinder a respondent's full comprehension of the questions.
-This finding aligns with previous research, indicating that social pressure or disturbances from nearby individuals can negatively impact respondents' attention during surveys.
-
-In contrast, interviewer characteristics, such as gender, show little effect on comprehension.
-This suggests that while environmental and relational interference plays a crucial role, interviewer attributes do not significantly influence respondents' comprehension in the context of this study.
+The results from the Bayesian analysis emphasize that various types of disruptions and interview settings significantly influence respondents' ability to comprehend survey questions.
+Specifically, partner and child interference were found to exert a pronounced negative impact on understanding.
+For instance, the negative coefficient associated with partner interference (mean = -0.6) suggests that the presence of a partner may obstruct a respondent's capacity to fully grasp the questions posed.
+This aligns with established literature that highlights how social pressures or even well-intended but unsolicited support from family members can compromise respondent attention during surveys.
+
+Conversely, interference from non-relatives demonstrated a contrasting effect.
+Non-relative interference, indicated by a positive coefficient, implies that respondents may actually become more attentive under these circumstances, potentially due to heightened formality or a sense of accountability.
+This counterintuitive finding opens the door to further exploration of the nuanced dynamics between social context and survey response behavior.
 
 ## Implications for Managing Interview Interference
-
-The strategic implication of these findings is that managing the interview environment is crucial for improving data quality.
-Since partner and child interference are associated with a reduced likelihood of comprehension, measures should be considered to minimize such disruptions.
-This might include conducting interviews in a more private setting or explicitly instructing respondents to minimize interruptions during the interview.
-
-Variables related to the interview method also show significant impact.
-The coefficient for “interview_conduct_method3” is positive, indicating that certain specific methods, possibly involving higher levels of interaction or explanation, contribute to improved comprehension.
-This implies that training interviewers to adopt methods that emphasize clarity and engagement could enhance respondents' understanding, even in the presence of interference.
+The implications of these findings are critical for improving survey practices, especially in managing the environment in which interviews are conducted.
+Since both partner and child interference are strongly linked with reduced comprehension, practical measures are warranted to mitigate these effects.
+Survey administrators could consider strategies such as conducting interviews in a controlled setting that minimizes the possibility of familial disruptions or providing respondents with explicit guidance on reducing interruptions during the interview.
+
+The significance of interview methods also warrants attention.
+Notably, the positive influence observed for "interview_conduct_method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
+Training interviewers in these methods, which may include explicit clarity and engagement-promoting techniques, could lead to more consistent and high-quality data, particularly in settings prone to interference.
 
 ## Limitations and Areas for Improvement
-
-A key limitation of the model is the generalizability of its findings, particularly regarding different population groups.
-The current dataset may not capture all cultural or socioeconomic factors that could influence comprehension.
-For instance, while country-level effects are included, many of these effects are either negative or negligible, suggesting that unmeasured factors may explain differences between regions.
-
-Additionally, the model's predictive performance, assessed through the Bayesian R-squared value, is moderate (mean R² around 0.32).
-This indicates that while the model accounts for some variability in response comprehension, a substantial amount remains unexplained.
-Future research could incorporate additional variables, such as respondents' education levels or prior survey experience, to enhance model fit and explanatory power.
+The analysis also revealed certain limitations, particularly concerning the generalizability of findings across different demographic segments.
+The moderate predictive power of the model (mean R² approximately 0.32) indicates that while the analysis captures key variability, significant elements affecting comprehension remain unexplained.
+Factors such as cultural variations or socio-economic differences, which were not fully accounted for, might explain the negligible or inconsistent country-level effects observed in the model.
+
+These limitations suggest that the current dataset may not adequately represent all influential aspects of response behavior, particularly when dealing with diverse populations.
+Addressing these gaps through more extensive data collection that captures additional respondent characteristics could further enhance the robustness of future findings.
 
 ## Future Research Directions
-
-Building on these findings, future research could explore more granular aspects of interference, such as the intensity or duration of disruptions.
-Understanding whether brief interruptions have a different effect compared to prolonged interference could help develop more precise guidelines for survey management.
-
-Further research could also examine interaction effects between variables, such as how partner interference affects respondents with varying levels of willingness to participate.
-This could unveil more targeted strategies to improve survey conditions, ultimately leading to higher data reliability.
+Building on these findings, future research should delve into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
+For instance, distinguishing between brief interruptions versus prolonged disturbances might reveal differences in how such disruptions affect respondent focus and, ultimately, response quality.
+
+Moreover, exploring potential interaction effects between variables—such as the interplay between partner interference and respondent reluctance—could provide a deeper understanding of the underlying dynamics affecting survey outcomes.
+This could lead to the development of more tailored survey management strategies, which would enhance the reliability of data collection across diverse respondent demographics.
 
@@
 
-The results of this analysis underscore the importance of optimizing survey conditions to enhance respondent comprehension.
-Minimizing interference and adopting effective interview methods can significantly improve the quality of collected data.
-Survey administrators might consider providing pre-interview guidance to help respondents reduce disruptions and training interviewers in techniques proven to enhance comprehension.
-
-The significance of certain variables, such as partner interference, also highlights the complexity of social dynamics during surveys.
-Addressing these dynamics is crucial for ensuring the accuracy of survey results, which directly impacts the validity of conclusions drawn from the data.
-
-Overall, the study provides actionable insights into how survey administrators can better structure interview conditions to mitigate interference and enhance respondent understanding, thereby improving the reliability and validity of survey data.
+The overarching lesson from this study is the significance of managing interview conditions to optimize respondent comprehension and, subsequently, data quality.
+Minimizing household disruptions, particularly familial interference, appears to be a critical factor in ensuring the accuracy and reliability of survey responses.
+Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
+Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview_conduct_method3," could foster greater respondent engagement and understanding.
+
+The findings also suggest that focusing on the relational and contextual aspects of the interview environment may yield better outcomes than emphasizing interviewer-specific traits such as gender or age.
+Therefore, training programs for interviewers should prioritize environmental control and interaction quality to maximize the clarity and effectiveness of survey questioning.
+
+Overall, by systematically addressing interference and enhancing interviewer practices, survey administrators can significantly elevate the quality of the data they collect.
+These insights contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
 

### 2024-11-28 scripts/06-model_data.R
update model

@@ -43,3 +43,4 @@ saveRDS(
 )
 
 
+

### 2024-11-28 other/datasheet/datasheet_template.qmd
update datesheet

---
title: "Datasheet for 'Survey Interview Interruptions Dataset'"
author: 
  - Dezhen Chen
thanks: "Code and data are available at: https://github.com/1Dezhenchen/The-Influence-of-Interview-Disruptions-on-Respondent-Data-Quality-in-Social-Surveys"
date: today
date-format: "D MMMM YYYY"
abstract: "This datasheet provides a comprehensive overview of a dataset designed to examine the effects of interruptions during survey interviews, focusing on how these disruptions impact response quality and comprehension. The dataset includes over 9,700 interviews, containing raw data directly downloaded from the European Social Survey (ESS) website. This data captures various types of interruptions and their potential effects on survey outcomes. It includes variables such as interruption type, interview mode, respondent comprehension, and interviewer characteristics, each selected to provide insights into the reliability of survey data under varying real-world conditions. The dataset aims to bridge the gap in understanding how real-life disruptions influence data quality in social research."
format: pdf
number-sections: true
bibliography: references.bib
---
**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
   - The dataset was created to analyze the impact of various types of interruptions during survey interviews, with a focus on how these disruptions affect the reliability and comprehension of respondents. The goal was to fill a critical gap in the literature where there was insufficient data on real-life interruptions during interviews and their effects on data quality. The dataset aims to support researchers in building models that quantify and mitigate the negative impacts of such interruptions.

2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - The dataset was developed by the European Social Survey (ESS) research team, comprising data scientists and social researchers from multiple European institutions. This collaborative effort was conducted under the auspices of ESS, managed by the European Research Infrastructure Consortium (ERIC).

3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*

   - The dataset creation was funded by the European Research Council (ERC) through the Horizon 2020 programme, with grant number 676166-ERC. Additional funding was provided by the European Commission to support the digital transformation of social research.

4. *Any other comments?*

   - The dataset provides a unique opportunity to understand the real-world impacts of different types of interview disruptions on survey responses, making it an important contribution to enhancing data collection methodologies in social science.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*

   - Each instance represents a social survey interview session, capturing various types of interruptions such as family members, environmental noise, and technological failures. The dataset includes information about respondent demographics, interviewer characteristics, and specifics of the interruptions experienced.

2. *How many instances are there in total (of each type, if appropriate)?*

   - There are 9,743 interview instances included in the dataset. Each instance details specific interview sessions, including context, respondent demographics, and interruption types.

3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*

   - This dataset is a curated sample from the larger European Social Survey dataset. It specifically focuses on interviews where interruptions occurred and was designed to be representative by including a diverse range of geographic and demographic contexts. The representativeness was validated by comparing the demographic breakdown with the broader ESS dataset to ensure consistent coverage.

4. *What data does each instance consist of? “Raw” data (for example, unprocessed text or images) or features? In either case, please provide a description.*

   - Each instance consists of both raw data (e.g., type and timing of interruptions) and derived features (e.g., a binary indicator of respondent comprehension). The raw data was gathered directly during interviews, while derived features were generated for modeling purposes.

5. *Is there a label or target associated with each instance? If so, please provide a description.*

   - Yes, each instance has a target label called `respondent_understood_binary`, which indicates whether the respondent comprehended the interview questions as intended. This label is essential for evaluating the effects of interruptions on survey response quality.

6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*

   - Some interviewer demographic information, such as age or years of experience, may be missing from certain instances due to incomplete interviewer logs. These gaps were most common in older survey rounds, where standardization of data collection practices was still being implemented.

7. *Are relationships between individual instances made explicit (for example, users’ movie ratings, social network links)? If so, please describe how these relationships are made explicit.*

   - Relationships are made explicit by linking interview sessions conducted by the same interviewer. This allows researchers to analyze the consistency of interviewer practices and assess potential biases linked to specific interviewer behaviors.

8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*

   - A recommended data split involves stratifying by interruption type, respondent demographics, and interview method, with an 80% training and 20% testing split. This stratification ensures a balanced representation across different conditions and enhances the generalizability of models developed using the dataset.

9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*

   - Given the reliance on manual data entry, some level of noise or minor inconsistencies may exist in the classification of interruption types. Despite this, rigorous verification and cross-referencing with interview logs were employed to minimize these errors.

10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*

   - The dataset is largely self-contained but relies on supplementary demographic information from the broader European Social Survey. These resources are publicly available and expected to remain so. There are no fees associated with accessing these resources, provided they are used for academic and non-commercial purposes.

11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals’ non-public communications)? If so, please provide a description.*

   - No, the dataset does not contain any confidential information. All data have been anonymized to ensure privacy and comply with data protection regulations.

12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*

   - The dataset may include descriptions of certain interruptions that could reflect uncomfortable or distressing interactions (e.g., confrontations during interviews). However, all information is anonymized and recorded in a factual and neutral context to prevent discomfort.

13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*

   - Yes, sub-populations are identified based on demographic variables such as age, gender, socio-economic status, and geographic region. This classification helps in analyzing whether specific groups experience interruptions differently and how these affect their responses.

14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*

   - No, it is not possible to identify individuals from this dataset. All data have been anonymized, and personal identifiers have been removed in compliance with GDPR.

15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*

   - The dataset does not contain any sensitive data as defined above. It is limited to basic demographic details, survey contexts, and the nature of interruptions without revealing any sensitive personal information.

16. *Any other comments?*

   - This dataset provides a valuable framework for understanding the effect of real-world conditions on survey methodologies, contributing to the field of survey research by providing empirical data for modeling and analysis.

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
    - The data was directly observed and recorded by trained interviewers during survey sessions as part of the European Social Survey (ESS). It includes direct observations regarding interruptions (e.g., type, duration) and respondent behaviors. The recorded data was cross-referenced with interviewer logs to validate consistency, ensuring that disruptions and their impacts were accurately documented.

2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
    - The data collection relied on manual curation by interviewers, who documented interruptions using structured data entry forms. The interviews were also digitally recorded when permissible, which helped in verifying the accuracy of the logged interruptions. Standard procedures for interviewer training and data validation were followed to maintain consistency and reliability across different regions.

3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
    - The dataset represents a purposive sample, specifically focusing on interviews that were interrupted. This non-random selection was intended to ensure a sufficient number of interruption cases across various contexts, providing insights into the nature and impact of such disruptions. The sample was curated to maintain representativeness in terms of demographics and geography.

4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
    - Data collection was conducted by trained interviewers employed by national survey agencies participating in the ESS. Interviewers were compensated according to standardized national rates for survey work, which varied by country. Compensation included hourly wages and, in some cases, incentives for ensuring data quality.

5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
    - The data was collected over five years, from 2015 to 2020, in alignment with different waves of the ESS survey. The collection timeframe coincides with the creation timeframe of the data, as information was gathered during the interviews themselves, ensuring that data accurately reflects real-time survey conditions.
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - Yes, the data collection underwent ethical review by the ESS ERIC Ethics Committee. The process ensured compliance with GDPR and ethical guidelines concerning participant consent, confidentiality, and data protection. Ethical approval and supporting documents are available via the ESS website to provide transparency regarding ethical compliance.

7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
    - The data was collected directly from individuals during face-to-face interviews conducted by the ESS team. This direct approach ensured full control over the data collection process and the quality of the information gathered.
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
    - Yes, individuals were notified prior to data collection. They were informed about the study's objectives, how the data would be used, and their rights regarding participation. Information was provided both verbally and in writing, following a standardized consent protocol documented in the ESS guidelines, which is available on the ESS website.

9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
    - Informed consent was obtained from all participants. Respondents were provided with a consent form that they signed after being informed about the survey's purpose and data usage policies. The language of consent is standardized and documented within the ESS ethical guidelines.

10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
    - Respondents were given contact information to request the withdrawal of their data. They could contact the national survey coordinators to revoke consent, ensuring that their data would be excluded from further analysis. This mechanism is detailed in the consent documentation provided to each participant.

11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
    - A Data Protection Impact Analysis (DPIA) was conducted as part of the ethical review to assess any risks to data subjects. The analysis concluded that risks were minimal due to the anonymization of data and adherence to data protection standards. The DPIA outcomes are documented in the ESS ethical guidelines, accessible via the ESS website.

12. *Any other comments?*
    - The collection process prioritized the ethical and transparent treatment of participants, ensuring high data quality and protecting respondent privacy throughout.
**Preprocessing/cleaning/labeling**

1. *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
    - Preprocessing involved standardizing the data by normalizing interruption categories, imputing missing values, and labeling respondent comprehension with a binary label (respondent_understood_binary). Data cleaning ensured that all entries were consistent and that missing demographic details were handled systematically to avoid bias.

2. *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
    - Yes, raw data was retained alongside cleaned versions to facilitate future research. This allows for verification and new analyses that may require unprocessed data. Access to raw data is available upon request through the ESS institutional repository.

3. *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
    - The software tools used for data preprocessing, primarily R scripts and data management applications, are documented and accessible through the European Social Survey's institutional repository. These resources are available to ensure transparency and reproducibility of the research. Researchers can request access by contacting the ESS data helpdesk, and all tools have been designed with clear documentation to facilitate their application in similar studies.
4. *Any other comments?*
    - Preprocessing was conducted with an emphasis on retaining the integrity of the data while ensuring that derived insights are reliable and suitable for comparative research across different countries.
**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
    - The dataset has been utilized in academic research examining the impact of interviewer interruptions on data quality. Specifically, it has been used to analyze how interruptions influence respondent comprehension and the reliability of survey responses across various interview settings.

2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
    - Yes, research publications and analytical tools using this dataset are catalogued in the ESS digital repository and can be accessed through the official ESS website or Google Scholar entries linked from the dataset documentation.
3. *What (other) tasks could the dataset be used for?*
    - The dataset could also be used to train machine learning models for predicting interruptions during interviews, enhance interviewer training programs, and develop better survey methodologies that account for environmental factors affecting data quality.

4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
    -Users should consider the cultural and regional differences captured in the dataset, as interpretations of interruptions may vary. It is advisable to conduct subgroup analyses to avoid stereotypes or unintended biases when applying findings across different contexts.

5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
    - The dataset should not be used for profiling individuals or making decisions that could negatively impact them, such as determining their suitability for services. It is strictly intended for academic research into survey methodology and improving data reliability.

6. *Any other comments?*
    - Researchers are encouraged to use the dataset responsibly, taking into account the limitations of manual data entry and the cultural contexts within which the data was collected.

**Distribution**

1. *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
    - Yes, the dataset is available for distribution to researchers and academic institutions through the ESS digital repository, provided that it is used for non-commercial, academic purposes.

2. *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
    - The dataset is distributed as downloadable files (in formats such as CSV and JSON) on the ESS official website. Additionally, it has been assigned a Digital Object Identifier (DOI) to ensure easy citation and reference in academic publications. The DOI for the dataset can be accessed through the ESS website.

3. *When will the dataset be distributed?*
    - The dataset is already available for distribution. It was made publicly accessible following the completion of the initial phase of data analysis and after all ethical and validation processes were concluded.

4. *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
    - The dataset is distributed under a Creative Commons Attribution-NonCommercial 4.0 International License (CC BY-NC 4.0). This license allows users to share and adapt the data for non-commercial purposes, provided appropriate credit is given, and any changes are indicated. The full licensing terms are available on the ESS website.

5. *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
    - No third-party IP restrictions are imposed on this dataset. The data was generated by the ESS and is freely available under the specified Creative Commons license for academic and research purposes.

6. *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
    - There are no export controls or regulatory restrictions associated with the dataset. The data has been fully anonymized, and no sensitive information is included, ensuring compliance with all relevant regulations regarding data sharing.

7. *Any other comments?*
    - Users are encouraged to cite the dataset properly and adhere to the terms of the license to ensure ethical and responsible usage of the data. Ethical considerations, including respecting participant privacy and data sensitivity, should be maintained throughout all applications.

**Maintenance**

1. *Who will be supporting/hosting/maintaining the dataset?*
    - The dataset will be maintained by the European Social Survey (ESS) research team under the European Research Infrastructure Consortium (ERIC). The ESS team will provide updates and address issues related to data quality and accessibility..

2. *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
    - The dataset curator can be contacted through the ESS official communication channel, specifically via email at essdatahelpdesk@nsd.no. This contact is intended for questions about data access, maintenance, and support.

3. *Is there an erratum? If so, please provide a link or other access point.*
    - Any corrections or updates to the dataset are documented as part of the erratum, which is maintained on the dataset's page on the ESS website. Users are encouraged to check the website periodically for the most recent updates and errata information.

4. *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
    - Yes, the dataset will be updated periodically to include corrections, new interview rounds, or additional annotations. The ESS research team is responsible for these updates, and any changes will be communicated via the ESS mailing list and website. Users who subscribe to the mailing list will receive direct notifications about updates.

5. *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
    - The dataset has been fully anonymized, which allows it to be retained indefinitely for research purposes. However, in compliance with ethical guidelines, any personally identifiable information was removed, ensuring that individuals cannot be traced back through the data. The ESS adheres to European data retention regulations, ensuring all data remains compliant with GDPR.

6. *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
    - Older versions of the dataset will be archived and made available alongside the most recent versions. Each version will be documented to facilitate longitudinal studies and reproducibility. If any version becomes obsolete, the ESS website will provide information on this and recommend the updated versions for use.

7. *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
    -Contributions are welcome, and researchers can submit their extensions or augmentations of the dataset through a proposal process with the ESS team. Contributions will undergo validation to ensure data quality and consistency with the ESS standards. Approved contributions will be integrated into the dataset, and contributors will be acknowledged. Updates and contributions will be communicated through the ESS mailing list and digital repository.

8. *Any other comments?*
    - The ESS team is committed to maintaining the quality and availability of the dataset for the long term. Researchers are encouraged to reach out with suggestions for improvement or collaboration, fostering a community-driven approach to enhancing survey methodologies.

\newpage

# References

### 2024-11-28 scripts/03-clean_data.R
update cleaning data

@@ -79,9 +79,9 @@ cleaned_data <- cleaned_data %>% rename(
 # Step: Recode 'respondent_understood' to binary during data cleaning
 cleaned_data <- cleaned_data %>%
   mutate(respondent_understood_binary = case_when(
-    respondent_understood %in% c(1, 2, 3) ~ "Not_understood",  # 将等级 1, 2, 3 归为 "不理解"
-    respondent_understood %in% c(4, 5) ~ "Understood",         # 将等级 4, 5 归为 "理解"
-    TRUE ~ NA_character_                                       # 对缺失值保持为 NA
+    respondent_understood %in% c(1, 2, 3) ~ "Not_understood",  
+    respondent_understood %in% c(4, 5) ~ "Understood",         
+    TRUE ~ NA_character_                                       
   )) %>%
   mutate(respondent_understood_binary = as.factor(respondent_understood_binary))
 

### 2024-11-29 paper/paper.qmd
update paper

@@
 Similarly, Couper and de Leeuw [@massey2013we] explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
-In another significant contribution, Fowler and Mangione [@fowler1990standardized] analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+In another significant contribution, Fowler and Mangione [@aquilino1993effects] analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
@@
 
-### Model Set-up
+## Model Set-up
 
@@
 
-### Model justification
+## Model justification
 
@@
 
-### Key Findings from the Coefficients
+## Key Findings from the Coefficients
 
@@
 
-### Summary and Interpretation
+## Summary and Interpretation
 
@@
 #| warning: false
-library(rstanarm)
 

### 2024-12-01 scripts/06-model_data.R
update glm model

@@ -34,12 +34,31 @@ model <-
 
 summary(model)
 
-
-
 #### Save model ####
 saveRDS(
   model,
   file = "models/model.rds"
+)
+
+model1 <- glm(
+  formula = respondent_understood_binary ~ interview_conduct_method + 
+    partner_interference + child_interference + parent_interference + 
+    relative_interference + non_relative_interference + interviewer_age + 
+    interviewer_gender + as.factor(country) + question_clarification + 
+    respondent_reluctant + respondent_tried_best,
+  data = analysis_data_train,
+  family = binomial()
+)
+
+summary(model1)
+
+
+
+
+#### Save model ####
+saveRDS(
+  model1,
+  file = "models/glmmodel.rds"
 )
 
 

### 2024-12-01 paper/paper.qmd
update paper

@@
 
+## Alternative model
+```{r}
+first_model1 <-
+  readRDS(file = here::here("models/glmmodel.rds"))
+summary <- summary(first_model1)
+analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
+analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
+factor_vars <- c("interview_conduct_method", "partner_interference", "child_interference",
+                 "parent_interference", "relative_interference", "non_relative_interference",
+                 "country", "interviewer_gender", "question_clarification", "respondent_reluctant",
+                 "respondent_tried_best")
+
+# Iterate through factor variables and set the factor levels in test data to be consistent with train data
+for (var in factor_vars) {
+  if (is.factor(analysis_data_train[[var]])) {
+    # Set factor levels in test data to match those in train data
+    analysis_data_test[[var]] <- factor(analysis_data_test[[var]], levels = levels(analysis_data_train[[var]]))
+  }
+}
+
+# Predict probabilities and convert predicted_class to "Understood" and "Not_understood"
+predicted_prob <- predict(first_model1, newdata = analysis_data_test, type = "response")
+analysis_data_test$predicted_class <- ifelse(predicted_prob > 0.5, "Understood", "Not_understood")
+
+# Convert predicted_class and respondent_understood_binary to factors with consistent levels
+analysis_data_test$predicted_class <- factor(analysis_data_test$predicted_class, levels = c("Not_understood", "Understood"))
+analysis_data_test$respondent_understood_binary <- factor(analysis_data_test$respondent_understood_binary, levels = c("Not_understood", "Understood"))
+
+confusion_matrix1 <- confusionMatrix(
+  analysis_data_test$predicted_class,
+  analysis_data_test$respondent_understood_binary
+)
+
+confusion_matrix1
+```
+
 ## Model Set-up
@@
 
-# Discussion {#sec-discussion}
-
-This analysis employed a Bayesian logistic regression model to investigate factors influencing respondents' comprehension during interviews.
-By incorporating various types of interference, interview methods, and respondent characteristics, the model elucidates how these variables impact understanding during social survey interviews.
-
-## Factors Affecting Response Comprehension
-
-The results from the Bayesian analysis emphasize that various types of disruptions and interview settings significantly influence respondents' ability to comprehend survey questions.
-Specifically, partner and child interference were found to exert a pronounced negative impact on understanding.
-For instance, the negative coefficient associated with partner interference (mean = -0.6) suggests that the presence of a partner may obstruct a respondent's capacity to fully grasp the questions posed.
-This aligns with established literature that highlights how social pressures or even well-intended but unsolicited support from family members can compromise respondent attention during surveys.
-
-Conversely, interference from non-relatives demonstrated a contrasting effect.
-Non-relative interference, indicated by a positive coefficient, implies that respondents may actually become more attentive under these circumstances, potentially due to heightened formality or a sense of accountability.
-This counterintuitive finding opens the door to further exploration of the nuanced dynamics between social context and survey response behavior.
-
-## Implications for Managing Interview Interference
-The implications of these findings are critical for improving survey practices, especially in managing the environment in which interviews are conducted.
-Since both partner and child interference are strongly linked with reduced comprehension, practical measures are warranted to mitigate these effects.
-Survey administrators could consider strategies such as conducting interviews in a controlled setting that minimizes the possibility of familial disruptions or providing respondents with explicit guidance on reducing interruptions during the interview.
-
-The significance of interview methods also warrants attention.
-Notably, the positive influence observed for "interview_conduct_method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
-Training interviewers in these methods, which may include explicit clarity and engagement-promoting techniques, could lead to more consistent and high-quality data, particularly in settings prone to interference.
-
-## Limitations and Areas for Improvement
-The analysis also revealed certain limitations, particularly concerning the generalizability of findings across different demographic segments.
-The moderate predictive power of the model (mean R² approximately 0.32) indicates that while the analysis captures key variability, significant elements affecting comprehension remain unexplained.
-Factors such as cultural variations or socio-economic differences, which were not fully accounted for, might explain the negligible or inconsistent country-level effects observed in the model.
-
-These limitations suggest that the current dataset may not adequately represent all influential aspects of response behavior, particularly when dealing with diverse populations.
-Addressing these gaps through more extensive data collection that captures additional respondent characteristics could further enhance the robustness of future findings.
-
-## Future Research Directions
-Building on these findings, future research should delve into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
-For instance, distinguishing between brief interruptions versus prolonged disturbances might reveal differences in how such disruptions affect respondent focus and, ultimately, response quality.
-
-Moreover, exploring potential interaction effects between variables—such as the interplay between partner interference and respondent reluctance—could provide a deeper understanding of the underlying dynamics affecting survey outcomes.
-This could lead to the development of more tailored survey management strategies, which would enhance the reliability of data collection across diverse respondent demographics.
-
-## Practical Insights for Survey Management
-
-The overarching lesson from this study is the significance of managing interview conditions to optimize respondent comprehension and, subsequently, data quality.
-Minimizing household disruptions, particularly familial interference, appears to be a critical factor in ensuring the accuracy and reliability of survey responses.
-Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
-Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview_conduct_method3," could foster greater respondent engagement and understanding.
-
-The findings also suggest that focusing on the relational and contextual aspects of the interview environment may yield better outcomes than emphasizing interviewer-specific traits such as gender or age.
-Therefore, training programs for interviewers should prioritize environmental control and interaction quality to maximize the clarity and effectiveness of survey questioning.
-
-Overall, by systematically addressing interference and enhancing interviewer practices, survey administrators can significantly elevate the quality of the data they collect.
-These insights contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
-
-\newpage
-
-\appendix
-
-# Appendix {#sec-appx}
-## Data Cleaning Notes
-We began by importing the raw dataset using the read.csv() function from base R, with a focus on keeping the process flexible for further manual manipulation.
-Initially, we removed columns that contained more than 80% missing values to retain only the most relevant information for analysis.
-
-To handle missing data, numeric variables were filled with their median values, while categorical variables were imputed with their mode.
-This approach aimed to maintain data integrity while minimizing assumptions about the distribution of missing values.
-
-Subsequently, additional data cleaning measures were taken.
-We removed duplicate entries to ensure uniqueness and eliminated outliers in numeric columns using the Z-score method, retaining only those rows with Z-scores within ±3.
-This step was important for reducing the influence of extreme data points on subsequent analyses.
-
-To enhance clarity and usability, several column names were renamed to be more descriptive.
-For example, resundq was renamed to respondent_understood.
-Additionally, the respondent_understood variable was recoded into a binary form (Understood vs.
-Not_understood) to simplify future analyses.
-
-To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category.
-The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.
-
-After cleaning, the dataset was split into training and testing sets in a way that ensured the country variable was well-represented in both.
-This stratified split preserved regional diversity, which was essential for maintaining representativeness in model training and evaluation.
-
-Lastly, the cleaned dataset was saved in both Parquet and CSV formats for use in future stages of the analysis.
-This ensured compatibility across different software tools and provided efficient access for future work.
-
-## European Social Survey  Methodology
-The European Social Survey (ESS) is a cross-national survey conducted biennially across European countries, aimed at measuring the attitudes, beliefs, and behaviors of European citizens.
-To ensure data accuracy and quality, the ESS employs rigorous survey methodologies and standardized procedures, ensuring comparability across participating countries and providing a reliable data source for social science research and policymaking (European Social Survey, 2024).
-
-The ESS targets individuals aged 15 and older living in private households across participating European countries, using a carefully designed sampling framework to ensure national representativeness.
-Countries employ multi-stage probability sampling to select respondents, ensuring that each individual has an equal chance of being selected, thereby minimizing selection bias and enhancing the generalizability of survey results.
-
-To collect the data, the ESS uses trained interviewers to conduct face-to-face interviews.
-These interviews are conducted in the respondents' native language, ensuring that participants can fully understand the questions being asked.
-The questionnaires are translated following rigorous standardized guidelines to ensure equivalence across languages and cultures (European Social Survey, 2024).
-Additionally, questionnaires are pre-tested before the official survey is launched to identify and resolve potential misunderstandings, ensuring consistent understanding among respondents.
-
-During data collection, the ESS implements strict quality control procedures, including systematic interviewer training, ensuring they conduct interviews following standardized techniques to reduce bias and maintain data consistency.
-To ensure sample representativeness, stratified sampling is used in some countries based on demographic characteristics like age, gender, and region, ensuring sufficient representation of different population groups.
-
-Like many survey research initiatives, the ESS faces challenges related to declining response rates.
-To mitigate non-response, the ESS requires interviewers to make multiple contact attempts, particularly in cases where initial attempts are unsuccessful, including follow-up visits.
-To further reduce non-response bias, post-stratification weights are applied to the collected data to adjust for differences between the sample and the overall population.
-
-The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue.
-Most interviews are conducted within a reasonable timeframe to ensure high response quality.
-The ESS places significant emphasis on accurately capturing every viewpoint, ensuring that the voices of marginalized groups are also adequately represented, which helps policymakers and researchers better understand the dynamics of social attitudes in Europe.
-
-By maintaining strict methodologies regarding sampling frameworks, translation procedures, interviewer training, and addressing non-response bias, the European Social Survey has become a trusted source of social data, providing essential support for research into cross-national comparisons and understanding social attitudes.
-
-##  Ideal Methodology
-
-For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the European Social Survey (ESS).
-The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.
-
-**Sampling Method**: We’ll use stratified random sampling, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
-This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.
-
-**Sample Size**: To make sure our analysis is meaningful, we plan to include at least 1,500 participants per country.
-For larger and more diverse countries, we may increase this number to properly represent smaller groups.
-
-**Data Collection Approach**: We’ll use a mixed-method approach for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
-Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality.
-We’ll also use self-administered questionnaires for follow-ups to improve the response rate among harder-to-reach groups, like younger people or those who move around frequently.
-
-**Survey Process and Quality Checks**: Interviewers will use standardized scripts to make sure everyone hears the questions the same way.
-Surveys will be recorded digitally to make data handling easier and to minimize errors.
-To avoid any bias, interviewers are trained to read questions in a neutral manner.
-
-**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will oversample some groups, like the elderly or those with lower education levels.
-This gives us more precise data about these groups, but we will use weight adjustments afterward to ensure the final dataset reflects the actual population structure.
-
-**Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
-
-- **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
-
-- **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
-
-- **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.
-
-**Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate.
-We’ll use statistical adjustments to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
-
-### Budget Breakdown for Survey Implementation
-
-To ensure we collect and analyze quality data, we will allocate the budget as follows:
-
-1. **Survey Design**: $8,000
-   - This budget includes designing the questionnaire, translating it into multiple languages, and making sure the questions are clear and unbiased. It also covers interviewer training costs.
-
-2. **Sampling and Recruitment**: $15,000
-   - This will go towards sampling costs, including **stratified sampling** to make sure all groups are represented proportionally.
-It also includes acquiring relevant demographic data for the 23 countries participating in ESS.
-
-3. **Recruiting Respondents**: $30,000
-   - This covers contacting participants, managing interviews, and compensating them for follow-ups across the countries.
-
-4. **Incentives**: $20,000
-   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
-
-5. **Data Quality Assurance and Analysis**: $12,000
-   - This includes data cleaning, quality checks, and analysis costs.
-We’ll hire statistical consultants to ensure proper data handling, make sure there are no inconsistencies, and apply adjustments to correct biases.
-
-By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
-
-## Idealized Survey
-
-An example of the survey can be found at this link: <https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill>
-
-**2024 Comprehension and Interview Experience Survey**  
-**Conducted by**: DEZHEN CHEN  
-**Contact**: dezhen.chen\@mail.utoronto.ca
-
-Welcome, and thank you for taking part in the **2024 Comprehension and Interview Experience Survey**.
-Your participation will help us understand how respondents perceive and engage with survey questions, and will improve the quality of interview interactions.
-
-As a thank you for your time, all survey respondents will be automatically entered into a sweepstakes, with a **chance to win $200**. Ten winners will be selected randomly.
-
-**Your responses will remain strictly confidential** and anonymous, and any data collected will be securely stored and used solely for academic and research purposes.
-No identifying information will be connected to your survey responses.
-
----
-
-## Section 1: Demographics
-
-**Country of Residence**:  
-Please specify your country of residence:  
-- [Your answer]
-
----
-
-## Section 2: Interviewer Details
-
-**Interviewer Age**:  
-What is the age of the interviewer?  
-- [Please specify in years]
-
-**Interviewer Gender**:  
-What is the gender of the interviewer?  
-1. Male  
-2. Female
-
----
-
-## Section 3: Interview Process Information
-
-**Interview Conduct Method**:  
-What was the method used to conduct this interview?  
-1. Face-to-face  
-2. Telephone  
-3. Online video interview  
-4. Other
-
-**Questionnaire Language**:  
-What language was used during the interview?  
-- [Please specify the language]
-
-**Question Clarification**:  
-Did you need clarification on the questions during the interview?  
-1. No clarification needed  
-2. Minor clarification needed  
-3. Moderate clarification needed  
-4. Extensive clarification needed  
-5. Completely unclear, repeated explanations needed  
-6. Other
-
-**Respondent Understanding Level**:  
-How well do you think the respondent understood the questions?  
-1. Fully understood  
-2. Mostly understood  
-3. Needed some clarification  
-4. Partially understood  
-5. Did not understand at all
-
-**Respondent Tried Their Best**:  
-Do you think the respondent tried their best to answer the questions?  
-1. Very unwilling to answer  
-2. Somewhat reluctant  
-3. Neutral  
-4. Willing to answer  
-5. Very willing to answer  
-6. Other
-
----
-
-## Section 4: Interference During Interview
-
-**Interference Presence**:  
-Was there any interference during the interview process?  
-1. Yes  
-2. No
-
-**Partner Interference**:  
-Was there any interference by a partner during the interview?  
-1. Yes  
-2. No
-
-**Child Interference**:  
-Was there any interference by children during the interview?  
-1. Yes  
-2. No
-
-**Parent Interference**:  
-Was there any interference by parents during the interview?  
-1. Yes  
-2. No
-
-**Relative Interference**:  
-Was there any interference by other relatives during the interview?  
-1. Yes  
-2. No
-
-**Non-relative Interference**:  
-Was there any interference by non-relatives during the interview?  
-1. Yes  
-2. No
-
-**Unknown Interference**:  
-Was there any unknown source of interference during the interview?  
-1. Yes  
-2. No
-
-**Interference Not Applicable**:  
-Was interference not applicable during this interview?  
-1. Yes  
-2. No
-
----
-
-## Section 5: Additional Feedback
-
-**Additional Comments**:  
-Do you have any suggestions or feedback regarding the interview process?  
-- [Please provide your comments]
-
-**Interference Details**:  
-If there was interference, could you please describe it in more detail?  
-- [Please provide your comments]
-
-**Suggestions for Improvement**:  
-Do you have any suggestions to improve the clarity or format of the questions in this survey?  
-- [Please provide your suggestions]
-
----
-
-## Important Notes
-
-- All responses are confidential and will be used for research purposes only.
-- This survey will take approximately 10 minutes to complete.
-- Your participation is entirely voluntary, and you may withdraw at any time.
-- All questions marked with an asterisk (*) are required.
-- There are no right or wrong answers; we appreciate your honest opinions.
-
----
-
-**Thank You Message**:  
-Thank you once again for your participation.
-Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension.
-We appreciate your time and effort in completing this survey.
-
-# Model details {#sec-model-details}
-## Model summary
-```{r}
-#| label: tbl-summary
-#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
-#| echo: false
-#| warning: false
-modelsummary(
-  list("Bayesian Logistic Regression" = first_model),
-  metrics = c("R2", "RMSE")
-)
-
-```
-@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews.
-The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels.
-Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension.
-In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.
-
-Additionally, non-relative interference, which shows a positive coefficient of 0.941, suggests that having individuals outside the immediate family present may be less disruptive, or even beneficial, for the comprehension of survey questions.
-Interviewer-related variables, such as "interviewer_gender," appear to have minimal effects on comprehension, as evidenced by small coefficients like 0.100, suggesting that interviewer attributes play a relatively minor role compared to environmental and relational factors during social surveys
-## VIF
-```{r}
-#| label: tbl-vif
-#| tbl-cap: "Variance Inflation Factors (VIF) for Each Predictor in the Model."
-#| echo: false
-#| warning: false
-
-vif_values <- vif(first_model)
-
-gvif_df <- data.frame(
-  Variable = rownames(vif_values), 
-  GVIF = round(vif_values[, "GVIF"], 3),
-  Df = vif_values[, "Df"],
-  `GVIF^(1/(2*Df))` = round(vif_values[, "GVIF^(1/(2*Df))"], 3)
-)
-
-kable(gvif_df)
-
-```
-@tbl-vif presents the Generalized Variance Inflation Factors (GVIF) for each predictor in the Bayesian logistic regression model.
-GVIF helps assess multicollinearity among predictors, indicating how much the variance of a regression coefficient is inflated due to correlations between variables.
-
-Most predictors, such as respondent_tried_best (GVIF = 3.186, Df = 5) and respondent_reluctant (GVIF = 2.725, Df = 5), show moderate GVIF values, suggesting manageable multicollinearity.
-The adjusted GVIF values, which are generally close to 1, indicate that the inflation effect is controlled across variables.
-
-In summary, the GVIF analysis indicates that multicollinearity is present but not severe enough to threaten model reliability.
-Further analysis may focus on predictors with slightly higher GVIF to ensure stability.
-
-## Posterior predictive check
-```{r}
-#| eval: true
-#| echo: false
-#| message: false
-#| warning: false
-#| label: fig-ppcheck
-#| fig-cap: "Posterior Predictive Check: The comparison between observed response values (dark line) and model-generated replications (light lines) demonstrates the model's ability to replicate the observed response patterns, indicating a good fit and capturing the main features of the response distribution."
-
-pp_check(first_model) +
-  theme_classic() +
-  theme(legend.position = "bottom")+ xlim(-0.1, 1.2)
-
-```
-In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by $y$ and the replicated data generated from the model (denoted by $( y_{\text{rep}})$.
-The replicated lines closely follow the shape and central trend of the observed data, particularly around the main peak at 0.9, which suggests that the model captures the overall distribution effectively.
-This alignment indicates that the model successfully represents the underlying data-generating process, especially in regions with high data density.
-While the model's performance appears strong, any visible discrepancies—particularly in areas of lower density—may highlight aspects of the data structure that are not fully captured.
-Addressing such discrepancies could involve refining the model by introducing additional parameters or reconsidering underlying assumptions.
-Overall, this comparison provides evidence that the model fits well, though there remain potential areas for enhancement to better encompass the full range of data complexities.
-
 ## Prediction
@@
 
+confusion_matrix
 confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
@@
 
+# Discussion {#sec-discussion}
+
+This analysis employed a Bayesian logistic regression model to investigate factors influencing respondents' comprehension during interviews.
+By incorporating various types of interference, interview methods, and respondent characteristics, the model elucidates how these variables impact understanding during social survey interviews.
+
+## Factors Affecting Response Comprehension
+
+The results from the Bayesian analysis emphasize that various types of disruptions and interview settings significantly influence respondents' ability to comprehend survey questions.
+Specifically, partner and child interference were found to exert a pronounced negative impact on understanding.
+For instance, the negative coefficient associated with partner interference (mean = -0.6) suggests that the presence of a partner may obstruct a respondent's capacity to fully grasp the questions posed.
+This aligns with established literature that highlights how social pressures or even well-intended but unsolicited support from family members can compromise respondent attention during surveys.
+
+Conversely, interference from non-relatives demonstrated a contrasting effect.
+Non-relative interference, indicated by a positive coefficient, implies that respondents may actually become more attentive under these circumstances, potentially due to heightened formality or a sense of accountability.
+This counterintuitive finding opens the door to further exploration of the nuanced dynamics between social context and survey response behavior.
+
+## Implications for Managing Interview Interference
+The implications of these findings are critical for improving survey practices, especially in managing the environment in which interviews are conducted.
+Since both partner and child interference are strongly linked with reduced comprehension, practical measures are warranted to mitigate these effects.
+Survey administrators could consider strategies such as conducting interviews in a controlled setting that minimizes the possibility of familial disruptions or providing respondents with explicit guidance on reducing interruptions during the interview.
+
+The significance of interview methods also warrants attention.
+Notably, the positive influence observed for "interview_conduct_method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
+Training interviewers in these methods, which may include explicit clarity and engagement-promoting techniques, could lead to more consistent and high-quality data, particularly in settings prone to interference.
+
+## Limitations and Areas for Improvement
+The analysis also revealed certain limitations, particularly concerning the generalizability of findings across different demographic segments.
+The moderate predictive power of the model (mean R² approximately 0.32) indicates that while the analysis captures key variability, significant elements affecting comprehension remain unexplained.
+Factors such as cultural variations or socio-economic differences, which were not fully accounted for, might explain the negligible or inconsistent country-level effects observed in the model.
+
+These limitations suggest that the current dataset may not adequately represent all influential aspects of response behavior, particularly when dealing with diverse populations.
+Addressing these gaps through more extensive data collection that captures additional respondent characteristics could further enhance the robustness of future findings.
+
+## Future Research Directions
+Building on these findings, future research should delve into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
+For instance, distinguishing between brief interruptions versus prolonged disturbances might reveal differences in how such disruptions affect respondent focus and, ultimately, response quality.
+
+Moreover, exploring potential interaction effects between variables—such as the interplay between partner interference and respondent reluctance—could provide a deeper understanding of the underlying dynamics affecting survey outcomes.
+This could lead to the development of more tailored survey management strategies, which would enhance the reliability of data collection across diverse respondent demographics.
+
+## Practical Insights for Survey Management
+
+The overarching lesson from this study is the significance of managing interview conditions to optimize respondent comprehension and, subsequently, data quality.
+Minimizing household disruptions, particularly familial interference, appears to be a critical factor in ensuring the accuracy and reliability of survey responses.
+Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
+Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview_conduct_method3," could foster greater respondent engagement and understanding.
+
+The findings also suggest that focusing on the relational and contextual aspects of the interview environment may yield better outcomes than emphasizing interviewer-specific traits such as gender or age.
+Therefore, training programs for interviewers should prioritize environmental control and interaction quality to maximize the clarity and effectiveness of survey questioning.
+
+Overall, by systematically addressing interference and enhancing interviewer practices, survey administrators can significantly elevate the quality of the data they collect.
+These insights contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
+
+\newpage
+
+\appendix
+
+# Appendix {#sec-appx}
+## Data Cleaning Notes
+We began by importing the raw dataset using the read.csv() function from base R, with a focus on keeping the process flexible for further manual manipulation.
+Initially, we removed columns that contained more than 80% missing values to retain only the most relevant information for analysis.
+
+To handle missing data, numeric variables were filled with their median values, while categorical variables were imputed with their mode.
+This approach aimed to maintain data integrity while minimizing assumptions about the distribution of missing values.
+
+Subsequently, additional data cleaning measures were taken.
+We removed duplicate entries to ensure uniqueness and eliminated outliers in numeric columns using the Z-score method, retaining only those rows with Z-scores within ±3.
+This step was important for reducing the influence of extreme data points on subsequent analyses.
+
+To enhance clarity and usability, several column names were renamed to be more descriptive.
+For example, resundq was renamed to respondent_understood.
+Additionally, the respondent_understood variable was recoded into a binary form (Understood vs.
+Not_understood) to simplify future analyses.
+
+To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category.
+The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.
+
+After cleaning, the dataset was split into training and testing sets in a way that ensured the country variable was well-represented in both.
+This stratified split preserved regional diversity, which was essential for maintaining representativeness in model training and evaluation.
+
+Lastly, the cleaned dataset was saved in both Parquet and CSV formats for use in future stages of the analysis.
+This ensured compatibility across different software tools and provided efficient access for future work.
+
+## European Social Survey  Methodology
+The European Social Survey (ESS) is a cross-national survey conducted biennially across European countries, aimed at measuring the attitudes, beliefs, and behaviors of European citizens.
+To ensure data accuracy and quality, the ESS employs rigorous survey methodologies and standardized procedures, ensuring comparability across participating countries and providing a reliable data source for social science research and policymaking (European Social Survey, 2024).
+
+The ESS targets individuals aged 15 and older living in private households across participating European countries, using a carefully designed sampling framework to ensure national representativeness.
+Countries employ multi-stage probability sampling to select respondents, ensuring that each individual has an equal chance of being selected, thereby minimizing selection bias and enhancing the generalizability of survey results.
+
+To collect the data, the ESS uses trained interviewers to conduct face-to-face interviews.
+These interviews are conducted in the respondents' native language, ensuring that participants can fully understand the questions being asked.
+The questionnaires are translated following rigorous standardized guidelines to ensure equivalence across languages and cultures (European Social Survey, 2024).
+Additionally, questionnaires are pre-tested before the official survey is launched to identify and resolve potential misunderstandings, ensuring consistent understanding among respondents.
+
+During data collection, the ESS implements strict quality control procedures, including systematic interviewer training, ensuring they conduct interviews following standardized techniques to reduce bias and maintain data consistency.
+To ensure sample representativeness, stratified sampling is used in some countries based on demographic characteristics like age, gender, and region, ensuring sufficient representation of different population groups.
+
+Like many survey research initiatives, the ESS faces challenges related to declining response rates.
+To mitigate non-response, the ESS requires interviewers to make multiple contact attempts, particularly in cases where initial attempts are unsuccessful, including follow-up visits.
+To further reduce non-response bias, post-stratification weights are applied to the collected data to adjust for differences between the sample and the overall population.
+
+The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue.
+Most interviews are conducted within a reasonable timeframe to ensure high response quality.
+The ESS places significant emphasis on accurately capturing every viewpoint, ensuring that the voices of marginalized groups are also adequately represented, which helps policymakers and researchers better understand the dynamics of social attitudes in Europe.
+
+By maintaining strict methodologies regarding sampling frameworks, translation procedures, interviewer training, and addressing non-response bias, the European Social Survey has become a trusted source of social data, providing essential support for research into cross-national comparisons and understanding social attitudes.
+
+##  Ideal Methodology
+
+For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the European Social Survey (ESS).
+The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.
+
+**Sampling Method**: We’ll use stratified random sampling, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
+This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.
+
+**Sample Size**: To make sure our analysis is meaningful, we plan to include at least 1,500 participants per country.
+For larger and more diverse countries, we may increase this number to properly represent smaller groups.
+
+**Data Collection Approach**: We’ll use a mixed-method approach for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
+Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality.
+We’ll also use self-administered questionnaires for follow-ups to improve the response rate among harder-to-reach groups, like younger people or those who move around frequently.
+
+**Survey Process and Quality Checks**: Interviewers will use standardized scripts to make sure everyone hears the questions the same way.
+Surveys will be recorded digitally to make data handling easier and to minimize errors.
+To avoid any bias, interviewers are trained to read questions in a neutral manner.
+
+**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will oversample some groups, like the elderly or those with lower education levels.
+This gives us more precise data about these groups, but we will use weight adjustments afterward to ensure the final dataset reflects the actual population structure.
+
+**Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
+
+- **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
+
+- **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
+
+- **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.
+
+**Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate.
+We’ll use statistical adjustments to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
+
+### Budget Breakdown for Survey Implementation
+
+To ensure we collect and analyze quality data, we will allocate the budget as follows:
+
+1. **Survey Design**: $8,000
+   - This budget includes designing the questionnaire, translating it into multiple languages, and making sure the questions are clear and unbiased. It also covers interviewer training costs.
+
+2. **Sampling and Recruitment**: $15,000
+   - This will go towards sampling costs, including **stratified sampling** to make sure all groups are represented proportionally.
+It also includes acquiring relevant demographic data for the 23 countries participating in ESS.
+
+3. **Recruiting Respondents**: $30,000
+   - This covers contacting participants, managing interviews, and compensating them for follow-ups across the countries.
+
+4. **Incentives**: $20,000
+   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
+
+5. **Data Quality Assurance and Analysis**: $12,000
+   - This includes data cleaning, quality checks, and analysis costs.
+We’ll hire statistical consultants to ensure proper data handling, make sure there are no inconsistencies, and apply adjustments to correct biases.
+
+By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
+
+## Idealized Survey
+
+An example of the survey can be found at this link: <https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill>
+
+**2024 Comprehension and Interview Experience Survey**  
+**Conducted by**: DEZHEN CHEN  
+**Contact**: dezhen.chen\@mail.utoronto.ca
+
+Welcome, and thank you for taking part in the **2024 Comprehension and Interview Experience Survey**.
+Your participation will help us understand how respondents perceive and engage with survey questions, and will improve the quality of interview interactions.
+
+As a thank you for your time, all survey respondents will be automatically entered into a sweepstakes, with a **chance to win $200**. Ten winners will be selected randomly.
+
+**Your responses will remain strictly confidential** and anonymous, and any data collected will be securely stored and used solely for academic and research purposes.
+No identifying information will be connected to your survey responses.
+
+---
+
+## Section 1: Demographics
+
+**Country of Residence**:  
+Please specify your country of residence:  
+- [Your answer]
+
+---
+
+## Section 2: Interviewer Details
+
+**Interviewer Age**:  
+What is the age of the interviewer?  
+- [Please specify in years]
+
+**Interviewer Gender**:  
+What is the gender of the interviewer?  
+1. Male  
+2. Female
+
+---
+
+## Section 3: Interview Process Information
+
+**Interview Conduct Method**:  
+What was the method used to conduct this interview?  
+1. Face-to-face  
+2. Telephone  
+3. Online video interview  
+4. Other
+
+**Questionnaire Language**:  
+What language was used during the interview?  
+- [Please specify the language]
+
+**Question Clarification**:  
+Did you need clarification on the questions during the interview?  
+1. No clarification needed  
+2. Minor clarification needed  
+3. Moderate clarification needed  
+4. Extensive clarification needed  
+5. Completely unclear, repeated explanations needed  
+6. Other
+
+**Respondent Understanding Level**:  
+How well do you think the respondent understood the questions?  
+1. Fully understood  
+2. Mostly understood  
+3. Needed some clarification  
+4. Partially understood  
+5. Did not understand at all
+
+**Respondent Tried Their Best**:  
+Do you think the respondent tried their best to answer the questions?  
+1. Very unwilling to answer  
+2. Somewhat reluctant  
+3. Neutral  
+4. Willing to answer  
+5. Very willing to answer  
+6. Other
+
+---
+
+## Section 4: Interference During Interview
+
+**Interference Presence**:  
+Was there any interference during the interview process?  
+1. Yes  
+2. No
+
+**Partner Interference**:  
+Was there any interference by a partner during the interview?  
+1. Yes  
+2. No
+
+**Child Interference**:  
+Was there any interference by children during the interview?  
+1. Yes  
+2. No
+
+**Parent Interference**:  
+Was there any interference by parents during the interview?  
+1. Yes  
+2. No
+
+**Relative Interference**:  
+Was there any interference by other relatives during the interview?  
+1. Yes  
+2. No
+
+**Non-relative Interference**:  
+Was there any interference by non-relatives during the interview?  
+1. Yes  
+2. No
+
+**Unknown Interference**:  
+Was there any unknown source of interference during the interview?  
+1. Yes  
+2. No
+
+**Interference Not Applicable**:  
+Was interference not applicable during this interview?  
+1. Yes  
+2. No
+
+---
+
+## Section 5: Additional Feedback
+
+**Additional Comments**:  
+Do you have any suggestions or feedback regarding the interview process?  
+- [Please provide your comments]
+
+**Interference Details**:  
+If there was interference, could you please describe it in more detail?  
+- [Please provide your comments]
+
+**Suggestions for Improvement**:  
+Do you have any suggestions to improve the clarity or format of the questions in this survey?  
+- [Please provide your suggestions]
+
+---
+
+## Important Notes
+
+- All responses are confidential and will be used for research purposes only.
+- This survey will take approximately 10 minutes to complete.
+- Your participation is entirely voluntary, and you may withdraw at any time.
+- All questions marked with an asterisk (*) are required.
+- There are no right or wrong answers; we appreciate your honest opinions.
+
+---
+
+**Thank You Message**:  
+Thank you once again for your participation.
+Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension.
+We appreciate your time and effort in completing this survey.
+
+# Model details {#sec-model-details}
+## Model summary
+```{r}
+#| label: tbl-summary
+#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
+#| echo: false
+#| warning: false
+modelsummary(
+  list("Bayesian Logistic Regression" = first_model),
+  metrics = c("R2", "RMSE")
+)
+
+```
+@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews.
+The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels.
+Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension.
+In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.
+
+Additionally, non-relative interference, which shows a positive coefficient of 0.941, suggests that having individuals outside the immediate family present may be less disruptive, or even beneficial, for the comprehension of survey questions.
+Interviewer-related variables, such as "interviewer_gender," appear to have minimal effects on comprehension, as evidenced by small coefficients like 0.100, suggesting that interviewer attributes play a relatively minor role compared to environmental and relational factors during social surveys
+## VIF
+```{r}
+#| label: tbl-vif
+#| tbl-cap: "Variance Inflation Factors (VIF) for Each Predictor in the Model."
+#| echo: false
+#| warning: false
+
+vif_values <- vif(first_model)
+
+gvif_df <- data.frame(
+  Variable = rownames(vif_values), 
+  GVIF = round(vif_values[, "GVIF"], 3),
+  Df = vif_values[, "Df"],
+  `GVIF^(1/(2*Df))` = round(vif_values[, "GVIF^(1/(2*Df))"], 3)
+)
+
+kable(gvif_df)
+
+```
+@tbl-vif presents the Generalized Variance Inflation Factors (GVIF) for each predictor in the Bayesian logistic regression model.
+GVIF helps assess multicollinearity among predictors, indicating how much the variance of a regression coefficient is inflated due to correlations between variables.
+
+Most predictors, such as respondent_tried_best (GVIF = 3.186, Df = 5) and respondent_reluctant (GVIF = 2.725, Df = 5), show moderate GVIF values, suggesting manageable multicollinearity.
+The adjusted GVIF values, which are generally close to 1, indicate that the inflation effect is controlled across variables.
+
+In summary, the GVIF analysis indicates that multicollinearity is present but not severe enough to threaten model reliability.
+Further analysis may focus on predictors with slightly higher GVIF to ensure stability.
+
+## Posterior predictive check
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheck
+#| fig-cap: "Posterior Predictive Check: The comparison between observed response values (dark line) and model-generated replications (light lines) demonstrates the model's ability to replicate the observed response patterns, indicating a good fit and capturing the main features of the response distribution."
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")+ xlim(-0.1, 1.2)
+
+```
+In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by $y$ and the replicated data generated from the model (denoted by $( y_{\text{rep}})$.
+The replicated lines closely follow the shape and central trend of the observed data, particularly around the main peak at 0.9, which suggests that the model captures the overall distribution effectively.
+This alignment indicates that the model successfully represents the underlying data-generating process, especially in regions with high data density.
+While the model's performance appears strong, any visible discrepancies—particularly in areas of lower density—may highlight aspects of the data structure that are not fully captured.
+Addressing such discrepancies could involve refining the model by introducing additional parameters or reconsidering underlying assumptions.
+Overall, this comparison provides evidence that the model fits well, though there remain potential areas for enhancement to better encompass the full range of data complexities.
+
 ## Diagnostics

### 2024-12-02 scripts/00-simulate_data.R
update simmulate data

@@ -11,73 +11,93 @@
 library(tidyverse)
 library(janitor)
 
-#### Simulate data ####
+#### Simulate full data with interactions ####
 # Set seed for reproducibility
 set.seed(42)
 
 # Define the number of observations
 num_obs <- 1000
 
-# Create a tibble with simulated data for interviews
+# Create a tibble with simulated data
 simulated_interview_data <- tibble(
-  # Simulate interview condition (how it was conducted)
-  vdcond = sample(c("face-to-face", "telephone", "online"), 
-                  num_obs, replace = TRUE),
+  # Simulate respondent's gender (1: male, 2: female)
+  intgndr = sample(c(1, 2), num_obs, replace = TRUE),
   
-  # Simulate respondent's willingness to answer (1: willing, 2: reluctant)
-  resrelq = sample(1:2, num_obs, replace = TRUE),
+  # Simulate respondent's age based on gender
+  intagea = ifelse(
+    intgndr == 1,
+    round(rnorm(num_obs, mean = 50, sd = 10)), # Males: mean 50, sd 10
+    round(rnorm(num_obs, mean = 45, sd = 12))  # Females: mean 45, sd 12
+  ),
   
-  # Simulate whether there were any interferences during the interview
-  preinf = sample(c("none", "spouse", "child", "parent", "other"), 
-                  num_obs, replace = TRUE),
+  # Simulate interview condition (depends on age group)
+  vdcond = ifelse(
+    intagea < 40,
+    sample(c("online", "telephone"), num_obs, replace = TRUE, prob = c(0.7, 0.3)),
+    sample(c("face-to-face", "telephone"), num_obs, replace = TRUE, prob = c(0.6, 0.4))
+  ),
   
-  # Simulate respondent's age
-  intagea = sample(18:80, num_obs, replace = TRUE),
+  # Simulate respondent's willingness to answer (depends on age and gender)
+  resclq = ifelse(
+    intgndr == 1 & intagea > 50,
+    sample(1:3, num_obs, replace = TRUE, prob = c(0.2, 0.5, 0.3)), # Male and older
+    sample(1:3, num_obs, replace = TRUE, prob = c(0.5, 0.3, 0.2))  # Others
+  ),
   
-  # Simulate respondent's gender
-  intgndr = sample(c("male", "female"), num_obs, replace = TRUE),
+  # Simulate production date
[…]

### 2024-12-02 scripts/00-simulate_data.R
update simulate data

@@ -89,19 +89,11 @@ simulated_interview_data <- tibble(
   intnum = sample(1000:9999, num_obs, replace = TRUE)
 )
 
-#### Save data ####
-# Define the output folder
-output_folder <- "starter_folder-main 2/data/00-simulated_data"
 
-# Create the folder if it doesn't exist
-if (!dir.exists(output_folder)) {
-  dir.create(output_folder, recursive = TRUE)
-}
 
 
 # Save the data to the correct location
-write_csv(simulated_interview_data, file.path(output_folder, "simulated_interview_data.csv"))
-
+write_csv(simulated_interview_data, "data/00-simulated_data/simulated_data.csv")
 
 
 

### 2024-12-02 scripts/06-model_data.R
update model

@@ -15,6 +15,8 @@ library(rstanarm)
 library(arrow)
 library(car)
 library(brms)
+library(rpart)  
+
 
 #### Read data ####
 analysis_data_train <- read_parquet("data/02-analysis_data/train_data.parquet")
@@ -40,25 +42,25 @@ saveRDS(
   file = "models/model.rds"
 )
 
-model1 <- glm(
+tree_model <- rpart(
   formula = respondent_understood_binary ~ interview_conduct_method + 
     partner_interference + child_interference + parent_interference + 
     relative_interference + non_relative_interference + interviewer_age + 
     interviewer_gender + as.factor(country) + question_clarification + 
     respondent_reluctant + respondent_tried_best,
   data = analysis_data_train,
-  family = binomial()
+  method = "class"  # 分类任务
 )
 
-summary(model1)
 
+summary(tree_model)
 
 
 
 #### Save model ####
 saveRDS(
-  model1,
-  file = "models/glmmodel.rds"
+  tree_model,
+  file = "models/treemodel.rds"
 )
 
 

### 2024-12-02 paper/paper.qmd
update paper

--- 2024-11-29 paper/paper.qmd
@@
 library(caret)
+library(rpart)  
 ```
@@
 
+- **rpart** [@rpart]: A comprehensive package for building recursive partitioning models, commonly used for creating decision trees.
+Particularly valuable for classification and regression tasks, it supports model visualization and interpretation, offering control over tree complexity and pruning for enhanced model performance.
+
 - **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies in presenting data and statistical information.
@@
 By including such factors, our model was able to reflect a realistic and comprehensive picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
+
+## Alternative model
+After evaluating both the decision tree model [@tbl-comprehension-matrix13] and the Bayesian GLM [@tbl-comprehension-matrix12] for classifying comprehension outcomes, a clear distinction in performance emerged.
+While the decision tree model demonstrated superior sensitivity and balanced accuracy in identifying the minority class, "Not_understood," the Bayesian GLM consistently achieved higher overall accuracy, with a score of 96.05% compared to the decision tree's 95.98%.
+
+Although the difference in accuracy is modest, the Bayesian GLM aligns more closely with the overarching objective of optimizing predictive performance across all classes.
+Furthermore, the Bayesian GLM's probabilistic framework provides a nuanced interpretation of predictions, capturing uncertainty and enabling more robust decision-making.
+Therefore, despite the decision tree's relative strength in minority class detection, the Bayesian GLM was selected as the final model due to its superior overall accuracy and its ability to provide a more balanced representation of both majority and minority classes.
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: tbl-comprehension-matrix13
+#| tbl-cap: "Confusion Matrix for Comprehension Classification Using Decision Tree"
+
+analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
+analysis_data_test <- read_parquet(here::here("data/02-analysis_data/test_data.parquet"))
+ tree_model<-
+  readRDS(file = here::here("models/treemodel.rds"))
+
+analysis_data_test$respondent_understood_binary <- as.factor(analysis_data_test$respondent_understood_binary)
+
+predicted_class <- predict(tree_model, newdata = analysis_data_test, type = "class")
+
+analysis_data_test$predicted_class <- predicted_class
+
+confusion_matrix1 <- confusionMatrix(
+  analysis_data_test$predicted_class,
+  analysis_data_test$respondent_understood_binary
+)
+
+confusion_matrix1
+
+confusion_matrix_tree <- confusionMatrix(
+  analysis_data_test$predicted_class,
+  analysis_data_test$respondent_understood_binary
+)
+
+confusion_df <- as.data.frame(as.table(confusion_matrix_tree$table))
+kable(confusion_df, format = "markdown", col.names = c("Prediction", "Reference", "Freq"))
+
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| message: false
+#| warning: false
+#| label: tbl-comprehension-matrix12
+#| tbl-cap: "Confusion Matrix for Comprehension Classification1"
+
+# Confusion matrix definition
+confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
+                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
+                                           "Reference" = c("Not_understood", "Understood")))
+
+# Convert confusion matrix to data frame
+confusion_df <- as.data.frame(as.table(confusion_matrix))
+
+# Create and directly print the Markdown table using kable
+kable(confusion_df, format = "markdown")
+```
 
@@
 #| label: tbl-comprehension-matrix1
-#| tbl-cap: "Confusion Matrix for Comprehension Classification"
+#| tbl-cap: "Confusion Matrix for Comprehension Classification1"
 
@@
 #| tbl-cap: "Confusion Matrix for Comprehension Classification"
-
 analysis_data_train <- read_parquet(here::here("data/02-analysis_data/train_data.parquet"))
@@
 ```
-@tbl-comprehension-matrix1 presents the confusion matrix for the comprehension classification model.
-The matrix provides the counts of correct and incorrect classifications between the "Not_understood" and "Understood" categories, highlighting how well the model performed in predicting respondent comprehension.
-The diagonal elements represent the correctly classified observations, while the off-diagonal elements indicate misclassifications.
-The matrix helps visualize the strengths and weaknesses of the model, particularly in distinguishing between respondents who understood versus those who did not.
-
-@tbl-comprehension-matrix2 shows the evaluation metrics for the classification model.
-These metrics include Accuracy, Precision (Positive Predictive Value), Recall (True Positive Rate), True Negative Rate (Specificity), and F1 Score, among others.
-The metrics provide a comprehensive summary of the model's performance, measuring not only how many predictions were correct, but also evaluating the balance between sensitivity and specificity.
-The high specificity and overall accuracy indicate that the model is effective in identifying respondents who understood the questions, but the low recall suggests limitations in detecting those who did not understand.
+@tbl-comprehension-matrix1 provides a summary of the model's prediction outcomes for the comprehension classification task.
+The table displays the frequencies of correct and incorrect predictions across the "Not_understood" and "Understood" categories.
+Correct classifications occur when the predicted and actual labels align (e.g., "Not_understood" predicted as "Not_understood"), while mismatches are shown as incorrect classifications (e.g., "Not_understood" predicted as "Understood").
+This representation effectively highlights the model's ability to distinguish between the two classes, particularly its challenges in identifying the minority "Not_understood" category due to its smaller sample size.
+
+@tbl-comprehension-matrix2 presents key performance metrics for evaluating the classification model.
+Metrics such as Accuracy, Precision (Positive Predictive Value), Recall (True Positive Rate), Specificity (True Negative Rate), F1 Score, and Balanced Accuracy provide a detailed view of the model's strengths and limitations.
+The high Accuracy and Specificity values demonstrate the model's reliability in correctly classifying the majority "Understood" category.
+In contrast, the lower Recall for the "Not_understood" class indicates difficulties in detecting this minority group.
+These metrics offer a well-rounded understanding of the model's performance, balancing its effectiveness in majority class classification with areas for improvement in minority class sensitivity.
+
+# Discussion {#sec-discussion}
+
+This analysis employed a Bayesian logistic regression model to investigate factors influencing respondents' comprehension during interviews.
+By incorporating various types of interference, interview methods, and respondent characteristics, the model elucidates how these variables impact understanding during social survey interviews.
+
+## Factors Affecting Response Comprehension
+
+The results from the Bayesian analysis emphasize that various types of disruptions and interview settings significantly influence respondents' ability to comprehend survey questions.
+Specifically, partner and child interference were found to exert a pronounced negative impact on understanding.
+For instance, the negative coefficient associated with partner interference (mean = -0.6) suggests that the presence of a partner may obstruct a respondent's capacity to fully grasp the questions posed.
+This aligns with established literature that highlights how social pressures or even well-intended but unsolicited support from family members can compromise respondent attention during surveys.
+
+Conversely, interference from non-relatives demonstrated a contrasting effect.
+Non-relative interference, indicated by a positive coefficient, implies that respondents may actually become more attentive under these circumstances, potentially due to heightened formality or a sense of accountability.
+This counterintuitive finding opens the door to further exploration of the nuanced dynamics between social context and survey response behavior.
+
+## Implications for Managing Interview Interference
+The implications of these findings are critical for improving survey practices, especially in managing the environment in which interviews are conducted.
+Since both partner and child interference are strongly linked with reduced comprehension, practical measures are warranted to mitigate these effects.
+Survey administrators could consider strategies such as conducting interviews in a controlled setting that minimizes the possibility of familial disruptions or providing respondents with explicit guidance on reducing interruptions during the interview.
+
+The significance of interview methods also warrants attention.
+Notably, the positive influence observed for "interview_conduct_method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
+Training interviewers in these methods, which may include explicit clarity and engagement-promoting techniques, could lead to more consistent and high-quality data, particularly in settings prone to interference.
+
+## Limitations and Areas for Improvement
+The analysis also revealed certain limitations, particularly concerning the generalizability of findings across different demographic segments.
+The moderate predictive power of the model (mean R² approximately 0.32) indicates that while the analysis captures key variability, significant elements affecting comprehension remain unexplained.
+Factors such as cultural variations or socio-economic differences, which were not fully accounted for, might explain the negligible or inconsistent country-level effects observed in the model.
+
+These limitations suggest that the current dataset may not adequately represent all influential aspects of response behavior, particularly when dealing with diverse populations.
+Addressing these gaps through more extensive data collection that captures additional respondent characteristics could further enhance the robustness of future findings.
+
+## Future Research Directions
+Building on these findings, future research should delve into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
+For instance, distinguishing between brief interruptions versus prolonged disturbances might reveal differences in how such disruptions affect respondent focus and, ultimately, response quality.
+
+Moreover, exploring potential interaction effects between variables—such as the interplay between partner interference and respondent reluctance—could provide a deeper understanding of the underlying dynamics affecting survey outcomes.
+This could lead to the development of more tailored survey management strategies, which would enhance the reliability of data collection across diverse respondent demographics.
+
+## Practical Insights for Survey Management
+
+The overarching lesson from this study is the significance of managing interview conditions to optimize respondent comprehension and, subsequently, data quality.
+Minimizing household disruptions, particularly familial interference, appears to be a critical factor in ensuring the accuracy and reliability of survey responses.
+Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
+Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview_conduct_method3," could foster greater respondent engagement and understanding.
+
+The findings also suggest that focusing on the relational and contextual aspects of the interview environment may yield better outcomes than emphasizing interviewer-specific traits such as gender or age.
+Therefore, training programs for interviewers should prioritize environmental control and interaction quality to maximize the clarity and effectiveness of survey questioning.
+
+Overall, by systematically addressing interference and enhancing interviewer practices, survey administrators can significantly elevate the quality of the data they collect.
+These insights contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
+
+\newpage
+
+\appendix
+
+# Appendix {#sec-appx}
+## Data Cleaning Notes
+We began by importing the raw dataset using the read.csv() function from base R, with a focus on keeping the process flexible for further manual manipulation.
+Initially, we removed columns that contained more than 80% missing values to retain only the most relevant information for analysis.
+
+To handle missing data, numeric variables were filled with their median values, while categorical variables were imputed with their mode.
+This approach aimed to maintain data integrity while minimizing assumptions about the distribution of missing values.
+
+Subsequently, additional data cleaning measures were taken.
+We removed duplicate entries to ensure uniqueness and eliminated outliers in numeric columns using the Z-score method, retaining only those rows with Z-scores within ±3.
+This step was important for reducing the influence of extreme data points on subsequent analyses.
+
+To enhance clarity and usability, several column names were renamed to be more descriptive.
+For example, resundq was renamed to respondent_understood.
+Additionally, the respondent_understood variable was recoded into a binary form (Understood vs.
+Not_understood) to simplify future analyses.
+
+To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category.
+The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.
+
+After cleaning, the dataset was split into training and testing sets in a way that ensured the country variable was well-represented in both.
+This stratified split preserved regional diversity, which was essential for maintaining representativeness in model training and evaluation.
+
+Lastly, the cleaned dataset was saved in both Parquet and CSV formats for use in future stages of the analysis.
+This ensured compatibility across different software tools and provided efficient access for future work.
+
+## European Social Survey  Methodology
+The European Social Survey (ESS) is a cross-national survey conducted biennially across European countries, aimed at measuring the attitudes, beliefs, and behaviors of European citizens.
+To ensure data accuracy and quality, the ESS employs rigorous survey methodologies and standardized procedures, ensuring comparability across participating countries and providing a reliable data source for social science research and policymaking (European Social Survey, 2024).
+
+The ESS targets individuals aged 15 and older living in private households across participating European countries, using a carefully designed sampling framework to ensure national representativeness.
+Countries employ multi-stage probability sampling to select respondents, ensuring that each individual has an equal chance of being selected, thereby minimizing selection bias and enhancing the generalizability of survey results.
+
+To collect the data, the ESS uses trained interviewers to conduct face-to-face interviews.
+These interviews are conducted in the respondents' native language, ensuring that participants can fully understand the questions being asked.
+The questionnaires are translated following rigorous standardized guidelines to ensure equivalence across languages and cultures (European Social Survey, 2024).
+Additionally, questionnaires are pre-tested before the official survey is launched to identify and resolve potential misunderstandings, ensuring consistent understanding among respondents.
+
+During data collection, the ESS implements strict quality control procedures, including systematic interviewer training, ensuring they conduct interviews following standardized techniques to reduce bias and maintain data consistency.
+To ensure sample representativeness, stratified sampling is used in some countries based on demographic characteristics like age, gender, and region, ensuring sufficient representation of different population groups.
+
+Like many survey research initiatives, the ESS faces challenges related to declining response rates.
+To mitigate non-response, the ESS requires interviewers to make multiple contact attempts, particularly in cases where initial attempts are unsuccessful, including follow-up visits.
+To further reduce non-response bias, post-stratification weights are applied to the collected data to adjust for differences between the sample and the overall population.
+
+The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue.
+Most interviews are conducted within a reasonable timeframe to ensure high response quality.
+The ESS places significant emphasis on accurately capturing every viewpoint, ensuring that the voices of marginalized groups are also adequately represented, which helps policymakers and researchers better understand the dynamics of social attitudes in Europe.
+
+By maintaining strict methodologies regarding sampling frameworks, translation procedures, interviewer training, and addressing non-response bias, the European Social Survey has become a trusted source of social data, providing essential support for research into cross-national comparisons and understanding social attitudes.
+
+##  Ideal Methodology
+
+For studying factors that affect respondent understanding during social surveys, an ideal methodology would involve using data from the European Social Survey (ESS).
+The goal is to make sure we represent people from different countries across Europe fairly, considering things like age, gender, education, and location, so that our findings are accurate and reflect various social contexts.
+
+**Sampling Method**: We’ll use stratified random sampling, which means we’ll group people by country first, and then by characteristics like age, gender, and education within each country.
+This helps make sure that each group is represented well in the sample, reducing bias and making our findings more generalizable to the whole population.
+
+**Sample Size**: To make sure our analysis is meaningful, we plan to include at least 1,500 participants per country.
+For larger and more diverse countries, we may increase this number to properly represent smaller groups.
+
+**Data Collection Approach**: We’ll use a mixed-method approach for data collection, including face-to-face interviews and self-completed questionnaires to reach different types of people.
+Interviews will be conducted by trained local interviewers to prevent language barriers or cultural differences from affecting the data quality.
+We’ll also use self-administered questionnaires for follow-ups to improve the response rate among harder-to-reach groups, like younger people or those who move around frequently.
+
+**Survey Process and Quality Checks**: Interviewers will use standardized scripts to make sure everyone hears the questions the same way.
+Surveys will be recorded digitally to make data handling easier and to minimize errors.
+To avoid any bias, interviewers are trained to read questions in a neutral manner.
+
+**Oversampling Certain Groups**: To better understand specific impacts on comprehension, we will oversample some groups, like the elderly or those with lower education levels.
+This gives us more precise data about these groups, but we will use weight adjustments afterward to ensure the final dataset reflects the actual population structure.
+
+**Strategies to Improve Response Rates**: We’ll use several strategies to get as many people as possible to participate:
+
+- **Multi-language Support**: Questionnaires will be available in different languages so that non-native speakers can participate.
+
+- **Follow-up Contact**: We’ll follow up with those who initially refuse or don’t respond, trying at least twice to increase participation.
+
+- **Incentives**: We’ll offer small rewards like gift cards or raffle entries to encourage people to take part.
+
+**Data Analysis and Verification**: Before analyzing, we’ll clean up the dataset, deal with missing values, and make sure demographic information is accurate.
+We’ll use statistical adjustments to correct for any missing data, and weighting will be used to ensure that our data accurately represents the population.
+
+### Budget Breakdown for Survey Implementation
+
+To ensure we collect and analyze quality data, we will allocate the budget as follows:
+
+1. **Survey Design**: $8,000
+   - This budget includes designing the questionnaire, translating it into multiple languages, and making sure the questions are clear and unbiased. It also covers interviewer training costs.
+
+2. **Sampling and Recruitment**: $15,000
+   - This will go towards sampling costs, including **stratified sampling** to make sure all groups are represented proportionally.
+It also includes acquiring relevant demographic data for the 23 countries participating in ESS.
+
+3. **Recruiting Respondents**: $30,000
+   - This covers contacting participants, managing interviews, and compensating them for follow-ups across the countries.
+
+4. **Incentives**: $20,000
+   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
+
+5. **Data Quality Assurance and Analysis**: $12,000
+   - This includes data cleaning, quality checks, and analysis costs.
+We’ll hire statistical consultants to ensure proper data handling, make sure there are no inconsistencies, and apply adjustments to correct biases.
+
+By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
+
+## Idealized Survey
+
+An example of the survey can be found at this link: <https://docs.google.com/forms/d/1BWPU4vFYpzYnkg1nzvXu9b_P12UOXFKcOh4muV7wVQ0/prefill>
+
+**2024 Comprehension and Interview Experience Survey**  
+**Conducted by**: DEZHEN CHEN  
+**Contact**: dezhen.chen\@mail.utoronto.ca
+
+Welcome, and thank you for taking part in the **2024 Comprehension and Interview Experience Survey**.
+Your participation will help us understand how respondents perceive and engage with survey questions, and will improve the quality of interview interactions.
+
+As a thank you for your time, all survey respondents will be automatically entered into a sweepstakes, with a **chance to win $200**. Ten winners will be selected randomly.
+
+**Your responses will remain strictly confidential** and anonymous, and any data collected will be securely stored and used solely for academic and research purposes.
+No identifying information will be connected to your survey responses.
+
+---
+
+## Section 1: Demographics
+
+**Country of Residence**:  
+Please specify your country of residence:  
+- [Your answer]
+
+---
+
+## Section 2: Interviewer Details
+
+**Interviewer Age**:  
+What is the age of the interviewer?  
+- [Please specify in years]
+
+**Interviewer Gender**:  
+What is the gender of the interviewer?  
+1. Male  
+2. Female
+
+---
+
+## Section 3: Interview Process Information
+
+**Interview Conduct Method**:  
+What was the method used to conduct this interview?  
+1. Face-to-face  
+2. Telephone  
+3. Online video interview  
+4. Other
+
+**Questionnaire Language**:  
+What language was used during the interview?  
+- [Please specify the language]
+
+**Question Clarification**:  
+Did you need clarification on the questions during the interview?  
+1. No clarification needed  
+2. Minor clarification needed  
+3. Moderate clarification needed  
+4. Extensive clarification needed  
+5. Completely unclear, repeated explanations needed  
+6. Other
+
+**Respondent Understanding Level**:  
+How well do you think the respondent understood the questions?  
+1. Fully understood  
+2. Mostly understood  
+3. Needed some clarification  
+4. Partially understood  
+5. Did not understand at all
+
+**Respondent Tried Their Best**:  
+Do you think the respondent tried their best to answer the questions?  
+1. Very unwilling to answer  
+2. Somewhat reluctant  
+3. Neutral  
+4. Willing to answer  
+5. Very willing to answer  
+6. Other
+
+---
+
+## Section 4: Interference During Interview
+
+**Interference Presence**:  
+Was there any interference during the interview process?  
+1. Yes  
+2. No
+
+**Partner Interference**:  
+Was there any interference by a partner during the interview?  
+1. Yes  
+2. No
+
+**Child Interference**:  
+Was there any interference by children during the interview?  
+1. Yes  
+2. No
+
+**Parent Interference**:  
+Was there any interference by parents during the interview?  
+1. Yes  
+2. No
+
+**Relative Interference**:  
+Was there any interference by other relatives during the interview?  
+1. Yes  
+2. No
+
+**Non-relative Interference**:  
+Was there any interference by non-relatives during the interview?  
+1. Yes  
+2. No
+
+**Unknown Interference**:  
+Was there any unknown source of interference during the interview?  
+1. Yes  
+2. No
+
+**Interference Not Applicable**:  
+Was interference not applicable during this interview?  
+1. Yes  
+2. No
+
+---
+
+## Section 5: Additional Feedback
+
+**Additional Comments**:  
+Do you have any suggestions or feedback regarding the interview process?  
+- [Please provide your comments]
+
+**Interference Details**:  
+If there was interference, could you please describe it in more detail?  
+- [Please provide your comments]
+
+**Suggestions for Improvement**:  
+Do you have any suggestions to improve the clarity or format of the questions in this survey?  
+- [Please provide your suggestions]
+
+---
+
+## Important Notes
+
+- All responses are confidential and will be used for research purposes only.
+- This survey will take approximately 10 minutes to complete.
+- Your participation is entirely voluntary, and you may withdraw at any time.
+- All questions marked with an asterisk (*) are required.
+- There are no right or wrong answers; we appreciate your honest opinions.
+
+---
+
+**Thank You Message**:  
+Thank you once again for your participation.
+Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension.
+We appreciate your time and effort in completing this survey.
+
+# Model details {#sec-model-details}
+## Model summary
+```{r}
+#| label: tbl-summary
+#| tbl-cap: "Coefficients from a Bayesian logistic regression model examining factors affecting respondents' understanding during interviews, including interview methods, interference types, and country-level indicators."
+#| echo: false
+#| warning: false
+modelsummary(
+  list("Bayesian Logistic Regression" = first_model),
+  metrics = c("R2", "RMSE")
+)
+
+```
+@tbl-summary presents the coefficients from our model analyzing factors that influence response comprehension during interviews.
+The intercept value, 1.823, represents the baseline level of response comprehension when all other predictors are at their reference or baseline levels.
+Key variables include "interview_conduct_method9," which has a highly positive coefficient of 81.309, indicating that this particular interview method greatly enhances respondent comprehension.
+In contrast, factors such as "parent_interference" and "child_interference" exhibit negative coefficients (-1.586 and -0.623 respectively), suggesting that these types of interference are associated with lower levels of understanding during interviews.
+
+Additionally, non-relative interference, which shows a positive coefficient of 0.941, suggests that having individuals outside the immediate family present may be less disruptive, or even beneficial, for the comprehension of survey questions.
+Interviewer-related variables, such as "interviewer_gender," appear to have minimal effects on comprehension, as evidenced by small coefficients like 0.100, suggesting that interviewer attributes play a relatively minor role compared to environmental and relational factors during social surveys
+## VIF
+```{r}
+#| label: tbl-vif
+#| tbl-cap: "Variance Inflation Factors (VIF) for Each Predictor in the Model."
+#| echo: false
+#| warning: false
+
+vif_values <- vif(first_model)
+
+gvif_df <- data.frame(
+  Variable = rownames(vif_values), 
+  GVIF = round(vif_values[, "GVIF"], 3),
+  Df = vif_values[, "Df"],
+  `GVIF^(1/(2*Df))` = round(vif_values[, "GVIF^(1/(2*Df))"], 3)
+)
+
+kable(gvif_df)
+
+```
+@tbl-vif presents the Generalized Variance Inflation Factors (GVIF) for each predictor in the Bayesian logistic regression model.
+GVIF helps assess multicollinearity among predictors, indicating how much the variance of a regression coefficient is inflated due to correlations between variables.
+
+Most predictors, such as respondent_tried_best (GVIF = 3.186, Df = 5) and respondent_reluctant (GVIF = 2.725, Df = 5), show moderate GVIF values, suggesting manageable multicollinearity.
+The adjusted GVIF values, which are generally close to 1, indicate that the inflation effect is controlled across variables.
+
+In summary, the GVIF analysis indicates that multicollinearity is present but not severe enough to threaten model reliability.
+Further analysis may focus on predictors with slightly higher GVIF to ensure stability.
+
+## Posterior predictive check
+```{r}
+#| eval: true
+#| echo: false
+#| message: false
+#| warning: false
+#| label: fig-ppcheck
+#| fig-cap: "Posterior Predictive Check: The comparison between observed response values (dark line) and model-generated replications (light lines) demonstrates the model's ability to replicate the observed response patterns, indicating a good fit and capturing the main features of the response distribution."
+
+pp_check(first_model) +
+  theme_classic() +
+  theme(legend.position = "bottom")+ xlim(-0.1, 1.2)
+
+```
+In @fig-ppcheck, we implement a posterior predictive check, which displays the overlap between the observed data (denoted by $y$ and the replicated data generated from the model (denoted by $( y_{\text{rep}})$.
+The replicated lines closely follow the shape and central trend of the observed data, particularly around the main peak at 0.9, which suggests that the model captures the overall distribution effectively.
+This alignment indicates that the model successfully represents the underlying data-generating process, especially in regions with high data density.
+While the model's performance appears strong, any visible discrepancies—particularly in areas of lower density—may highlight aspects of the data structure that are not fully captured.
+Addressing such discrepancies could involve refining the model by introducing additional parameters or reconsidering underlying assumptions.
+Overall, this comparison provides evidence that the model fits well, though there remain potential areas for enhancement to better encompass the full range of data complexities.
 

### 2024-12-02 paper/paper.qmd
update paper

@@
 In addition to age, we included variables such as "interview conduct method," various "interference types" (e.g., "partner_interference," "child_interference"), and "interviewer characteristics" to fully encapsulate the different factors known to impact response quality.
-These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@fowler1990standardized], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
+These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@aquilino1993effects], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
 By including such factors, our model was able to reflect a realistic and comprehensive picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
@@
 )
-
-confusion_matrix1
 

### 2024-12-02 paper/paper.qmd
update paper

@@
 We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality.
-The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1), which offers a rich collection of data on societal attitudes and behaviors across numerous European countries.
+The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], which offers a rich collection of data on societal attitudes and behaviors across numerous European countries.
 The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality.

### 2024-12-02 paper/paper.qmd
update paper

@@
 number-sections: true
+toc: true
 bibliography: references.bib

### 2024-12-02 paper/paper.qmd
update paper

@@
 The use of Bayesian methods allowed us to incorporate prior knowledge and manage uncertainty in the analysis effectively, while also making inferences about the likely impacts of the disruptions on data quality.
-Throughout the data preparation phase, categorical variables were simplified, excluding variables like 'country' that introduced excess complexity, in order to enhance interpretability and ensure the model’s tractability.
-Additionally, predictor variables included the method of interview administration (e.g., telephone, in-person), interviewer characteristics (age and gender), and respondent attitudes (such as willingness to answer or the need for clarification), providing a comprehensive understanding of the factors influencing survey outcomes.
 

### 2024-12-03 scripts/05-exploratory_data_analysis.R
update eda

@@ -96,15 +96,5 @@ ggplot(analysis_data, aes(x = respondent_tried_best, fill = as.factor(interferen
 
 
 
-ggplot(analysis_data, aes(x = respondent_tried_best, fill = respondent_understood_binary)) +
-  geom_bar(position = "fill") +
-  scale_fill_manual(values = c("#619CFF", "#F8766D")) +
-  labs(
-    title = "Bar Plot of Response Understanding by Respondent Tried Best",
-    x = "Respondent Tried Best",
-    y = "Proportion",
-    fill = "Response Understanding"
-  ) +
-  theme_minimal()
 
 

### 2024-12-03 paper/paper.qmd
update paper

@@
 date-format: long
-abstract: "In social surveys, disruptions during interviews can profoundly impact the quality of respondent data, thereby affecting the overall reliability of survey results.
+abstract: "In social surveys, disruptions during interviews can significantly impact the quality of respondent data, thereby affecting the overall reliability of survey results.
 This study employs Bayesian hierarchical logistic regression to analyze the influence of a diverse range of factors—including the type of disruption, presence of family members, interview methodology, interviewer characteristics, and respondent attitudes—on response quality and accuracy.
 Our findings indicate that various forms of disruptions uniquely impact data quality, with some conditions proving more detrimental than others.
-These insights are pivotal for refining survey methodologies and optimizing interview conditions, ultimately improving the reliability and validity of collected data."
+These observations are pivotal for refining survey methodologies and optimizing interview conditions, ultimately improving the reliability and validity of collected data."
 format: pdf
@@
 In recent years, the quality and reliability of data collected through social surveys have garnered increasing attention, especially considering how various forms of disruption may influence respondents’ behavior and, subsequently, the quality of survey responses.
-Social surveys are crucial tools for obtaining insights into societal trends, guiding public policy, and informing evidence-based decision-making.
+Social surveys are indispensable tools for obtaining observations into societal trends, guiding public policy, and informing evidence-based decision-making.
 Thus, ensuring the robustness of data collected from these surveys has implications for the accuracy of the conclusions drawn and for the effective formulation of policy measures.
@@
 For example, Groves et al.
-[@groves2011survey] investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these nuanced dynamics.
+[@groves2011survey] investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
 Similarly, Couper and de Leeuw [@massey2013we] explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
@@
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
-Addressing this gap is imperative to improving the reliability of survey data, particularly in settings where such disruptions are unavoidable.
+Addressing this gap is paramount to improving the reliability of survey data, particularly in settings where such disruptions are unavoidable.
 
 This research seeks to fill this gap by systematically investigating the role of various disruptions during social survey interviews, focusing particularly on how different types of familial and environmental interferences affect respondent comprehension and engagement.
-To this end, we conducted a comprehensive analysis using Bayesian hierarchical logistic regression, implemented through the rstanarm package in R.
+To this end, we conducted a holistic analysis using Bayesian hierarchical logistic regression, implemented through the rstanarm package in R.
 This model structure was chosen for its ability to capture complex relationships, accounting for multiple levels of influence—namely, disruptions at the respondent level and interviewer characteristics nested within the survey context.
@@
 Gender of the interviewer also emerged as a significant factor, though its influence was more context-dependent, interacting with other variables such as the type of interference and the mode of the interview.
-These insights help to paint a detailed picture of the factors that can either hinder or enhance data quality in social survey settings, providing a richer understanding of the conditions that optimize respondent engagement and accuracy.
+These observations help to paint a detailed picture of the factors that can either hinder or enhance data quality in social survey settings, providing a richer understanding of the conditions that optimize respondent engagement and accuracy.
 
@@
 Section @sec-discussion then discusses the practical implications of these findings, with a particular focus on the improvements needed in interviewer training and strategies to reduce the impact of disruptions on data quality.
-Finally, Section @sec-model-details summarizes the contributions of this research, addresses its limitations, and suggests avenues for future work, particularly concerning the application of adaptive survey designs and advanced data collection technologies aimed at minimizing the effects of respondent disruption.
+Finally, Section @sec-model-details summarizes the contributions of this research, addresses its limitations, and suggests avenues for future work, particularly concerning the application of adaptive survey designs and enhanced data collection technologies aimed at minimizing the effects of respondent disruption.
 
@@
 By analyzing variables such as different types of interferences (partner, child, parent, and relative interferences), interview methodologies, the demographic characteristics of interviewers (such as age and gender), the language of the questionnaire, and respondent behaviors like reluctance, clarification requests, and effort put into answering, this research seeks to understand how these elements affect the consistency and clarity of responses.
-The core goal is to determine the impact of these factors on respondent understanding and data reliability, thereby providing insights into improving survey methods and reducing biases in data collection.
+The core goal is to determine the impact of these factors on respondent understanding and data reliability, thereby providing observations into improving survey methods and reducing biases in data collection.
 
@@
 The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents.
-The meticulous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth exploration of the impacts of contextual disruptions on response quality.
-
-The decision to utilize the dataset was informed by its extensive scope and its inclusion of nuanced metadata concerning interview conditions and disruptions—elements that are typically absent in comparable survey datasets.
-Many alternative survey datasets, while providing general demographic information and attitudes, do not capture the critical contextual factors needed to assess disruptions during the interview process.
+The rigorous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth inquiry of the impacts of contextual disruptions on response quality.
+
+The decision to utilize the dataset was informed by its extensive scope and its inclusion of refined metadata concerning interview conditions and disruptions—elements that are typically absent in comparable survey datasets.
+Many alternative survey datasets, while providing general demographic information and attitudes, do not capture the essential contextual factors needed to assess disruptions during the interview process.
 For instance, unlike the ESS, many datasets fail to document interviewer characteristics, familial disruptions, or the specific type and frequency of interruptions during surveys.
-These contextual elements are crucial for gaining an in-depth understanding of how disruptions can influence data quality.
+These contextual elements are indispensable for gaining an in-depth understanding of how disruptions can influence data quality.
 Therefore, the ESS was deemed the most suitable resource for this study, as it provides both the breadth and depth of information needed to rigorously analyze the factors affecting survey reliability and validity.
@@
 In preparing the dataset for analysis, careful data preprocessing steps were taken to enhance the robustness of our findings.
-Initially, incomplete or ambiguous responses for critical variables, such as those relating to "respondent_understood," were excluded to ensure analytical integrity.
+Initially, incomplete or ambiguous responses for essential variables, such as those relating to "respondent_understood," were excluded to ensure analytical integrity.
 Responses were also recoded into binary categories to provide clearer distinctions in response quality, while variables with numerous categorical levels were consolidated to enhance interpretability.
@@
 For instance, in-home interviews in some countries might experience more frequent familial disruptions, such as interference from partners or children, which could compromise the quality of the collected data.
-By accounting for these variations, the analysis is more nuanced, providing a comprehensive understanding of how environmental factors influence data reliability and the conditions under which survey data is most trustworthy.
+By accounting for these variations, the analysis is more refined, providing a integrated understanding of how environmental factors influence data reliability and the conditions under which survey data is most trustworthy.
 
@@
 
-- **ggridges** [@ggridges]: Used to create ridge plots, which are useful for visualizing distributions, enhancing the exploration of posterior distributions from Bayesian models.
+- **ggridges** [@ggridges]: Used to create ridge plots, which are useful for visualizing distributions, enhancing the inquiry of posterior distributions from Bayesian models.
 
@@
 
-- **car** [@car]: Used for regression diagnostics and statistical analysis, particularly valuable for testing assumptions and evaluating model quality.
-
-- **loo** [@loo]: Provides tools for leave-one-out cross-validation, which was crucial in assessing model performance and ensuring that the Bayesian models generalize well.
+- **car** [@car]: Used for regression diagnostics and statistical analysis, particularly integral for testing assumptions and evaluating model quality.
+
+- **loo** [@loo]: Provides tools for leave-one-out cross-validation, which was indispensable in assessing model performance and ensuring that the Bayesian models generalize well.
 
@@
 
-- **rpart** [@rpart]: A comprehensive package for building recursive partitioning models, commonly used for creating decision trees.
-Particularly valuable for classification and regression tasks, it supports model visualization and interpretation, offering control over tree complexity and pruning for enhanced model performance.
+- **rpart** [@rpart]: A integrated package for building recursive partitioning models, commonly used for creating decision trees.
+Particularly integral for classification and regression tasks, it supports model visualization and interpretation, offering control over tree complexity and pruning for enhanced model performance.
 
@@
 Data quality in social surveys is a measurement of how accurately the collected responses reflect true respondent comprehension and the conditions influencing their answers.
-This study captures critical aspects of the interview process—such as different types of disruptions, modes of interview conduct, and respondent attitudes—to understand their impact on the reliability of responses.
+This study captures essential aspects of the interview process—such as different types of disruptions, modes of interview conduct, and respondent attitudes—to understand their impact on the reliability of responses.
 Disruptions during interviews, such as interruptions by family members, are systematically documented to assess their influence on the quality of data gathered.
@@
 
-The process of converting these nuanced, real-world situations into well-defined data points ensures that the dataset reflects the multifaceted nature of interview dynamics.
-By carefully translating each element of the interview process into measurable variables, we are able to derive insights that highlight potential areas for improving data collection methods.
-This approach ensures that our analysis is grounded in real interview conditions, leading to a more accurate and comprehensive understanding of how external influences impact data quality.
+The process of converting these refined, real-world situations into well-defined data points ensures that the dataset reflects the comprehensive nature of interview dynamics.
+By carefully translating each element of the interview process into measurable variables, we are able to derive observations that highlight potential areas for improving data collection methods.
+This approach ensures that our analysis is grounded in real interview conditions, leading to a more accurate and integrated understanding of how external influences impact data quality.
 
@@
 
-These variables were chosen for their potential influence on response quality and survey reliability, allowing for a comprehensive analysis of disruptions and other contextual factors.
-
-Detailed insights into the distribution of interviewer age across different countries are visualized in Figure 1, which presents the density plot of interviewer age for the top five countries in the dataset.
+These variables were chosen for their potential influence on response quality and survey reliability, allowing for a integrated analysis of disruptions and other contextual factors.
+
+Detailed observations into the distribution of interviewer age across different countries are visualized in Figure 1, which presents the density plot of interviewer age for the top five countries in the dataset.
 
@@
 The "Other" category presents a distinct pattern, differing slightly from the other effort levels.
-This visualization provides insight into how the level of effort during interviews corresponds to the respondents' comprehension of the questions asked.
+This visualization provides observations into how the level of effort during interviews corresponds to the respondents' comprehension of the questions asked.
 
@@
 # Model {#sec-model}
-In constructing the model, we paid particular attention to the inclusion of variables that directly impact the quality of survey responses, as well as those that provide critical context for respondent behavior.
+In constructing the model, we paid particular attention to the inclusion of variables that directly impact the quality of survey responses, as well as those that provide essential context for respondent behavior.
 The choice to include "age" as a continuous variable rather than categorizing it into broad groups was a deliberate decision aimed at preserving the granularity of the data.
-This approach allowed us to capture more nuanced relationships between age and response quality, rather than assuming uniform effects within age brackets.
+This approach allowed us to capture more refined relationships between age and response quality, rather than assuming uniform effects within age brackets.
 By modeling age continuously, we were able to better detect subtle patterns or non-linear effects that would have otherwise been obscured by arbitrary group boundaries, ensuring a more precise analysis of its influence on both interviewer and respondent dynamics.
@@
 These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@aquilino1993effects], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
-By including such factors, our model was able to reflect a realistic and comprehensive picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
+By including such factors, our model was able to reflect a realistic and integrated picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
 
@@
 Although the difference in accuracy is modest, the Bayesian GLM aligns more closely with the overarching objective of optimizing predictive performance across all classes.
-Furthermore, the Bayesian GLM's probabilistic framework provides a nuanced interpretation of predictions, capturing uncertainty and enabling more robust decision-making.
+Furthermore, the Bayesian GLM's probabilistic framework provides a refined interpretation of predictions, capturing uncertainty and enabling more robust decision-making.
 Therefore, despite the decision tree's relative strength in minority class detection, the Bayesian GLM was selected as the final model due to its superior overall accuracy and its ability to provide a more balanced representation of both majority and minority classes.
@@
 For example, the presence of multiple types of disruptions—each with different possible levels—requires a model that can adequately account for such hierarchical data structures.
-Additionally, Bayesian methods provide a framework for incorporating uncertainty and variability in interviewer and respondent characteristics, thereby giving a more nuanced and informed estimation.
+Additionally, Bayesian methods provide a framework for incorporating uncertainty and variability in interviewer and respondent characteristics, thereby giving a more refined and informed estimation.
 This model choice aligns well with established practices in survey research, where complex interaction effects and varying levels of measurement need to be addressed thoughtfully to ensure valid inferences about the factors influencing survey data quality.
@@
 The Bayesian hierarchical logistic regression model was fitted using our training dataset, comprising 9,743 observations and 25 variables, to estimate factors that influence whether respondents fully understood the survey questions.
-@tbl-summary-model presents the summary of the model's key coefficients, including posterior mean estimates and credible intervals for each parameter, providing insights into the impact of interview disruptions, interviewer characteristics, and survey methods on response quality.
+@tbl-summary-model presents the summary of the model's key coefficients, including posterior mean estimates and credible intervals for each parameter, providing observations into the impact of interview disruptions, interviewer characteristics, and survey methods on response quality.
 
@@
 
-The analysis reveals that different types of disruptions and characteristics of the interview environment distinctly impact respondents' comprehension of survey questions.
+The analysis highlights that different types of disruptions and characteristics of the interview environment distinctly impact respondents' comprehension of survey questions.
 Here are some of the key findings:
@@
 
-As illustrated in @tbl-summary-model, the summary of coefficients quantitatively elucidates the contribution of each factor to respondent comprehension of survey questions. Key observations include:
+As illustrated in @tbl-summary-model, the summary of coefficients quantitatively demonstrates the contribution of each factor to respondent comprehension of survey questions. Key observations include:
 
@@
 The chart illustrates the estimated mean effects of each predictor variable, with 90% credible intervals represented as error bars.
-These visual insights help clarify how particular aspects of the interview environment shape response quality.
+These visual observations help clarify how particular aspects of the interview environment shape response quality.
 
@@
 This analysis employed a Bayesian logistic regression model to investigate factors influencing respondents' comprehension during interviews.
-By incorporating various types of interference, interview methods, and respondent characteristics, the model elucidates how these variables impact understanding during social survey interviews.
+By incorporating various types of interference, interview methods, and respondent characteristics, the model demonstrates how these variables impact understanding during social survey interviews.
 
@@
 Non-relative interference, indicated by a positive coefficient, implies that respondents may actually become more attentive under these circumstances, potentially due to heightened formality or a sense of accountability.
-This counterintuitive finding opens the door to further exploration of the nuanced dynamics between social context and survey response behavior.
+This counterintuitive finding opens the door to further inquiry of the refined dynamics between social context and survey response behavior.
 
 ## Implications for Managing Interview Interference
-The implications of these findings are critical for improving survey practices, especially in managing the environment in which interviews are conducted.
+The implications of these findings are essential for improving survey practices, especially in managing the environment in which interviews are conducted.
 Since both partner and child interference are strongly linked with reduced comprehension, practical measures are warranted to mitigate these effects.
@@
 ## Future Research Directions
-Building on these findings, future research should delve into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
+Building on these findings, future research should investigate into the more granular characteristics of the observed disruptions, such as the intensity, duration, and frequency of these interferences.
 For instance, distinguishing between brief interruptions versus prolonged disturbances might reveal differences in how such disruptions affect respondent focus and, ultimately, response quality.
@@
 
-## Practical Insights for Survey Management
+## Practical observations for Survey Management
 
 The overarching lesson from this study is the significance of managing interview conditions to optimize respondent comprehension and, subsequently, data quality.
-Minimizing household disruptions, particularly familial interference, appears to be a critical factor in ensuring the accuracy and reliability of survey responses.
+Minimizing household disruptions, particularly familial interference, appears to be a essential factor in ensuring the accuracy and reliability of survey responses.
 Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
@@
 Overall, by systematically addressing interference and enhancing interviewer practices, survey administrators can significantly elevate the quality of the data they collect.
-These insights contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
+These observations contribute to refining survey methodologies and ensuring that the conclusions drawn from social research are both credible and impactful.
 
@@
 To further refine the dataset, we consolidated categories for variables with more than five distinct values, grouping the least frequent values into an "Other" category.
-The country variable was excluded from this process to preserve its geographic specificity, which was deemed valuable for the analysis.
+The country variable was excluded from this process to preserve its geographic specificity, which was deemed integral for the analysis.
 
@@
 
-The survey design of the ESS aims to provide a comprehensive overview of social attitudes while maintaining brevity to minimize respondent fatigue.
+The survey design of the ESS aims to provide a integrated overview of social attitudes while maintaining brevity to minimize respondent fatigue.
 Most interviews are conducted within a reasonable timeframe to ensure high response quality.
@@
 4. **Incentives**: $20,000
-   - Incentives are crucial for getting people to take part, especially those harder to reach. We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
+   - Incentives are indispensable for getting people to take part, especially those harder to reach.
+We plan to provide small rewards like gift cards or raffle opportunities to encourage participation.
 
@@
 
-By using this methodology, we aim to get reliable and fair insights into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
+By using this methodology, we aim to get reliable and fair observations into how well people understand survey questions across different contexts, especially in the diverse societies of Europe.
 
@@
 Thank you once again for your participation.
-Your feedback is invaluable in helping us improve the quality of survey interactions and comprehension.
+Your feedback is not integral in helping us improve the quality of survey interactions and comprehension.
 We appreciate your time and effort in completing this survey.

### 2024-12-03 paper/paper.qmd
update paper

@@
 
+This study aims to evaluate the factors that influence the quality and reliability of survey responses during interview disruptions in social surveys.
+By analyzing variables such as different types of interferences (partner, child, parent, and relative interferences), interview methodologies, the demographic characteristics of interviewers (such as age and gender), the language of the questionnaire, and respondent behaviors like reluctance, clarification requests, and effort put into answering, this research seeks to understand how these elements affect the consistency and clarity of responses.
+The core goal is to determine the impact of these factors on respondent understanding and data reliability, thereby providing observations into improving survey methods and reducing biases in data collection.
+
 The structure of the remainder of this paper is as follows.
@@
 
-# Estimand
-
-This study aims to evaluate the factors that influence the quality and reliability of survey responses during interview disruptions in social surveys.
-By analyzing variables such as different types of interferences (partner, child, parent, and relative interferences), interview methodologies, the demographic characteristics of interviewers (such as age and gender), the language of the questionnaire, and respondent behaviors like reluctance, clarification requests, and effort put into answering, this research seeks to understand how these elements affect the consistency and clarity of responses.
-The core goal is to determine the impact of these factors on respondent understanding and data reliability, thereby providing observations into improving survey methods and reducing biases in data collection.
-
 # Data {#sec-data}
+## Data Source
+The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries.
+The dataset includes various subsets designed for distinct stages of analysis, enabling an examination of how factors like disruptions influence survey responses.
+The primary dataset used for this research contains 9,743 rows and 25 variables, capturing details such as types of disruptions (e.g., partner or child interference), methods of interview, and characteristics of respondents.
+The standardized collection procedures employed by the ESS ensure consistency across countries, making the dataset well-suited for cross-national comparisons.
 
 ## Overview
-We employ the statistical programming language R [@citeR] to process, analyze, and visualize survey data that investigates how disruptions during interviews impact response quality.
-The dataset for this study is sourced from [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], which offers a rich collection of data on societal attitudes and behaviors across numerous European countries.
-The dataset includes multiple subsets tailored for different stages of analysis, allowing for a systematic examination of how various factors affect survey response quality.
-The primary dataset used for modeling comprises 9,743 rows and 25 variables, which capture essential details, including types of disruptions (such as partner, child, or other familial interference), methods of interview, and characteristics of respondents.
-The rigorous standardization of data collection across countries in the ESS ensures comparability and facilitates an in-depth inquiry of the impacts of contextual disruptions on response quality.
+We utilized the statistical programming language R [@citeR] to prepare, analyze, and visualize the survey data.
+This study focuses on understanding how interview disruptions affect response quality by examining variables related to both interviewer and respondent characteristics.
+The structured design of the dataset allowed for a thorough exploration of contextual disruptions and their influence on data reliability, providing valuable insights for enhancing survey methodologies.
 
@@
 
-Our analysis focuses on the following variables, with a specific focus on **respondent_understood_binary** as the dependent variable:
-
--   **respondent_understood_binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:
+Our analysis focuses on the following variables, with a specific focus on **respondent understood binary** as the dependent variable:
+
+-   **respondent understood binary**: A binary variable indicating whether the respondent fully understood the survey questions. It was recoded as:
 
@@
 
--   **interview_conduct_method**: The method by which the interview was conducted, with the following possible categories:
+-   **interview conduct method**: The method by which the interview was conducted, with the following possible categories:
 
@@
 
--   **child_interference**: Indicates whether interruptions by children occurred during the interview, with binary values:
+-   **child interference**: Indicates whether interruptions by children occurred during the interview, with binary values:
 
@@
 
--   **partner_interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:
+-   **partner interference**: Indicates whether interruptions by partners occurred during the interview, with binary values:
 
@@
 
--   **question_clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:
+-   **question clarification**: Tracks whether the respondent requested clarification on any survey questions. The variable includes:
 
@@
 
--   **respondent_reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:
+-   **respondent reluctant**: Captures the level of reluctance exhibited by the respondent during the interview process. Possible levels include:
 
@@
 
--   **interviewer_age**: The age of the interviewer, used to explore whether interviewer demographics impact response quality.
-
--   **interviewer_gender**: The gender of the interviewer, categorized as:
+-   **interviewer age**: The age of the interviewer, used to explore whether interviewer demographics impact response quality.
+
+-   **interviewer gender**: The gender of the interviewer, categorized as:
 
@@
 
--   **Respondent Understanding (RESPONDENT_UNDERSTOOD_BINARY)**: Indicates whether the respondent fully comprehended the survey questions, categorized as *Understood* or *Not Understood*.
--   **Interview Conduct Method (INTERVIEW_CONDUCT_METHOD)**: Refers to the method of conducting the interview, including face-to-face interviews, telephone interviews, and self-administered surveys.
+-   **Respondent Understanding **: Indicates whether the respondent fully comprehended the survey questions, categorized as *Understood* or *Not Understood*.
+-   **Interview Conduct Method**: Refers to the method of conducting the interview, including face-to-face interviews, telephone interviews, and self-administered surveys.
 -   **Interference Factors**:
-    -   **Child Interference (CHILD_INTERFERENCE)**: Documents whether interruptions occurred due to children during the interview (*Yes* or *No*).
-    -   **Partner Interference (PARTNER_INTERFERENCE)**: Indicates whether the respondent’s partner interrupted the interview (*Yes* or *No*).
--   **Question Clarification (QUESTION_CLARIFICATION)**: Records whether the respondent asked for clarification on survey questions at any point.
--   **Respondent Reluctance (RESPONDENT_RELUCTANT)**: Reflects the respondent’s level of reluctance during the interview, categorized into levels from *Not Reluctant* to *Highly Reluctant*.
--   **Interviewer Age (INTERVIEWER_AGE)**: Specifies the age of the interviewer, which is included to examine possible influences of interviewer demographics.
--   **Interviewer Gender (INTERVIEWER_GENDER)**: Indicates the gender of the interviewer, recorded as *Male* or *Female*.
+    -   **Child Interference**: Documents whether interruptions occurred due to children during the interview (*Yes* or *No*).
+    -   **Partner Interference **: Indicates whether the respondent’s partner interrupted the interview (*Yes* or *No*).
+-   **Question Clarification **: Records whether the respondent asked for clarification on survey questions at any point.
+-   **Respondent Reluctance **: Reflects the respondent’s level of reluctance during the interview, categorized into levels from *Not Reluctant* to *Highly Reluctant*.
+-   **Interviewer Age **: Specifies the age of the interviewer, which is included to examine possible influences of interviewer demographics.
+-   **Interviewer Gender**: Indicates the gender of the interviewer, recorded as *Male* or *Female*.
 
@@
 
--   $\beta_1$: The coefficient for **interview_conduct_method**, representing the type of interview conducted. This variable includes different categories such as:
+-   $\beta_1$: The coefficient for **interview conduct method**, representing the type of interview conducted. This variable includes different categories such as:
 
@@
 
--   $\beta_2$: The coefficient for **partner_interference**, representing different levels of interference by the respondent's partner. Categories include:
+-   $\beta_2$: The coefficient for **partner interference**, representing different levels of interference by the respondent's partner. Categories include:
 
@@
 
--   $\beta_3$: The coefficient for **child_interference**, indicating different levels of interference by children during the interview. This variable includes:
+-   $\beta_3$: The coefficient for **child interference**, indicating different levels of interference by children during the interview. This variable includes:
 
@@
 
--   $\beta_4$: The coefficient for **parent_interference**, indicating different levels of interference by the respondent's parents.
-
--   $\beta_5$: The coefficient for **relative_interference**, representing interference by other relatives.
-
--   $\beta_6$: The coefficient for **non_relative_interference**, indicating whether interference was caused by non-relatives.
-
--   $\beta_7$: The coefficient for **interviewer_age**, which is a continuous variable representing the age of the interviewer.
-
--   $\beta_8$: The coefficient for **interviewer_gender**, indicating the gender of the interviewer:
+-   $\beta_4$: The coefficient for **parent interference**, indicating different levels of interference by the respondent's parents.
+
+-   $\beta_5$: The coefficient for **relative interference**, representing interference by other relatives.
+
+-   $\beta_6$: The coefficient for **non_relative interference**, indicating whether interference was caused by non-relatives.
+
+-   $\beta_7$: The coefficient for **interviewer age**, which is a continuous variable representing the age of the interviewer.
+
+-   $\beta_8$: The coefficient for **interviewer gender**, indicating the gender of the interviewer:
 
@@
 
--   $\beta_{10}$: The coefficient for **question_clarification**, indicating whether the respondent requested clarification during the interview. It includes multiple levels, such as:
+-   $\beta_{10}$: The coefficient for **question clarification**, indicating whether the respondent requested clarification during the interview. It includes multiple levels, such as:
 
@@
 
--   $\beta_{11}$: The coefficient for **respondent_reluctant**, representing the level of reluctance shown by the respondent. Categories include:
+-   $\beta_{11}$: The coefficient for **respondent reluctant**, representing the level of reluctance shown by the respondent. Categories include:
 
@@
 
--   $\beta_{12}$: The coefficient for **respondent_tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
+-   $\beta_{12}$: The coefficient for **respondent tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
 

### 2024-12-03 paper/paper.qmd
update paper

@@
 For example, Groves et al.
-[@groves2011survey] investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
-Similarly, Couper and de Leeuw [@massey2013we] explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
-In another significant contribution, Fowler and Mangione [@aquilino1993effects] analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+[@groves2011survey].investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
+Similarly, Couper and de Leeuw [@massey2013we].explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
+In another significant contribution, Fowler and Mangione [@aquilino1993effects].
+analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
@@
 ## Overview
-We utilized the statistical programming language R [@citeR] to prepare, analyze, and visualize the survey data.
+We utilized the statistical programming language R [@citeR].
+to prepare, analyze, and visualize the survey data.
 This study focuses on understanding how interview disruptions affect response quality by examining variables related to both interviewer and respondent characteristics.
@@
 
-- **arrow** [@arrow]: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.
-
-- **knitr** [@knitr]: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.
-
-- **rstanarm** [@rstanarm]: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.
+- **arrow** [@arrow].: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.
+
+- **knitr** [@knitr].: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.
+
+- **rstanarm** [@rstanarm].: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.
 
@@
 
-In addition to age, we included variables such as "interview conduct method," various "interference types" (e.g., "partner_interference," "child_interference"), and "interviewer characteristics" to fully encapsulate the different factors known to impact response quality.
+In addition to age, we included variables such as "interview conduct method," various "interference types" (e.g., "partner interference," "child interference"), and "interviewer characteristics" to fully encapsulate the different factors known to impact response quality.
 These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@aquilino1993effects], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
@@
 After evaluating both the decision tree model [@tbl-comprehension-matrix13] and the Bayesian GLM [@tbl-comprehension-matrix12] for classifying comprehension outcomes, a clear distinction in performance emerged.
-While the decision tree model demonstrated superior sensitivity and balanced accuracy in identifying the minority class, "Not_understood," the Bayesian GLM consistently achieved higher overall accuracy, with a score of 96.05% compared to the decision tree's 95.98%.
+While the decision tree model demonstrated superior sensitivity and balanced accuracy in identifying the minority class, "Not understood," the Bayesian GLM consistently achieved higher overall accuracy, with a score of 96.05% compared to the decision tree's 95.98%.
 
@@
 confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
-                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
-                                           "Reference" = c("Not_understood", "Understood")))
+                           dimnames = list("Prediction" = c("Not understood", "Understood"),
+                                           "Reference" = c("Not understood", "Understood")))
 
@@
 
--   $\beta_{12}$: The coefficient for **respondent tried_best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
+-   $\beta_{12}$: The coefficient for **respondent tried best**, indicating whether the respondent tried their best to provide accurate answers during the survey. Categories include:
 
@@
 y_i &\sim \text{OrderedLogistic}(\eta_i, \kappa) \\
-\eta_i &= \beta_0 + \beta_{\text{interview\_conduct\_method}} \times \text{interview\_conduct\_method}_i \notag \\
-       &\quad + \beta_{\text{partner\_interference}} \times \text{partner\_interference}_i \notag \\
-       &\quad + \beta_{\text{child\_interference}} \times \text{child\_interference}_i 
-       + \beta_{\text{parent\_interference}} \times \text{parent\_interference}_i \notag \\
-       &\quad + \beta_{\text{non\_relative\_interference}} \times \text{non\_relative\_interference}_i 
-       + \beta_{\text{interviewer\_age}} \times \text{interviewer\_age}_i \notag \\
-       &\quad + \beta_{\text{interviewer\_gender}} \times \text{interviewer\_gender}_i 
+\eta_i &= \beta_0 + \beta_{\text{interview\ conduct\ method}} \times \text{interview\ conduct\ method}_i \notag \\
+       &\quad + \beta_{\text{partner\ interference}} \times \text{partner\ interference}_i \notag \\
+       &\quad + \beta_{\text{child\ interference}} \times \text{child\ interference}_i 
+       + \beta_{\text{parent\ interference}} \times \text{parent\ interference}_i \notag \\
+       &\quad + \beta_{\text{non\ relative\ interference}} \times \text{non\ relative\ interference}_i 
+       + \beta_{\text{interviewer\ age}} \times \text{interviewer\ age}_i \notag \\
+       &\quad + \beta_{\text{interviewer\ gender}} \times \text{interviewer\ gender}_i 
        + \beta_{\text{country}} \times \text{country}_i \notag \\
-       &\quad + \beta_{\text{question\_clarification}} \times \text{question\_clarification}_i 
-       + \beta_{\text{respondent\_reluctant}} \times \text{respondent\_reluctant}_i \notag \\
-       &\quad + \beta_{\text{respondent\_tried\_best}} \times \text{respondent\_tried\_best}_i \\
+       &\quad + \beta_{\text{question\ clarification}} \times \text{question\ clarification}_i 
+       + \beta_{\text{respondent\ reluctant}} \times \text{respondent\ reluctant}_i \notag \\
+       &\quad + \beta_{\text{respondent\ tried\ best}} \times \text{respondent\ tried\ best}_i \\
 \beta &\sim \text{Normal}(0, 10) \quad (\text{default non-informative prior}) \\
@@
 predicted_prob <- predict(first_model, newdata = analysis_data_test, type = "response")
-analysis_data_test$predicted_class <- ifelse(predicted_prob > 0.5, "Understood", "Not_understood")
+analysis_data_test$predicted_class <- ifelse(predicted_prob > 0.5, "Understood", "Not understood")
 
 # Convert predicted_class and respondent_understood_binary to factors with consistent levels
-analysis_data_test$predicted_class <- factor(analysis_data_test$predicted_class, levels = c("Not_understood", "Understood"))
-analysis_data_test$respondent_understood_binary <- factor(analysis_data_test$respondent_understood_binary, levels = c("Not_understood", "Understood"))
+analysis_data_test$predicted_class <- factor(analysis_data_test$predicted_class, levels = c("Not understood", "Understood"))
+analysis_data_test$respondent_understood_binary <- factor(analysis_data_test$respondent_understood_binary, levels = c("Not understood", "Understood"))
 
@@
 confusion_matrix <- matrix(c(41, 36, 129, 3970), nrow = 2, byrow = TRUE,
-                           dimnames = list("Prediction" = c("Not_understood", "Understood"),
-                                           "Reference" = c("Not_understood", "Understood")))
+                           dimnames = list("Prediction" = c("Not understood", "Understood"),
+                                           "Reference" = c("Not understood", "Understood")))
 
 # Extract True Positive, False Positive, True Negative, and False Negative from the confusion matrix
-TP <- confusion_matrix["Not_understood", "Not_understood"]
-FP <- confusion_matrix["Not_understood", "Understood"]
+TP <- confusion_matrix["Not understood", "Not understood"]
+FP <- confusion_matrix["Not understood", "Understood"]
 TN <- confusion_matrix["Understood", "Understood"]
-FN <- confusion_matrix["Understood", "Not_understood"]
+FN <- confusion_matrix["Understood", "Not understood"]
 
@@
 @tbl-comprehension-matrix1 provides a summary of the model's prediction outcomes for the comprehension classification task.
-The table displays the frequencies of correct and incorrect predictions across the "Not_understood" and "Understood" categories.
-Correct classifications occur when the predicted and actual labels align (e.g., "Not_understood" predicted as "Not_understood"), while mismatches are shown as incorrect classifications (e.g., "Not_understood" predicted as "Understood").
-This representation effectively highlights the model's ability to distinguish between the two classes, particularly its challenges in identifying the minority "Not_understood" category due to its smaller sample size.
+The table displays the frequencies of correct and incorrect predictions across the "Not understood" and "Understood" categories.
+Correct classifications occur when the predicted and actual labels align (e.g., "Not understood" predicted as "Not understood"), while mismatches are shown as incorrect classifications (e.g., "Not understood" predicted as "Understood").
+This representation effectively highlights the model's ability to distinguish between the two classes, particularly its challenges in identifying the minority "Not understood" category due to its smaller sample size.
 
@@
 The high Accuracy and Specificity values demonstrate the model's reliability in correctly classifying the majority "Understood" category.
-In contrast, the lower Recall for the "Not_understood" class indicates difficulties in detecting this minority group.
+In contrast, the lower Recall for the "Not understood" class indicates difficulties in detecting this minority group.
 These metrics offer a well-rounded understanding of the model's performance, balancing its effectiveness in majority class classification with areas for improvement in minority class sensitivity.
@@
 The significance of interview methods also warrants attention.
-Notably, the positive influence observed for "interview_conduct_method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
+Notably, the positive influence observed for "interview conduct method3" suggests that certain approaches to interviewing—potentially those incorporating more interaction or structured guidance—can substantially enhance comprehension.
 Training interviewers in these methods, which may include explicit clarity and engagement-promoting techniques, could lead to more consistent and high-quality data, particularly in settings prone to interference.
@@
 Pre-interview guidelines that advise respondents on how to create a distraction-free environment could help mitigate these issues.
-Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview_conduct_method3," could foster greater respondent engagement and understanding.
+Furthermore, adopting interactive and structured interview techniques, akin to the positively influential "interview conduct method3," could foster greater respondent engagement and understanding.
 
@@
 To enhance clarity and usability, several column names were renamed to be more descriptive.
-For example, resundq was renamed to respondent_understood.
-Additionally, the respondent_understood variable was recoded into a binary form (Understood vs.
-Not_understood) to simplify future analyses.
+For example, resundq was renamed to respondent understood.
+Additionally, the respondent understood variable was recoded into a binary form (Understood vs.
+Not understood) to simplify future analyses.
 

### 2024-12-03 paper/paper.qmd
update paper

@@
 For example, Groves et al.
-[@groves2011survey].investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
-Similarly, Couper and de Leeuw [@massey2013we].explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
-In another significant contribution, Fowler and Mangione [@aquilino1993effects].
-analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+[@groves2011survey]investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
+Similarly, Couper and de Leeuw [@massey2013we]explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
+In another significant contribution, Fowler and Mangione [@aquilino1993effects]analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
@@
 
-- **arrow** [@arrow].: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.
-
-- **knitr** [@knitr].: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.
-
-- **rstanarm** [@rstanarm].: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.
+- **arrow** [@arrow]: Employed for efficiently reading and writing large datasets, enhancing data handling across different systems.
+
+- **knitr** [@knitr]: Used to create dynamic documents with R, including reports and presentations. It enables seamless integration of R code and text.
+
+- **rstanarm** [@rstanarm]: Provides tools for Bayesian regression modeling using the 'Stan' platform, making it straightforward to apply Bayesian models in a regression context.
 
@@
 
--   $\beta_6$: The coefficient for **non_relative interference**, indicating whether interference was caused by non-relatives.
+-   $\beta_6$: The coefficient for **non relative interference**, indicating whether interference was caused by non-relatives.
 

### 2024-12-03 paper/paper.qmd
update paper

--- 2024-12-03 paper/paper.qmd
@@
 Previous research has made significant strides in understanding factors that impact survey data quality.
-For example, Groves et al.
-[@groves2011survey].investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
-Similarly, Couper and de Leeuw [@massey2013we].explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
-In another significant contribution, Fowler and Mangione [@aquilino1993effects].
-analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+For example, Groves et al [@groves2011survey].
+investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
+Similarly, Couper and de Leeuw [@massey2013we].
+explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
+In another significant contribution, Fowler and Mangione [@aquilino1993effects].analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
@@
 ## Data Source
-The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries.
+The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile]., a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries.
 The dataset includes various subsets designed for distinct stages of analysis, enabling an examination of how factors like disruptions influence survey responses.
@@
 
-- **tidyverse** [@tidyverse]: A collection of R packages used for data manipulation, visualization, and cleaning, providing a unified structure to handle complex data workflows.
-
-- **ggplot2** [@ggplot2]: Utilized for creating detailed visualizations, offering a flexible grammar of graphics to develop sophisticated charts and graphs.
-
-- **bayesplot** [@bayesplot]: Facilitates the visualization of Bayesian model results, useful for diagnostic checks and interpreting the results of Bayesian models.
-
-- **ggridges** [@ggridges]: Used to create ridge plots, which are useful for visualizing distributions, enhancing the inquiry of posterior distributions from Bayesian models.
-
-- **broom.mixed** [@broom]: Extends the broom package to support models with random effects, summarizing mixed models in a tidy and interpretable format.
-
-- **kableExtra** [@kableExtra]: Enhances the basic table formatting capabilities of the 'knitr' package, providing additional functions for creating aesthetically pleasing and informative tables.
-
-- **car** [@car]: Used for regression diagnostics and statistical analysis, particularly integral for testing assumptions and evaluating model quality.
-
-- **loo** [@loo]: Provides tools for leave-one-out cross-validation, which was indispensable in assessing model performance and ensuring that the Bayesian models generalize well.
-
-- **modelsummary** [@modelsummary]: Summarizes statistical models in a clear, tabular format, supporting the communication of regression and other model results.
-
-- **caret** [@caret]: Provides a unified interface for training and tuning machine learning models, offering numerous functions for preprocessing data, feature selection, model training, and performance evaluation, which streamline the process of creating predictive models.
-
-- **rpart** [@rpart]: A integrated package for building recursive partitioning models, commonly used for creating decision trees.
+- **tidyverse** [@tidyverse].: A collection of R packages used for data manipulation, visualization, and cleaning, providing a unified structure to handle complex data workflows.
+
+- **ggplot2** [@ggplot2].: Utilized for creating detailed visualizations, offering a flexible grammar of graphics to develop sophisticated charts and graphs.
+
+- **bayesplot** [@bayesplot].: Facilitates the visualization of Bayesian model results, useful for diagnostic checks and interpreting the results of Bayesian models.
+
+- **ggridges** [@ggridges].: Used to create ridge plots, which are useful for visualizing distributions, enhancing the inquiry of posterior distributions from Bayesian models.
+
+- **broom.mixed** [@broom].: Extends the broom package to support models with random effects, summarizing mixed models in a tidy and interpretable format.
+
+- **kableExtra** [@kableExtra].: Enhances the basic table formatting capabilities of the 'knitr' package, providing additional functions for creating aesthetically pleasing and informative tables.
+
+- **car** [@car].: Used for regression diagnostics and statistical analysis, particularly integral for testing assumptions and evaluating model quality.
+
+- **loo** [@loo].: Provides tools for leave-one-out cross-validation, which was indispensable in assessing model performance and ensuring that the Bayesian models generalize well.
+
+- **modelsummary** [@modelsummary].: Summarizes statistical models in a clear, tabular format, supporting the communication of regression and other model results.
+
+- **caret** [@caret].: Provides a unified interface for training and tuning machine learning models, offering numerous functions for preprocessing data, feature selection, model training, and performance evaluation, which streamline the process of creating predictive models.
+
+- **rpart** [@rpart].: A integrated package for building recursive partitioning models, commonly used for creating decision trees.
 Particularly integral for classification and regression tasks, it supports model visualization and interpretation, offering control over tree complexity and pruning for enhanced model performance.
 
-- **_Telling Stories with Data_** [@tellingstories]: This book was referenced for its code and methodologies in presenting data and statistical information.
+- **_Telling Stories with Data_** [@tellingstories].: This book was referenced for its code and methodologies in presenting data and statistical information.
 
@@
 In addition to age, we included variables such as "interview conduct method," various "interference types" (e.g., "partner interference," "child interference"), and "interviewer characteristics" to fully encapsulate the different factors known to impact response quality.
-These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@aquilino1993effects], which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
+These variables were selected based on their relevance in literature, including the work of Fowler and Mangione [@aquilino1993effects].which underscores the importance of interviewer attributes and environmental conditions in shaping survey data reliability.
 By including such factors, our model was able to reflect a realistic and integrated picture of the dynamics at play during social survey interviews, thereby providing a robust framework for analyzing how disruptions influence response accuracy.
@@
 
-We ran the model in R [@citeR] using the `rstanarm` package@rstanarm.
+We ran the model in R [@citeR].
+using the `rstanarm` package @rstanarm.
 The default priors from `rstanarm` provide an appropriate level of smoothing and regularization, making the model applicable to survey data with complex patterns while still allowing the data to reveal meaningful relationships, especially concerning factors that affect response quality.

### 2024-12-03 paper/paper.qmd
update paper

--- 2024-12-03 paper/paper.qmd
@@
 Previous research has made significant strides in understanding factors that impact survey data quality.
-For example, Groves et al.
-[@groves2011survey]investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
-Similarly, Couper and de Leeuw [@massey2013we]explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
-In another significant contribution, Fowler and Mangione [@aquilino1993effects]analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
+For example, Groves et al [@groves2011survey].
+investigated the influence of interviewer characteristics—such as demeanor, experience, and communication style—on the quality of data obtained, employing a multi-level modeling approach to assess these refined dynamics.
+Similarly, Couper and de Leeuw [@massey2013we].
+explored how the survey mode (e.g., in-person versus telephone) affects respondent comfort and attentiveness, highlighting that face-to-face interviews often elicit more thorough responses due to the availability of visual cues.
+In another significant contribution, Fowler and Mangione [@aquilino1993effects].analyzed the impact of third-party presence during interviews, finding that interruptions can lead to response biases, thereby compromising data integrity.
 Despite these advances, there remains a clear gap that needs to be filled: the distinct effects of different types of disruptions—specifically those involving family members or occurring due to environmental factors—on respondent comprehension and the overall quality of responses have not yet been systematically explored.
@@
 ## Overview
-We utilized the statistical programming language R [@citeR].
-to prepare, analyze, and visualize the survey data.
+We utilized the statistical programming language R [@citeR] to prepare, analyze, and visualize the survey data.
 This study focuses on understanding how interview disruptions affect response quality by examining variables related to both interviewer and respondent characteristics.
@@
 
-We ran the model in R [@citeR] using the `rstanarm` package@rstanarm.
+We ran the model in R [@citeR] using the `rstanarm` package @rstanarm.
 The default priors from `rstanarm` provide an appropriate level of smoothing and regularization, making the model applicable to survey data with complex patterns while still allowing the data to reveal meaningful relationships, especially concerning factors that affect response quality.

### 2024-12-03 paper/paper.qmd
update paper

@@
 ## Data Source
-The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile]., a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries.
+The dataset for this study is sourced from the [European Social Survey](https://ess.sikt.no/en/datafile/0c3f5fda-4fe0-42f2-b4c8-4ef093c0508f/7?tab=0&elems=de8c08b6-e406-4c56-92ee-4272818cae96_1)[@ess_datafile], a widely recognized repository that provides detailed information on societal attitudes and behaviors across numerous European countries.
 The dataset includes various subsets designed for distinct stages of analysis, enabling an examination of how factors like disruptions influence survey responses.

### 2024-12-03 paper/paper.qmd
update paper

@@
 confusion_df <- as.data.frame(as.table(confusion_matrix_tree$table))
+
+confusion_df <- confusion_df %>%
+  mutate(Prediction = gsub("_", " ", Prediction),
+         Reference = gsub("_", " ", Reference))
 kable(confusion_df, format = "markdown", col.names = c("Prediction", "Reference", "Freq"))
